---
title: "BreedingNanalysis"
output: pdf_document
date: "2023-03-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lmerTest)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggthemes)
library(gapminder)
library(multcomp)
library(emmeans)
library(multcompView)
library(scales)
```

#Things to ask Ginny
- It automatically excludes NA values, but not 0 values, right? 
- Should we be treating the N rates as "levels" in the models or let them be numerical? - Should I be using lm or lmer? 
- Is doing a model with all locations' data included oksy or should I be using it as an effect within the model too?
-
#Questions

The main question we are trying to answer here is the ideal Nitrogen rate to apply to the intercropped plots for the breeding experiment. 

Variables we have include 1)Nitrogen rate 2)Alfalfa Biomass 3)IWG biomass 4)IWG grain yield 5)location 

#Goals 
create models for 1)each location and 2)all locations that show interaction between nitrogen rate and a)Alf biomass b)IWG biomass c)grain yield d)total biomass 

#read in csv 
```{r}
DataAll<-read.csv(file='MasterDataSpreadsheet  - All locations All years combined.csv', stringsAsFactors = F)
```

#isolate only intercropped plots and make some easily useable dataframes 
```{r}
#need to get rid of empty cells which represent monocrop treatments  
IntercroppedOnly1<- DataAll[DataAll$Intercropped != "", ]
#need to get rid of row 31 for Alfbio because of a messed up value (no dry weight was ever recorded so the PlotAlfDryKgHa was a big negative number)
IntercroppedOnly<-IntercroppedOnly1[-c(31),] # remove row 31
#need to create a total biomass in Kg/Ha 
IntercroppedOnly$TotalBioKgHa<-c(as.numeric(IntercroppedOnly$PlotIWGDryKgHa)+as.numeric(IntercroppedOnly$PlotAlfDryKgHa))
#need to create data frame for each location for ease 
NyOnly<-subset(IntercroppedOnly, Location == 'NY')
MnOnly<-subset(IntercroppedOnly, Location == 'MN')
WiOnly<-subset(IntercroppedOnly, Location == 'WI')
#need to take out all the 0 values for grain 
GrainDF<-IntercroppedOnly[IntercroppedOnly$PlotThreshedGrainKgHa!="0",]
#need to take out harvest 2 data because there won't be any grain data there, then can use these data frames for individual location grain analysis 
GrainNyOnly<-NyOnly[NyOnly$Harvest!="Fall",] # L changed from 2 to Fall
GrainMnOnly<-MnOnly[MnOnly$Harvest!="Fall",]
GrainWiOnly<-WiOnly[WiOnly$Harvest!="Fall",]

```


#potentially useful example I used from from Trisoc analysis stuff 
```{r}
#mod4 <- lmer(IWGha~Nitrogen*Crop*Location + Location:(1|block.rep),data=ALL_IWGonly) 
#mod4_N<-emmeans(mod4, ~Nitrogen)
#pairs(mod4_N)
```

#Following above example
#All locations Alf biomass
```{r}
# L : should Location be a character or a factor 
IntercroppedOnly$NRate <- as.factor(IntercroppedOnly$NRate)
IntercroppedOnly$Rep <- as.factor(IntercroppedOnly$Rep)
IntercroppedOnly$PlotAlfDryKgHa<-as.numeric(IntercroppedOnly$PlotAlfDryKgHa)
mod1<-lmer(PlotAlfDryKgHa~NRate*Location*YearCode + (1|Rep), data=IntercroppedOnly) # L this originally was NRate*Location, but I get an error: "boundary (singular) fit: see help('isSingular')" ; so I added YearCode
mod1N<-emmeans(mod1, ~NRate)
pairs(mod1N)
```

#All locations IWG biomass 
```{r}
IntercroppedOnly$NRate <- as.factor(IntercroppedOnly$NRate)
IntercroppedOnly$Rep <- as.factor(IntercroppedOnly$Rep)
IntercroppedOnly$PlotIWGDryKgHa<-as.numeric(IntercroppedOnly$PlotIWGDryKgHa)
mod2<-lmer(PlotIWGDryKgHa~NRate*Location*YearCode + (1|Rep), data=IntercroppedOnly) # L this originally was NRate*Location, but I get an error: "boundary (singular) fit: see help('isSingular')" ; so I added YearCode
mod2N<-emmeans(mod2, ~NRate)
pairs(mod2N)
```

#All locations grain yield 
```{r}
GrainDF$NRate <- as.factor(GrainDF$NRate)
GrainDF$Rep <- as.factor(GrainDF$Rep)
GrainDF$PlotThreshedGrainKgHa<-as.numeric(GrainDF$PlotThreshedGrainKgHa)
mod3<-lmer(PlotThreshedGrainKgHa~NRate*Location + (1|Rep), data=GrainDF)
mod3N<-emmeans(mod3, ~NRate)
pairs(mod3N)
```


#Same as above but split into each individual location (aka location not an interaction factor?)
#NY ALF biomass (mod1NY), IWG biomass (mod2NY), and Grain yield (mod3NY) compared across Nrates
```{r}
NyOnly$NRate <- as.factor(NyOnly$NRate)
NyOnly$Rep <- as.factor(NyOnly$Rep)
NyOnly$PlotAlfDryKgHa<-as.numeric(NyOnly$PlotAlfDryKgHa)
NyOnly$PlotIWGDryKgHa<-as.numeric(NyOnly$PlotIWGDryKgHa)
GrainNyOnly$NRate <- as.factor(GrainNyOnly$NRate)
GrainNyOnly$Rep <- as.factor(GrainNyOnly$Rep)
GrainNyOnly$PlotThreshedGrainKgHa<-as.numeric(GrainNyOnly$PlotThreshedGrainKgHa)
mod1NY<-lmer(PlotAlfDryKgHa~NRate + (1|Rep), data=NyOnly)
mod1NNY<-emmeans(mod1NY, ~NRate)
pairs(mod1NNY)
mod2NY<-lmer(PlotIWGDryKgHa~NRate + (1|Rep), data=NyOnly)
mod2NNY<-emmeans(mod2NY, ~NRate)
pairs(mod2NNY)
mod3NY<-lmer(PlotThreshedGrainKgHa~NRate + (1|Rep), data=GrainNyOnly)
mod3NNY<-emmeans(mod3NY, ~NRate)
pairs(mod3NNY)
```

#MN ALF biomass (mod1Mn), IWG biomass (mod2Mn), and Grain yield (mod3Mn) compared across Nrates
```{r}
MnOnly$NRate <- as.factor(MnOnly$NRate)
MnOnly$Rep <- as.factor(MnOnly$Rep)
MnOnly$PlotAlfDryKgHa<-as.numeric(MnOnly$PlotAlfDryKgHa)
MnOnly$PlotIWGDryKgHa<-as.numeric(MnOnly$PlotIWGDryKgHa)
GrainMnOnly$NRate <- as.factor(GrainMnOnly$NRate)
GrainMnOnly$Rep <- as.factor(GrainMnOnly$Rep)
GrainMnOnly$PlotThreshedGrainKgHa<-as.numeric(GrainMnOnly$PlotThreshedGrainKgHa)
mod1Mn<-lmer(PlotAlfDryKgHa~NRate + (1|Rep), data=MnOnly)
mod1NMn<-emmeans(mod1Mn, ~NRate)
pairs(mod1NMn)
mod2Mn<-lmer(PlotIWGDryKgHa~NRate + (1|Rep), data=MnOnly)
mod2NMn<-emmeans(mod2Mn, ~NRate)
pairs(mod2NMn)
mod3Mn<-lmer(PlotThreshedGrainKgHa~NRate + (1|Rep), data=GrainMnOnly)
mod3NMn<-emmeans(mod3Mn, ~NRate)
pairs(mod3NMn)
```

#Wi ALF biomass (mod1Wi), IWG biomass (mod2Wi), and Grain yield (mod3Wi) compared across Nrates
```{r}
WiOnly$NRate <- as.factor(WiOnly$NRate)
WiOnly$Rep <- as.factor(WiOnly$Rep)
WiOnly$PlotAlfDryKgHa<-as.numeric(WiOnly$PlotAlfDryKgHa)
WiOnly$PlotIWGDryKgHa<-as.numeric(WiOnly$PlotIWGDryKgHa)
GrainWiOnly$NRate <- as.factor(GrainWiOnly$NRate)
GrainWiOnly$Rep <- as.factor(GrainWiOnly$Rep)
GrainWiOnly$PlotThreshedGrainKgHa<-as.numeric(GrainWiOnly$PlotThreshedGrainKgHa)
mod1Wi<-lmer(PlotAlfDryKgHa~NRate + (1|Rep), data=WiOnly)
mod1NWi<-emmeans(mod1Wi, ~NRate)
pairs(mod1NWi)
mod2Wi<-lmer(PlotIWGDryKgHa~NRate + (1|Rep), data=WiOnly)
mod2NWi<-emmeans(mod2Wi, ~NRate)
pairs(mod2NWi)
mod3Wi<-lmer(PlotThreshedGrainKgHa~NRate + (1|Rep), data=GrainWiOnly)
mod3NWi<-emmeans(mod3Wi, ~NRate)
pairs(mod3NWi)
```



#Below is all the stuff I did first, not following Trisoc example (lm and anova) probably just silliness, feel free to ignore. 

#linear models for biomass based on all locations
```{r}
#Alfalfa biomass by Nrate 
AllLocAlfBio<-lm(PlotAlfDryKgHa~NRate, data=IntercroppedOnly)
summary(AllLocAlfBio)
#IWG Biomass by Nrate
AllLocIWGBio<-lm(PlotIWGDryKgHa~NRate, data=IntercroppedOnly)
summary(AllLocIWGBio)
#Total biomass (IWG+Alf) by Nrate
AllLocTotBio<-lm(TotalBioKgHa~NRate, data=IntercroppedOnly)
summary(AllLocTotBio)
```

#Anovas for biomass based on all locations 
```{r}
#Alfalfa biomass by Nrate 
AllLocAlfBio1<-aov(PlotAlfDryKgHa~NRate, data=IntercroppedOnly)
summary(AllLocAlfBio1)
#IWG Biomass by Nrate
AllLocIWGBio1<-aov(PlotIWGDryKgHa~NRate, data=IntercroppedOnly)
summary(AllLocIWGBio1)
#Total biomass (IWG+Alf) by Nrate
AllLocTotBio1<-aov(TotalBioKgHa~NRate, data=IntercroppedOnly)
summary(AllLocTotBio1)
```

#linear models for biomass in NY 
```{r}
NyAlfBio<-lm(PlotAlfDryKgHa~NRate, data=NyOnly)
summary(NyAlfBio)
NyIWGBio<-lm(PlotIWGDryKgHa~NRate, data=NyOnly)
summary(NyIWGBio)  
NyTotBio<-lm(TotalBioKgHa~NRate, data=NyOnly)
summary(NyTotBio)
```


#Anovas for biomass in NY 
```{r}
NyAlfBio1<-aov(PlotAlfDryKgHa~NRate, data=NyOnly)
summary(NyAlfBio1)
NyIWGBio1<-aov(PlotIWGDryKgHa~NRate, data=NyOnly)
summary(NyIWGBio1)  
NyTotBio1<-aov(TotalBioKgHa~NRate, data=NyOnly)
summary(NyTotBio1)
```

#linear models for biomass in MN 
```{r}
MnAlfBio<-lm(PlotAlfDryKgHa~NRate, data=MnOnly)
summary(MnAlfBio)
MnIWGBio<-lm(PlotIWGDryKgHa~NRate, data=MnOnly)
summary(MnIWGBio)  
MnTotBio<-lm(TotalBioKgHa~NRate, data=MnOnly)
summary(MnTotBio)
```

#Anovas for biomass in MN 
```{r}
MnAlfBio1<-aov(PlotAlfDryKgHa~NRate, data=MnOnly)
summary(MnAlfBio1)
MnIWGBio1<-aov(PlotIWGDryKgHa~NRate, data=MnOnly)
summary(MnIWGBio1)  
MnTotBio1<-aov(TotalBioKgHa~NRate, data=MnOnly)
summary(MnTotBio1)
```

#linear models for biomass in WI 
```{r}
WiAlfBio<-lm(PlotAlfDryKgHa~NRate, data=WiOnly)
summary(WiAlfBio)
WiIWGBio<-lm(PlotIWGDryKgHa~NRate, data=WiOnly)
summary(WiIWGBio)  
WiTotBio<-lm(TotalBioKgHa~NRate, data=WiOnly)
summary(WiTotBio)
```


#Anovas for biomass in WI 
```{r}
WiAlfBio1<-aov(PlotAlfDryKgHa~NRate, data=WiOnly)
summary(WiAlfBio1)
WiIWGBio1<-aov(PlotIWGDryKgHa~NRate, data=WiOnly)
summary(WiIWGBio1)  
WiTotBio1<-aov(TotalBioKgHa~NRate, data=WiOnly)
summary(WiTotBio1)
```


#Linear models of grain yield now; by location and not by location
```{r}
#all locations grain yield by Nrate
AllLocGrain<-lm(PlotThreshedGrainKgHa~NRate, data=GrainDF)
summary(AllLocGrain)
#NY grain yield by Nrate
NyGrain<-lm(PlotThreshedGrainKgHa~NRate, data=GrainNyOnly)
summary(NyGrain)
#WI grain yield by Nrate 
WiGrain<-lm(PlotThreshedGrainKgHa~NRate, data=GrainWiOnly)
summary(WiGrain)
#MN grain yield by Nrate (outlier because MN had a bad grain yield due to pests)
MnGrain<-lm(PlotThreshedGrainKgHa~NRate, data=GrainMnOnly)
summary(MnGrain)
```


#Anovas for grain yield now; by location and not by location
```{r}
#all locations grain yield by Nrate
AllLocGrain1<-aov(PlotThreshedGrainKgHa~NRate, data=GrainDF)
summary(AllLocGrain1)
TukeyHSD(AllLocGrain1, conf.level = .95)
#NY grain yield by Nrate
NyGrain1<-aov(PlotThreshedGrainKgHa~NRate, data=GrainNyOnly)
summary(NyGrain1)
TukeyHSD(NyGrain1)
#WI grain yield by Nrate 
WiGrain1<-aov(PlotThreshedGrainKgHa~NRate, data=GrainWiOnly)
summary(WiGrain1)
#MN grain yield by Nrate (outlier because MN had a bad grain yield due to pests)
MnGrain1<-aov(PlotThreshedGrainKgHa~NRate, data=GrainMnOnly)
summary(MnGrain1)
```


