---
title: "Alf-IWG Forage"
date: "2026-06-01"
editor_options: 
  chunk_output_type: console
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# just loading these in, unsure which exactly are still used
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(reshape2)
library(ggthemes)
library(gapminder)
library(multcomp)
library(emmeans)
library(multcompView)
library(lmerTest)
library(scales)
library(tidyverse)
library(readxl)
library(lme4)
library(gvlma)
library(rstatix)
library(sjPlot)
library(gt)
?library(car)
library(Rmisc)
library(nlme)
library(pgirmess)
library(MuMIn)
library(sjPlot)
library(grateful)
library(cowplot)
library(kableExtra)
library(MuMIn)
library(ggpmisc)
library(bestNormalize)
library(flextable)
```

# making emmeans functions 
```{r}
# Define a 3 WAY function for year 1 summer
compute_emmeansNXS <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P*CROP, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "1", Harvest = "Summer")
  
  return(emm_df)}

# Define a 3 WAY  function for year 1 fall
compute_emmeansNXF <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P*CROP, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "1", Harvest = "Fall")
  return(emm_df)}

# Define a 3 WAY  function for year 2 Summer
compute_emmeansNYS <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P*CROP, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "2", Harvest = "Summer")
  return(emm_df)}

# Define a 3 WAY function for year 2 Fall
compute_emmeansNYF <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P*CROP, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "2", Harvest = "Fall")
  return(emm_df)}

# Define a 3 WAY function for year 3 summer
compute_emmeansNZS <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P*CROP, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "3", Harvest = "Summer")
  
  return(emm_df)}

# Define a 3 WAY  function for year 3 fall
compute_emmeansNZF <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P*CROP, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "3", Harvest = "Fall")
  return(emm_df)}



# Define a NP function for year 1 summer
compute_emmeansNXS2 <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "1", Harvest = "Summer")
  return(emm_df)}

# Define a NP  function for year 1 fall
compute_emmeansNXF2 <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "1", Harvest = "Fall")
  return(emm_df)}

# Define a NP  function for year 2 Summer
compute_emmeansNYS2 <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "2", Harvest = "Summer")
  return(emm_df)}

# Define a NP function for year 2 Fall
compute_emmeansNYF2 <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "2", Harvest = "Fall")
  return(emm_df)}

# Define a NP function for year 3 summer
compute_emmeansNZS2 <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "3", Harvest = "Summer")
  return(emm_df)}

# Define a NP  function for year 3 fall
compute_emmeansNZF2 <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "3", Harvest = "Fall")
  return(emm_df)}
```

# letters for compact letter display
```{r}
custom_letters <- c("a", "b", "c", "d", "e", "f", "g","h","i","j","k","l","m","n","o","p","q","r","s","t","u","v","w","x","y","z")  # Customize the letters as needed
```

### Estimation of Dehulled Grain Yield

The IWG grain threshability visibly varied by site, and not all grains were fully dehulled, so it was deemed necessary to estimate the true mass of dehulled grain in order to prevent poorly threshed plots from being incorrectly represented as higher yielding. To correct for this, 3-gram samples were taken from each plot’s grain yield. These samples were weighed and imaged, and the images were analyzed using the software ilastik, which visually estimated the proportion of grain still in the hull, naked grain, grain still in the spikelet, and empty hulls and spikelets. The resulting proportions were used to create an estimated dehulled grain weight for the sample, which was then extrapolated to derive an adjusted dehulled grain yield for each experimental plot (Altendorf et al., 2021)

Adjusted plot grain yield= (estimated dehulled sample weight/ sample weight)*(plot grain yield weight) 

In year 3, dehulled weight was estimated for each location by hand cleaning a subset of the samples and using those to set up a linear regression model to predict all dehulled grain weights. A linear model of $y = \beta_0 + \beta X$, where y is dehulled weight and X is the original sample weight, achieved a $R^2 > 0.9$. The resulting estimates were used to obtain predicted dehulled grain weights for each sample via the predict function. This function uses the equation : predicted value = intercept + Threshed Weights*Estimate. 

### Land Equivalent Ratio (LER)

Land Equivalent Ratio (LER) was calculated to compare the performance of intercrops to that of monocultures... Indicates a relative total forage yield advantage for intercropped plots if the TLER is greater than 1(Mead & Willey, 1980). 

Total LER: TLER= LA+LB= YA/SA + YB/SB
where LA and LB are the partial land equivalent ratio (PLER) for the individual crops. YA and YB are the yields of an individual crop within the intercropped plot, and SA and SB are the yields of an individual crop within a monoculture plot (Mead & Willey, 1980). 

Proportional LER (PrLER) was calculated for each species’ biomass yield to determine each species’ relative contribution to the total LER (Oyejola & Mead, 1982). PLERs can be compared to determine competitive effects between the species in intercrop... A PLER greater than 0.5 indicates a relative yield advantage for a single crop in intercrop compared to its yield at the same seeding rate in monoculture. The proportional partial land equivalent ratio (PrPLER) is the proportion of component crop A to the TLER and can be used to understand how much each intercropped crop contributes to the TLER. 

Proportional LER: PrPLER= LA/TLER
where LA is the partial land equivalent ratio (PLER) for an individual crops and TLER is the total land equivalent ratio for an intercropped plot. 


TLER, PLER, and PrLER were calculated using plots of the same N rate to allow for comparison in the performance of the intercropped system at different N rates (Oyejola & Mead, 1982). TLER and PrLER could not be calculated for grain yields, as IWG only represented one grain-bearing crop in the intercrop, but PLER was calculated for grain yield to allow for comparison between N rates

Grain Partial LER : the ratio of grain yield in intercrop to the grain yield in IWG monoculture at a given N rate

### Relative Yield (RY)

Grain Relative Yield : the proportion of the grain yield in intercrop at 0 kg N ha-1 to the grain yield in monoculture at a non-zero N rate

### Effects and interactions of N rate (N), cropping system (CROP), and environment (E)

Log-linear mixed-effects models with replication as a random effect (ϵ) 
log(Response variable) ~ N*E*C + ϵ
Models for each year-harvest ( Year 1 Summer, Year 1 Fall, Year 2 Summer, Year 2 Fall, Year 3 Summer, Year 3 Fall) as Summer and Fall harvests were expected to have large differences in yield, and so that the change in response variables between years could be easily captured and compared.

Response variables: Yields
- Grain yield
Response variables: LER
- PLER of grain 
- Grain Relative Yield (RY)
Cropping system (C) was not included as a fixed effect for LER, as LER values are calculated as a ratio of yield in intercropping to yield in monoculture.

Analysis of covariance (ANCOVA) was used to determine significant differences (P<0.05) between independent variables and their interactions. Estimated marginal means (EMMs) were calculated and pairwise comparisons were used to understand and rank results between independent variables. 


### Data prep for analysis 

```{r}
data<-read.csv('data/Original_Data/MasterDataSpreadsheet.csv')
```
# Rows to remove due to missing data
NY 208 s22 missing alfalfa 
MN 1122 s23 missing grain 
```{r}
# 2022 Summer NY 208 is the first row in the data table
data <- data[-1, ] # 2022 Summer NY 208
# then the new row 1 becomes the next row needing to be taken out
data <- data[-1, ] # 2023 Summer MN 1122
```
# Rename variables to match models 
```{r}
data2 <- data |> 
  separate_wider_delim(Crop, delim = " + ", 
                       names = c("first_value", "second_value"), 
                       too_few = "align_start") |> 
  mutate(C = if_else(is.na(second_value), "monoculture", "intercrop")) |> 
  mutate(CROP = case_when(
    Intercropped == "y" ~ "Intercropped",  # If intercrop is "y", set CROP to intercrop
    Monocrop == "y" & ALF == "y" ~ "Mono_ALF",  # If monoculture is "y" and alfalfa is "y", set CROP to alfalfa
    Monocrop == "y" & IWG == "y" ~ "Mono_IWG",  # If monoculture is "y" and iwg is "y", set CROP to iwg
    Monocrop == "y" ~ "NA",  # If monoculture is "y" and neither alfalfa nor iwg is "y", set CROP to NA
    TRUE ~ NA_character_  # If no condition matches, assign NA
  ))

V<-data2$first_value #Variety (IWG, Shockwave, Higest, WL)
data2$V<-as.factor(V)
N<-data2$NRate # Nitrogen Rate (0, 40, 80, 120, 160)
data2$N<-as.numeric(N)
P<-data2$Location # Location ("MN", "NY", "WI", "KS")
data2$P<-as.factor(P)
data2$Rep<-as.factor(data2$Rep) # (1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16)
data2$C<-as.factor(data2$C) # Crop (intercrop, monoculture)
data2$CROP <- as.factor(data2$CROP) # Crop (intercrop, monoculture_IWG, monoculture_Alfalfa)
```

# Grain conversion

```{r}
#need to calculate the fractions 
# data points from imaging giving proportionss
# for yr 1 and 2 there are columns with plot individual info for this
data3 <- data2%>%filter(YearCode %in% c("X", "Y"))
#hull fraction 
data3$hullNHd<-data3$hull_N/(data3$hull_N+data3$nkd_N+data3$spklt_N)
#naked seed fraction 
data3$NdkNHd<-data3$nkd_N/(data3$hull_N+data3$nkd_N+data3$spklt_N)
#spiklet fraction 
data3$SpkltNHd <- ifelse(data3$spklt_N == 0, 0, data3$spklt_N / (data3$hull_N + data3$nkd_N + data3$spklt_N))

#IGNORE (Lee's equation)
# converted grain weight using proportion information and his calibration values
#then can just plug and chug into this equation 
#data2$YldHdDH <- (1.26975580047546E-03) + (0.897057684933234 * data2$image_sample_wt_g) - ((1.07961789616701E-05) * data2$hullNHd * data2$hull_A) + ((4.61501772182347E-06) * data2$NdkNHd * data2$nkd_A) - ((2.00025159218368E-05) * ifelse(is.nan(data2$SpkltNHd), 0, data2$SpkltNHd) * ifelse(is.nan(data2$spklt_A), 0, data2$spklt_A))

#new equation from Lee
# converted grain wieghts 
data3$WhSamDH = (0.905045351733363*data3$image_sample_wt_g)-((1.10627799960595E-05)*data3$hullNHd*data3$hull_A)+((4.10249606987368E-06)*data3$NdkNHd*data3$nkd_A)-((2.01262650442053E-05)* ifelse(is.nan(data3$SpkltNHd), 0, data3$SpkltNHd) * ifelse(is.nan(data3$spklt_A), 0, data3$spklt_A)) 


#fix below to create the right proportion and save it  
#samples sent for imaging were a subset, so have to apply the conversion factor to the subsample, need to calculate up to the whole plot samples
data3$G<-((data3$WhSamDH)/(data3$image_sample_wt_g))*(data3$PlotThreshedGrainKgHa)


# Year 3 adjustments 
# need to have naked seed weights to match the adjustments made in yr 1 and yr 2
# NY yr3 was hand threshed, so looks clean as is. No need for adjustments or dehulling
# KS, WI, and MN sending to NY to dehull
## weigh a subset of these after they are threshed. then clean that subset. Find the r^2 and if good (~80) then use to estimate a clean weight for the rest of the samples
data4 <- data2%>%filter(YearCode == "Z")
data4$hullNHd <- ""
data4$NdkNHd <- ""
data4$SpkltNHd <- ""
data4$WhSamDH <- ""
data4$G <- data4$PlotThreshedGrainKgHa
data_fixed <- rbind(data3,data4)
```

# Making things different data types as needed
```{r}
data_fixed$G<-as.numeric(data_fixed$G)
data_fixed$PlotIWGDryKgHa<-as.numeric(data_fixed$PlotIWGDryKgHa)
data_fixed$PlotAlfDryKgHa<-as.numeric(data_fixed$PlotAlfDryKgHa)
data_fixed$PlotTotForageKgHa<-as.numeric(data_fixed$PlotTotForageKgHa)
data_fixed$IWGCP<-as.numeric(data_fixed$IWGCP)
data_fixed$IWGdNDF48<-as.numeric(data_fixed$IWGdNDF48)
data_fixed$IWGLignin<-as.numeric(data_fixed$IWGLignin)
data_fixed$ALFCP<-as.numeric(data_fixed$ALFCP)
data_fixed$ALFdNDF48<-as.numeric(data_fixed$ALFdNDF48)
data_fixed$ALFLignin<-as.numeric(data_fixed$ALFLignin)
data_fixed$ALFADF<-as.numeric(data_fixed$ALFADF)
data_fixed$IWGADF<-as.numeric(data_fixed$IWGADF)
data_fixed$ALFaNDF<-as.numeric(data_fixed$ALFaNDF)
data_fixed$YearCode <- as.factor(data_fixed$YearCode)
```
# Nrate data isolation
```{r}
#Just shockwave 
Nd<-data_fixed[data_fixed$first_value != "WL" & data_fixed$first_value != "Higest" ,]

Nd <- Nd %>%
  mutate(CROP = case_when(
    `Crop1` == "Shockwave" ~ "monoA",
    `Crop1` == "IWG" ~ "monoI",
    `Crop1` == "Shockwave + IWG" ~ "inter",
    TRUE ~ NA_character_  # Handle other cases if any
  ))

# MN 2024 has some Filler plots which get the NA character, but code later in this script dosn't like it. 
# So removing these here
Nd <- Nd %>%
  filter(!is.na(CROP))
```

```{r}
#Year
NdX<-Nd[Nd$YearCode == "X",]
NdY<-Nd[Nd$YearCode == "Y",]
NdZ<-Nd[Nd$YearCode == "Z",]

#REMOVE this once you get the corrected year 2 grain values in 
NdY$G<-NdY$PlotThreshedGrainKgHa

#Harvest 
NdXS<-NdX[NdX$Harvest == "Summer",]
NdXF<-NdX[NdX$Harvest == "Fall",]

NdYS<-NdY[NdY$Harvest == "Summer",]
NdYF<-NdY[NdY$Harvest == "Fall",]

NdZS<-NdZ[NdZ$Harvest == "Summer",]
NdZF<-NdZ[NdZ$Harvest == "Fall",]

#IWG vs ALF 
NdXSI<-NdXS[NdXS$Crop1 != "Shockwave",]
NdXSA<-NdXS[NdXS$Crop1 != "IWG",]

NdXFI<-NdXF[NdXF$Crop1 != "Shockwave",]
NdXFA<-NdXF[NdXF$Crop1 != "IWG",]

NdYSI<-NdYS[NdYS$Crop1 != "Shockwave" ,]
NdYSA<-NdYS[NdYS$Crop1 != "IWG",]

NdYFI<-NdYF[NdYF$Crop1 != "Shockwave",]
NdYFA<-NdYF[NdYF$Crop1 != "IWG",]

NdZSI<-NdZS[NdZS$Crop1 != "Shockwave" ,]
NdZSA<-NdZS[NdZS$Crop1 != "IWG",]

NdZFI<-NdZF[NdZF$Crop1 != "Shockwave",]
NdZFA<-NdZF[NdZF$Crop1 != "IWG",]
```

```{r}
#adding year 1 mn grain to the G column because they were actually dehulled instead of imaged for using the equation
NdXSInoMN<-NdXSI[NdXSI$Location != "MN",]
NdXSIMN<-NdXSI[NdXSI$Location == "MN",]
NdXSIMN$G<-NdXSIMN$X2023MNGrainDeHulledKgHa
NdXSIG<-rbind(NdXSInoMN, NdXSIMN)
```

```{r}
# this chunk subsets to just columns that might be used in a anslysis then combines each year

#  "Year", "YearCode", "Harvest", "Location", "Treatment", "first_value", "second_value", "Crop1", "Plot", "Intercropped", "Monocrop", "IWG", "ALF", "NRate", "Rep", "Date", "QLengthCM", "QWidthCM", "QAreaHa", "RowSpacing", "RowsSampled", "QIWGForWetG", "SIWGForWetG", "SIWGDryG", "IWGQal", "IWGDM", "PlotIWGDryG", "PlotIWGDryKG", "PlotIWGDryKgHa", "QSpikeDryG", "QThreshedGrainDryG", "PlotThreshedGrainKgHa", "QAlfForWetG", "SAlfWetG", "SAlfDryG", "AlfQual", "AlfDM", "PlotAlfDryG", "PlotAlfDryKG", "PlotAlfDryKgHa", "PlotTotForageKgHa", "QWeedsWetG", "QWeedsDryG", "IWGRFV", "IWGADF", "IWGaNDF", "ALFaNDF", "ALFRFV", "ALFADF", "ALFaNDF", "C", "CROP", "V", "N", "P", "G"


shortenXS <- NdXS[,c("Year", "YearCode", "Harvest", "Location", "Treatment", "first_value", "second_value", "Crop1", "Plot", "Intercropped", "Monocrop", "IWG", "ALF", "NRate", "Rep", "Date", "QLengthCM", "QWidthCM", "QAreaHa", "RowSpacing", "RowsSampled", "QIWGForWetG", "SIWGForWetG", "SIWGDryG", "IWGQual", "IWGDM", "PlotIWGDryG", "PlotIWGDryKG", "PlotIWGDryKgHa", "QSpikeDryG", "QThreshedGrainDryG", "PlotThreshedGrainKgHa", "QAlfForWetG", "SAlfWetG", "SAlfDryG", "AlfQual", "AlfDM", "PlotAlfDryG", "PlotAlfDryKG", "PlotAlfDryKgHa", "PlotTotForageKgHa", "QWeedsWetG", "QWeedsDryG", "IWGADF", "IWGaNDF", "ALFADF", "ALFaNDF", "C", "CROP", "V", "N", "P", "G")]

shortenXF <- NdXF[,c("Year", "YearCode", "Harvest", "Location", "Treatment", "first_value", "second_value", "Crop1", "Plot", "Intercropped", "Monocrop", "IWG", "ALF", "NRate", "Rep", "Date", "QLengthCM", "QWidthCM", "QAreaHa", "RowSpacing", "RowsSampled", "QIWGForWetG", "SIWGForWetG", "SIWGDryG", "IWGQual", "IWGDM", "PlotIWGDryG", "PlotIWGDryKG", "PlotIWGDryKgHa", "QSpikeDryG", "QThreshedGrainDryG", "PlotThreshedGrainKgHa", "QAlfForWetG", "SAlfWetG", "SAlfDryG", "AlfQual", "AlfDM", "PlotAlfDryG", "PlotAlfDryKG", "PlotAlfDryKgHa", "PlotTotForageKgHa", "QWeedsWetG", "QWeedsDryG", "IWGADF", "IWGaNDF", "ALFADF", "ALFaNDF", "C", "CROP", "V", "N", "P", "G")]

shortenYS <- NdYS[,c("Year", "YearCode", "Harvest", "Location", "Treatment", "first_value", "second_value", "Crop1", "Plot", "Intercropped", "Monocrop", "IWG", "ALF", "NRate", "Rep", "Date", "QLengthCM", "QWidthCM", "QAreaHa", "RowSpacing", "RowsSampled", "QIWGForWetG", "SIWGForWetG", "SIWGDryG", "IWGQual", "IWGDM", "PlotIWGDryG", "PlotIWGDryKG", "PlotIWGDryKgHa", "QSpikeDryG", "QThreshedGrainDryG", "PlotThreshedGrainKgHa", "QAlfForWetG", "SAlfWetG", "SAlfDryG", "AlfQual", "AlfDM", "PlotAlfDryG", "PlotAlfDryKG", "PlotAlfDryKgHa", "PlotTotForageKgHa", "QWeedsWetG", "QWeedsDryG", "IWGADF", "IWGaNDF", "ALFADF", "ALFaNDF", "C", "CROP", "V", "N", "P", "G")]

shortenYF <- NdYF[,c("Year", "YearCode", "Harvest", "Location", "Treatment", "first_value", "second_value", "Crop1", "Plot", "Intercropped", "Monocrop", "IWG", "ALF", "NRate", "Rep", "Date", "QLengthCM", "QWidthCM", "QAreaHa", "RowSpacing", "RowsSampled", "QIWGForWetG", "SIWGForWetG", "SIWGDryG", "IWGQual", "IWGDM", "PlotIWGDryG", "PlotIWGDryKG", "PlotIWGDryKgHa", "QSpikeDryG", "QThreshedGrainDryG", "PlotThreshedGrainKgHa", "QAlfForWetG", "SAlfWetG", "SAlfDryG", "AlfQual", "AlfDM", "PlotAlfDryG", "PlotAlfDryKG", "PlotAlfDryKgHa", "PlotTotForageKgHa", "QWeedsWetG", "QWeedsDryG", "IWGADF", "IWGaNDF", "ALFADF", "ALFaNDF", "C", "CROP", "V", "N", "P", "G")]

shortenZS <- NdZS[,c("Year", "YearCode", "Harvest", "Location", "Treatment", "first_value", "second_value", "Crop1", "Plot", "Intercropped", "Monocrop", "IWG", "ALF", "NRate", "Rep", "Date", "QLengthCM", "QWidthCM", "QAreaHa", "RowSpacing", "RowsSampled", "QIWGForWetG", "SIWGForWetG", "SIWGDryG", "IWGQual", "IWGDM", "PlotIWGDryG", "PlotIWGDryKG", "PlotIWGDryKgHa", "QSpikeDryG", "QThreshedGrainDryG", "PlotThreshedGrainKgHa", "QAlfForWetG", "SAlfWetG", "SAlfDryG", "AlfQual", "AlfDM", "PlotAlfDryG", "PlotAlfDryKG", "PlotAlfDryKgHa", "PlotTotForageKgHa", "QWeedsWetG", "QWeedsDryG", "IWGADF", "IWGaNDF", "ALFADF", "ALFaNDF", "C", "CROP", "V", "N", "P", "G")]

shortenZF <- NdZF[,c("Year", "YearCode", "Harvest", "Location", "Treatment", "first_value", "second_value", "Crop1", "Plot", "Intercropped", "Monocrop", "IWG", "ALF", "NRate", "Rep", "Date", "QLengthCM", "QWidthCM", "QAreaHa", "RowSpacing", "RowsSampled", "QIWGForWetG", "SIWGForWetG", "SIWGDryG", "IWGQual", "IWGDM", "PlotIWGDryG", "PlotIWGDryKG", "PlotIWGDryKgHa", "QSpikeDryG", "QThreshedGrainDryG", "PlotThreshedGrainKgHa", "QAlfForWetG", "SAlfWetG", "SAlfDryG", "AlfQual", "AlfDM", "PlotAlfDryG", "PlotAlfDryKG", "PlotAlfDryKgHa", "PlotTotForageKgHa", "QWeedsWetG", "QWeedsDryG", "IWGADF", "IWGaNDF", "ALFADF", "ALFaNDF", "C", "CROP", "V", "N", "P", "G")]

newX <- rbind(shortenXS, shortenXF)
newY <- rbind(shortenYS, shortenYF)
newZ <- rbind(shortenZS, shortenZF)
newXY <- rbind(newX, newY)
forage_data <- rbind(newXY, newZ)

newXYS <- rbind(shortenXS, shortenYS)
forage_data_summer <- rbind(newXYS, shortenZS)

newXYF <- rbind(shortenXF, shortenYF)
forage_data_fall <- rbind(newXYF, shortenZF)
```

# Optional data viewing
```{r}
table(forage_data$Rep, forage_data$P) # make sure replicates are unique to a location
table(forage_data$P, forage_data$Rep)  # make sure replicates are unique to a location
table(forage_data$Plot, forage_data$P) # look to see if plot ids are unique to a location (they arn't)
with(subset(forage_data, !is.na(G)), table(P, Year)) # look at which years have data and how many data points
with(subset(forage_data, !is.na(G)), table(CROP, N, P, Year)) # for each site-year, look to see if and how many data points exist for each N rate
table(forage_data$Plot, forage_data$P) # look at each plot name and if and how many data points there are for that plot at each site
forage_data %>% group_by(P,Rep,Plot)%>%count()%>%View()# makes viewable data frame for each plot within a rep within a location and shows how many data points exisit for that specific plot
```


## Total Forage Yield 
# anova
```{r}
# want N to be numeric
is.numeric(forage_data$N)
# want P, CROP, and Year to be factors
is.factor(forage_data$P)
is.factor(forage_data$CROP)
is.character(forage_data$CROP)
is.factor(forage_data$YearCode)
is.character(forage_data$YearCode)
# forage_data$YearCode <- as.factor(forage_data$YearCode)
# Rep and Plot should also be factors
is.factor(forage_data$Rep)
is.factor(forage_data$Plot)
# forage_data$Plot <- as.character(forage_data$Plot)
forage_data$YearHarvest <- paste0(forage_data$YearCode, forage_data$Harvest)
# forage_data$YearHarvest <- as.factor(forage_data$YearHarvest)

# Linear Model
modTF <- lmer(PlotTotForageKgHa~N*P*CROP*YearHarvest + (1|Rep:P)+(1|Plot:Rep:P), data=forage_data)
summary(modTF)
# singularity : (look at random effects) variance on plot level is low compared to residual or rep so plot-to-plot var is essentially zero; stats consulting said this is okay to proceed
hist(residuals(modTF)) # check normality; look for normal distribution, ideally not too narrow
plot(predict(modTF),residuals(modTF)) # check for homoscedasisity; each point distribution, no fan shape
modTF_resid<-resid(modTF)
qqnorm(modTF_resid)
qqline(modTF_resid)
plot(modTF_resid)

modTFlog <- lmer(log(PlotTotForageKgHa+0.00001)~N*P*CROP*YearHarvest + (1|Rep:P)+(1|Plot:Rep:P), data=forage_data)
summary(modTFlog)
hist(residuals(modTFlog)) # check normality; look for normal distribution, ideally not too narrow
plot(predict(modTFlog),residuals(modTFlog)) # check for homoscedasisity; each point distribution, no fan shape
modTFlog_resid<-resid(modTFlog)
qqnorm(modTFlog_resid)
qqline(modTFlog_resid)
plot(modTFlog_resid)

modTFsqrt <- lmer(sqrt(PlotTotForageKgHa)~N*P*CROP*YearHarvest + (1|Rep:P)+(1|Plot:Rep:P), data=forage_data)
summary(modTFsqrt)
hist(residuals(modTFsqrt)) # check normality; look for normal distribution, ideally not too narrow
plot(predict(modTFsqrt),residuals(modTFsqrt)) # check for homoscedasisity; each point distribution, no fan shape
modTFsqrt_resid<-resid(modTFsqrt)
qqnorm(modTFsqrt_resid)
qqline(modTFsqrt_resid)
plot(modTFsqrt_resid)



anova(modTFsqrt) # print anova results
emmeans(modTFsqrt, ~N*P*CROP*YearCode, cov.reduce=FALSE) # estimated marginal means
emtrends(modTFsqrt, ~N+P+YearCode, var="N", infer=TRUE) # slope different than zero
emtrends(modTFsqrt, pairwise~YearCode|CROP+P, var="N", infer=TRUE) # slope different by cropP
```

## Total Forage Summer
# anova
```{r}
# want N to be numeric
is.numeric(forage_data_summer$N)
# want P, CROP, and Year to be factors
is.factor(forage_data_summer$P)
is.factor(forage_data_summer$CROP)
is.character(forage_data_summer$CROP)
is.factor(forage_data_summer$YearCode)
is.character(forage_data_summer$YearCode)
# forage_data_summer$YearCode <- as.factor(forage_data_summer$YearCode)
# Rep and Plot should also be factors
is.factor(forage_data_summer$Rep)
is.factor(forage_data_summer$Plot)
# forage_data_summer$Plot <- as.character(forage_data_summer$Plot)

# Linear Model
modTFS <- lmer(PlotTotForageKgHa~N*P*CROP*YearCode + (1|Rep:P)+(1|Plot:Rep:P), data=forage_data_summer)
summary(modTF)
# singularity : (look at random effects) variance on plot level is low compared to residual or rep so plot-to-plot var is essentially zero; stats consulting said this is okay to proceed
hist(residuals(modTFS)) # check normality; look for normal distribution, ideally not too narrow
plot(predict(modTFS),residuals(modTFS)) # check for homoscedasisity; each point distribution, no fan shape
modTFS_resid<-resid(modTFS)
qqnorm(modTFS_resid)
qqline(modTFS_resid)
plot(modTFS_resid)

modTFSlog <- lmer(log(PlotTotForageKgHa+0.00001)~N*P*CROP*YearCode + (1|Rep:P)+(1|Plot:Rep:P), data=forage_data_summer)
summary(modTFSlog)
hist(residuals(modTFSlog)) # check normality; look for normal distribution, ideally not too narrow
plot(predict(modTFSlog),residuals(modTFSlog)) # check for homoscedasisity; each point distribution, no fan shape
modTFSlog_resid<-resid(modTFSlog)
qqnorm(modTFSlog_resid)
qqline(modTFSlog_resid)
plot(modTFSlog_resid)

modTFSsqrt <- lmer(sqrt(PlotTotForageKgHa)~N*P*CROP*YearCode + (1|Rep:P)+(1|Plot:Rep:P), data=forage_data_summer)
summary(modTFSsqrt)
hist(residuals(modTFSsqrt)) # check normality; look for normal distribution, ideally not too narrow
plot(predict(modTFSsqrt),residuals(modTFSsqrt)) # check for homoscedasisity; each point distribution, no fan shape
modTFSsqrt_resid<-resid(modTFSsqrt)
qqnorm(modTFSsqrt_resid)
qqline(modTFSsqrt_resid)
plot(modTFSsqrt_resid)




anova(modTFS) # print anova results
emmeans(modTFS, ~N*P*CROP*YearCode, cov.reduce=FALSE) # estimated marginal means
emtrends(modTFS, ~N+P+YearCode, var="N", infer=TRUE) # slope different than zero
emtrends(modTFS, pairwise~YearCode|CROP+P, var="N", infer=TRUE) # slope different by cropP
  # make this a box and whisker plot; with pairwise comparison on the figure
```
# Two quick figures for fun (not cleaned up)
```{r}
ggplot(forage_data_summer, aes(x=N, y=PlotTotForageKgHa, color=YearCode))+geom_point()+facet_grid(CROP~P)+geom_smooth(method="lm", se=FALSE)

emmip(modTFS, YearCode~N | CROP*P, cov.reduce=FALSE, CIs = TRUE)+ #model predicted vales
    scale_x_continuous(breaks = c(0, 40, 80, 120, 160), labels = c("0", "40", "80", "120", "160"))
#emmip(modTFS, N~YearCode | CROP*P, cov.reduce=FALSE, CIs = TRUE) #model predicted vales (I don't like this orientation)
```
# percent change in grain yield per unit increase in nitrogen
```{r}
# percent change in grain yield per unit increase in nitrogen
# (P+CROP) and (P+Year)
# pvalue is showing slopes that are signifcanly different than zero (significant percent change in yield with N)

# N*P*CROP
# N slopes
emtrends_result<-emtrends(modTFS,~ P+CROP, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
  emtrends_df$plvl <-
    ifelse(emtrends_df$p.value == 0.05, ".",
    ifelse(emtrends_df$p.value < 0.05  & emtrends_df$p.value >= 0.01, "*",
    ifelse(emtrends_df$p.value < 0.01  & emtrends_df$p.value >= 0.001, "**",
    ifelse(emtrends_df$p.value < 0.001, "***", "")))) # slope different than zero
# Intercepts at N=0
emmeans_results<-emmeans(modTFS, ~P+CROP, at=list(N=0)) 
emmeans_df <- as.data.frame(emmeans_results)
# Merge slopes and intercepts
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("P", "CROP")) %>%
  select(P, CROP, emmean, N.trend, SE.x, plvl) 
View(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
# Create a new data frame with the calculated column
new_df <- merged_df %>%
    mutate(equation = sprintf("=%.2f+(%.4fN)", emmean, N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", N.trend / emmean * 100))%>%
    select(-emmean, -N.trend) 
sorted_df <- new_df %>%
  arrange(P, CROP)
View(sorted_df)

# N:Location:Year
# N slopes
emtrends_result<-emtrends(modTFS,~ P+YearCode, var= "N", infer=TRUE) 
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
  emtrends_df$plvl <-
    ifelse(emtrends_df$p.value == 0.05, ".",
    ifelse(emtrends_df$p.value < 0.05  & emtrends_df$p.value >= 0.01, "*",
    ifelse(emtrends_df$p.value < 0.01  & emtrends_df$p.value >= 0.001, "**",
    ifelse(emtrends_df$p.value < 0.001, "***", "")))) # slope different than zero
# Intercepts at N=0
emmeans_results<-emmeans(modTFS, ~P+YearCode, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
# Merge slopes and intercepts
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("P", "YearCode")) %>%
  select(P, YearCode, emmean, N.trend, SE.x, plvl) 
View(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
# Create a new data frame with the calculated column
new_df <- merged_df %>%
    mutate(equation = sprintf("=%.2f+(%.4fN)", emmean, N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", N.trend / emmean * 100))%>%
    select(-emmean, -N.trend) 
sorted_df <- new_df %>%
  arrange(P, YearCode)
View(sorted_df)
```
# relationship of location, cropping system, and year
```{r}
emtrends(modTFS, pairwise~YearCode|CROP+P, var="N", infer=TRUE) # slope different by cropP
emmeans(modTFS, ~N*P*CROP*YearCode, cov.reduce=FALSE) # estimated marginal means
emmeans(modTFS, ~P*CROP*YearCode, cov.reduce=FALSE) # estimated marginal means

# box and wisker plot with post-hoc compact letter display for sig differences?



#NdYSf$predicted <- predict(modNTCPYS, newdata = NdYSf, re.form = NA)
TFSemms <- emmeans(modTFS, ~ P*CROP*YearCode, type = "response") # Obtain estimated marginal means
emms_df <- as.data.frame(TFSemms)
cld_dataTFS <- cld(TFSemms, Letters=custom_letters)
cld_df <-as.data.frame(cld_dataTFS)
merged_df <- merge(emms_df, cld_df,by = c("P", "CROP", "YearCode"))
# custom cld position 
merged_df <- merged_df %>%
  left_join(
    forage_data_summer %>%
      group_by(P, CROP, YearCode) %>%
      dplyr::summarise(label_y = max(PlotTotForageKgHa, na.rm = TRUE) * 0.9, .groups = "drop"),
    by = c("P", "CROP", "YearCode")
  )
# Custom X-axis labels
#xlabels <- c("X", "Monoculture Alfalfa", "Monoculture IWG")
TFS_CPY <- ggplot(forage_data_summer, aes(x = YearCode, y = PlotTotForageKgHa, colour= CROP)) +
  geom_boxplot(position = position_dodge(width = 0.8)) + # blank
#  geom_text(data = merged_df, aes(x = YearCode, y = emmean.x, label = .group), 
            #position = position_dodge(width = 0.75),
#            color = "black", vjust = 0, hjust = 0, size=6)+ 
  
  geom_text(data = merged_df, aes(x = YearCode, y = label_y, label = .group, colour = CROP, group = CROP),
            position = position_dodge(width = 0.8), size = 6, show.legend = FALSE)+

  facet_wrap(~P, scales = "free", ncol = 2) +
  scale_colour_manual(values = c(inter = "#DDCC77", monoA = "#332288", monoI = "#661100")) +
  labs(x = "Year", y = "Total Forage (kg/ha)")+ #title=""
  theme(axis.text.y=element_text(size=14), #change font size of axis text
        axis.text.x=element_text(size=16),
        axis.title=element_text(size=22))
TFS_CPY
# 1500x1200
```

## Total Forage Fall
# anova
```{r}
# remove rows where the total forage was 0
forage_data_fall_2 <- subset(forage_data_fall, PlotTotForageKgHa != 0|is.na(PlotTotForageKgHa)) 
# MN Year 2 Fall plot 1210 value for total forage is extreme outlier (12091.732 kg/ha when next highest is 3452.477); driven by much higher iwg forage 
forage_data_fall_2 <- forage_data_fall_2 %>%
  dplyr::filter(!(YearCode == "Y" &
           Location == "MN" &
           Plot == "1210"))

# want N to be numeric
is.numeric(forage_data_fall_2$N)
# want P, CROP, and Year to be factors
is.factor(forage_data_fall_2$P)
is.factor(forage_data_fall_2$CROP)
# forage_data_fall_2$CROP <- as.factor(forage_data_fall_2$CROP)
is.factor(forage_data_fall_2$YearCode)
# forage_data_fall_2$YearCode <- as.factor(forage_data_fall_2$YearCode)
# Rep and Plot should also be factors
is.factor(forage_data_fall_2$Rep)
is.factor(forage_data_fall_2$Plot)
# forage_data_fall_2$Plot <- as.character(forage_data_fall_2$Plot)


# Linear Model
modTFF <- lmer(PlotTotForageKgHa~N*P*CROP*YearCode + (1|Rep:P)+(1|Plot:Rep:P), data=forage_data_fall_2)
summary(modTFF)
hist(residuals(modTFF)) # check normality; look for normal distribution, ideally not too narrow
plot(predict(modTFF),residuals(modTFF)) # check for homoscedasisity; each point distribution, no fan shape
modTFF_resid<-resid(modTFF)
qqnorm(modTFF_resid)
qqline(modTFF_resid)
plot(modTFF_resid)


modTFFsqrt <- lmer(sqrt(PlotTotForageKgHa)~N*P*CROP*YearCode + (1|Rep:P)+(1|Plot:Rep:P), data=forage_data_fall)
summary(modTFFsqrt)
hist(residuals(modTFFsqrt)) # check normality; look for normal distribution, ideally not too narrow
plot(predict(modTFFsqrt),residuals(modTFFsqrt)) # check for homoscedasisity; each point distribution, no fan shape
modTFFsqrt_resid<-resid(modTFFsqrt)
qqnorm(modTFFsqrt_resid)
qqline(modTFFsqrt_resid)
plot(modTFFsqrt_resid)


anova(modTFF) # print anova results
emmeans(modTFF, ~N*P*CROP*YearCode, cov.reduce=FALSE) # estimated marginal means
emtrends(modTFF, ~N+P+YearCode, var="N", infer=TRUE) # slope different than zero
emtrends(modTFF, pairwise~YearCode|CROP+P, var="N", infer=TRUE) # slope different by cropP
```
# relationship of location, cropping system, and year
```{r}
emtrends(modTFF, pairwise~YearCode|CROP+P, var="N", infer=TRUE) # slope different by cropP
emmeans(modTFF, ~N*P*CROP*YearCode, cov.reduce=FALSE) # estimated marginal means
emmeans(modTFF, ~P*CROP*YearCode, cov.reduce=FALSE) # estimated marginal means

# box and wisker plot with post-hoc compact letter display for sig differences?

TFFemms <- emmeans(modTFF, ~ P*CROP*YearCode, type = "response") # Obtain estimated marginal means
emmsTFF_df <- as.data.frame(TFFemms)
cld_dataTFF <- cld(TFFemms, Letters=custom_letters)
cldTFF_df <-as.data.frame(cld_dataTFF)
mergedTFF_df <- merge(emmsTFF_df, cldTFF_df,by = c("P", "CROP", "YearCode"))
# custom cld position 
mergedTFF_df <- mergedTFF_df %>%
  left_join(
    forage_data_fall_2 %>%
      group_by(P, CROP, YearCode) %>%
      dplyr::summarise(label_y = max(PlotTotForageKgHa, na.rm = TRUE) * 0.9, .groups = "drop"),
    by = c("P", "CROP", "YearCode")
  )
# Custom X-axis labels
TFF_CPY <- ggplot(forage_data_fall_2, aes(x = YearCode, y = PlotTotForageKgHa, colour= CROP)) +
  geom_boxplot(position = position_dodge(width = 0.8)) + # blank
  geom_text(data = mergedTFF_df, aes(x = YearCode, y = label_y, label = .group, colour = CROP, group = CROP),
            position = position_dodge(width = 0.8), size = 6, show.legend = FALSE)+
  facet_wrap(~P, scales = "free", ncol = 2) +
  scale_colour_manual(values = c(inter = "#DDCC77", monoA = "#332288", monoI = "#661100")) +
  labs(x = "Year", y = "Total Forage (kg/ha)")+ #title=""
  theme(axis.text.y=element_text(size=14), #change font size of axis text
        axis.text.x=element_text(size=16),
        axis.title=element_text(size=22))
TFF_CPY
# 1500x1200
```

## Alfalfa Forage Summer
# anova
```{r}
# want N to be numeric
is.numeric(forage_data_summer$N)
# want P, CROP, and Year to be factors
is.factor(forage_data_summer$P)
is.factor(forage_data_summer$CROP)
is.character(forage_data_summer$CROP)
is.factor(forage_data_summer$YearCode)
is.character(forage_data_summer$YearCode)
# forage_data_summer$YearCode <- as.factor(forage_data_summer$YearCode)
# Rep and Plot should also be factors
is.factor(forage_data_summer$Rep)
is.factor(forage_data_summer$Plot)
# forage_data_summer$Plot <- as.character(forage_data_summer$Plot)

# Linear Model
modAFS <- lmer(PlotAlfDryKgHa~N*P*CROP*YearCode + (1|Rep:P)+(1|Plot:Rep:P), data=forage_data_summer)
summary(modAFS)
hist(residuals(modAFS)) # check normality; look for normal distribution, ideally not too narrow
plot(predict(modAFS),residuals(modAFS)) # check for homoscedasisity; each point distribution, no fan shape
modAFS_resid<-resid(modAFS)
qqnorm(modAFS_resid)
qqline(modAFS_resid)
plot(modAFS_resid)

anova(modAFS) # print anova results
emmeans(modAFS, ~N*P*CROP*YearCode, cov.reduce=FALSE) # estimated marginal means
emtrends(modAFS, ~N+P+YearCode, var="N", infer=TRUE) # slope different than zero
emtrends(modAFS, pairwise~YearCode|CROP+P, var="N", infer=TRUE) # slope different by cropP
```
# Two quick figures for fun (not cleaned up)
```{r}
ggplot(forage_data_summer, aes(x=N, y=PlotAlfDryKgHa, color=YearCode))+geom_point()+facet_grid(CROP~P)+geom_smooth(method="lm", se=FALSE)

emmip(modAFS, YearCode~N | CROP*P, cov.reduce=FALSE, CIs = TRUE)+ #model predicted vales
    scale_x_continuous(breaks = c(0, 40, 80, 120, 160), labels = c("0", "40", "80", "120", "160"))
#emmip(modTFS, N~YearCode | CROP*P, cov.reduce=FALSE, CIs = TRUE) #model predicted vales (I don't like this orientation)
```
# percent change in grain yield per unit increase in nitrogen
```{r}
# percent change in grain yield per unit increase in nitrogen
# (P+CROP) and (P+Year)
# pvalue is showing slopes that are signifcanly different than zero (significant percent change in yield with N)

# N*P*Year
# N slopes
emtrends_result<-emtrends(modAFS,~ P+YearCode, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
  emtrends_df$plvl <-
    ifelse(emtrends_df$p.value == 0.05, ".",
    ifelse(emtrends_df$p.value < 0.05  & emtrends_df$p.value >= 0.01, "*",
    ifelse(emtrends_df$p.value < 0.01  & emtrends_df$p.value >= 0.001, "**",
    ifelse(emtrends_df$p.value < 0.001, "***", "")))) # slope different than zero
# Intercepts at N=0
emmeans_results<-emmeans(modAFS, ~P+YearCode, at=list(N=0)) 
emmeans_df <- as.data.frame(emmeans_results)
# Merge slopes and intercepts
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("P", "YearCode")) %>%
  select(P, YearCode, emmean, N.trend, SE.x, plvl) 
View(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
# Create a new data frame with the calculated column
new_df <- merged_df %>%
    mutate(equation = sprintf("=%.2f+(%.4fN)", emmean, N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", N.trend / emmean * 100))%>%
    select(-emmean, -N.trend) 
sorted_df <- new_df %>%
  arrange(P, YearCode)
View(sorted_df)
```
# relationship of location, cropping system, and year
```{r}
emtrends(modAFS, pairwise~YearCode|CROP+P, var="N", infer=TRUE) # slope different by cropP
emmeans(modAFS, ~N*P*CROP*YearCode, cov.reduce=FALSE) # estimated marginal means
emmeans(modAFS, ~P*CROP*YearCode, cov.reduce=FALSE) # estimated marginal means

# box and wisker plot with post-hoc compact letter display for sig differences?


AFSemms <- emmeans(modAFS, ~ P*CROP*YearCode, type = "response") # Obtain estimated marginal means
emmsAFS_df <- as.data.frame(AFSemms)
cld_dataAFS <- cld(AFSemms, Letters=custom_letters)
cldAFS_df <-as.data.frame(cld_dataAFS)
mergedAFS_df <- merge(emmsAFS_df, cldAFS_df,by = c("P", "CROP", "YearCode"))
# custom cld position 
mergedAFS_df <- mergedAFS_df %>%
  left_join(
    forage_data_summer %>%
      group_by(P, CROP, YearCode) %>%
      dplyr::summarise(label_y = if (all(is.na(PlotAlfDryKgHa))) {NA_real_} else {max(PlotAlfDryKgHa, na.rm = TRUE) * 0.9}, .groups = "drop"),
    by = c("P", "CROP", "YearCode")
  )
# Custom X-axis labels
AFS_CPY <- ggplot(forage_data_summer, aes(x = YearCode, y = PlotAlfDryKgHa, colour= CROP)) +
  geom_boxplot(position = position_dodge(width = 0.8)) + # blank
  geom_text(data = mergedAFS_df, aes(x = YearCode, y = label_y, label = .group, colour = CROP, group = CROP),
            position = position_dodge(width = 0.8), size = 6, show.legend = FALSE)+
  facet_wrap(~P, scales = "free", ncol = 2) +
  scale_colour_manual(values = c(inter = "#DDCC77", monoA = "#332288", monoI = "#661100")) +
  labs(x = "Year", y = "Alfalfa Forage (kg/ha)")+ #title=""
  theme(axis.text.y=element_text(size=14), #change font size of axis text
        axis.text.x=element_text(size=16),
        axis.title=element_text(size=22))
AFS_CPY
# 1500x1200
```

## Alfalfa Forage Fall
# anova
```{r}
# want N to be numeric
is.numeric(forage_data_fall$N)
# want P, CROP, and Year to be factors
is.factor(forage_data_fall$P)
is.factor(forage_data_fall$CROP)
# forage_data_fall$CROP <- as.factor(forage_data_fall$CROP)
is.factor(forage_data_fall$YearCode)
# forage_data_fall$YearCode <- as.factor(forage_data_fall$YearCode)
# Rep and Plot should also be factors
is.factor(forage_data_fall$Rep)
is.factor(forage_data_fall$Plot)
# forage_data_fall$Plot <- as.character(forage_data_fall$Plot)

# Linear Model
modAFF <- lmer(PlotAlfDryKgHa~N*P*CROP*YearCode + (1|Rep:P)+(1|Plot:Rep:P), data=forage_data_fall)
summary(modAFF)
hist(residuals(modAFF)) # check normality; look for normal distribution, ideally not too narrow
plot(predict(modAFF),residuals(modAFF)) # check for homoscedasisity; each point distribution, no fan shape
modAFF_resid<-resid(modAFF)
qqnorm(modAFF_resid)
qqline(modAFF_resid)
plot(modAFF_resid)

anova(modAFF) # print anova results
emmeans(modAFF, ~N*P*CROP*YearCode, cov.reduce=FALSE) # estimated marginal means
emtrends(modAFF, ~N+P+YearCode, var="N", infer=TRUE) # slope different than zero
emtrends(modAFF, pairwise~YearCode|CROP+P, var="N", infer=TRUE) # slope different by cropP
```

## IWG Forage Summer
# anova
```{r}
# want N to be numeric
is.numeric(forage_data_summer$N)
# want P, CROP, and Year to be factors
is.factor(forage_data_summer$P)
is.factor(forage_data_summer$CROP)
# forage_data_summer$CROP <- as.factor(forage_data_summer$CROP)
is.factor(forage_data_summer$YearCode)
# forage_data_summer$YearCode <- as.factor(forage_data_summer$YearCode)
# Rep and Plot should also be factors
is.factor(forage_data_summer$Rep)
is.factor(forage_data_summer$Plot)
# forage_data_summer$Plot <- as.character(forage_data_summer$Plot)

# Linear Model
modIFS <- lmer(PlotIWGDryKgHa~N*P*CROP*YearCode + (1|Rep:P)+(1|Plot:Rep:P), data=forage_data_summer)
summary(modIFS)
hist(residuals(modIFS)) # check normality; look for normal distribution, ideally not too narrow
plot(predict(modIFS),residuals(modIFS)) # check for homoscedasisity; each point distribution, no fan shape
modIFS_resid<-resid(modIFS)
qqnorm(modIFS_resid)
qqline(modIFS_resid)
plot(modIFS_resid)

anova(modIFS) # print anova results
emmeans(modIFS, ~N*P*CROP*YearCode, cov.reduce=FALSE) # estimated marginal means
emtrends(modIFS, ~N+P+YearCode, var="N", infer=TRUE) # slope different than zero
emtrends(modIFS, pairwise~YearCode|CROP+P, var="N", infer=TRUE) # slope different by cropP
```
# Two quick figures for fun (not cleaned up)
```{r}
ggplot(forage_data_summer, aes(x=N, y=PlotIWGDryKgHa, color=YearCode))+geom_point()+facet_grid(CROP~P)+geom_smooth(method="lm", se=FALSE)

emmip(modIFS, YearCode~N | CROP*P, cov.reduce=FALSE, CIs = TRUE)+ #model predicted vales
    scale_x_continuous(breaks = c(0, 40, 80, 120, 160), labels = c("0", "40", "80", "120", "160"))
#emmip(modTFS, N~YearCode | CROP*P, cov.reduce=FALSE, CIs = TRUE) #model predicted vales (I don't like this orientation)
```
# percent change in grain yield per unit increase in nitrogen
```{r}
# percent change in grain yield per unit increase in nitrogen
# (P+CROP) and (P+Year)
# pvalue is showing slopes that are signifcanly different than zero (significant percent change in yield with N)

# N*P*Year
# N slopes
emtrends_result<-emtrends(modIFS,~ P+YearCode, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
  emtrends_df$plvl <-
    ifelse(emtrends_df$p.value == 0.05, ".",
    ifelse(emtrends_df$p.value < 0.05  & emtrends_df$p.value >= 0.01, "*",
    ifelse(emtrends_df$p.value < 0.01  & emtrends_df$p.value >= 0.001, "**",
    ifelse(emtrends_df$p.value < 0.001, "***", "")))) # slope different than zero
# Intercepts at N=0
emmeans_results<-emmeans(modIFS, ~P+YearCode, at=list(N=0)) 
emmeans_df <- as.data.frame(emmeans_results)
# Merge slopes and intercepts
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("P", "YearCode")) %>%
  select(P, YearCode, emmean, N.trend, SE.x, plvl) 
View(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
# Create a new data frame with the calculated column
new_df <- merged_df %>%
    mutate(equation = sprintf("=%.2f+(%.4fN)", emmean, N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", N.trend / emmean * 100))%>%
    select(-emmean, -N.trend) 
sorted_df <- new_df %>%
  arrange(P, YearCode)
View(sorted_df)
```
# relationship of location, cropping system, and year
```{r}
emtrends(modIFS, pairwise~YearCode|CROP+P, var="N", infer=TRUE) # slope different by cropP
emmeans(modIFS, ~N*P*CROP*YearCode, cov.reduce=FALSE) # estimated marginal means
emmeans(modIFS, ~P*CROP*YearCode, cov.reduce=FALSE) # estimated marginal means

# box and wisker plot with post-hoc compact letter display for sig differences?


IFSemms <- emmeans(modIFS, ~ P*CROP*YearCode, type = "response") # Obtain estimated marginal means
emmsIFS_df <- as.data.frame(IFSemms)
cld_dataIFS <- cld(IFSemms, Letters=custom_letters)
cldIFS_df <-as.data.frame(cld_dataIFS)
mergedIFS_df <- merge(emmsIFS_df, cldIFS_df,by = c("P", "CROP", "YearCode"))
# custom cld position 
mergedIFS_df <- mergedIFS_df %>%
  left_join(
    forage_data_summer %>%
      group_by(P, CROP, YearCode) %>%
      dplyr::summarise(label_y = if (all(is.na(PlotIWGDryKgHa))) {NA_real_} else {max(PlotIWGDryKgHa, na.rm = TRUE) * 0.9}, .groups = "drop"),
    by = c("P", "CROP", "YearCode")
  )
# Custom X-axis labels
IFS_CPY <- ggplot(forage_data_summer, aes(x = YearCode, y = PlotIWGDryKgHa, colour= CROP)) +
  geom_boxplot(position = position_dodge(width = 0.8)) + # blank
  geom_text(data = mergedIFS_df, aes(x = YearCode, y = label_y, label = .group, colour = CROP, group = CROP),
            position = position_dodge(width = 0.8), size = 6, show.legend = FALSE)+
  facet_wrap(~P, scales = "free", ncol = 2) +
  scale_colour_manual(values = c(inter = "#DDCC77", monoA = "#332288", monoI = "#661100")) +
  labs(x = "Year", y = "IWG Forage (kg/ha)")+ #title=""
  theme(axis.text.y=element_text(size=14), #change font size of axis text
        axis.text.x=element_text(size=16),
        axis.title=element_text(size=22))
IFS_CPY
# 1500x1200
```

## IWG Forage Fall
# anova
```{r}
# remove rows where the total forage was 0
forage_data_fall_2 <- subset(forage_data_fall, PlotTotForageKgHa != 0|is.na(PlotTotForageKgHa)) 
# MN Year 2 Fall plot 1210 value for total forage is extreme outlier (12091.732 kg/ha when next highest is 3452.477); driven by much higher iwg forage 
forage_data_fall_2 <- forage_data_fall_2 %>%
  dplyr::filter(!(YearCode == "Y" &
           Location == "MN" &
           Plot == "1210"))

# want N to be numeric
is.numeric(forage_data_fall$N)
# want P, CROP, and Year to be factors
is.factor(forage_data_fall$P)
is.factor(forage_data_fall$CROP)
# forage_data_fall$CROP <- as.factor(forage_data_fall$CROP)
is.factor(forage_data_fall$YearCode)
# forage_data_fall$YearCode <- as.factor(forage_data_fall$YearCode)
# Rep and Plot should also be factors
is.factor(forage_data_fall$Rep)
is.factor(forage_data_fall$Plot)
# forage_data_fall$Plot <- as.character(forage_data_fall$Plot)

# Linear Model
modIFF <- lmer(PlotIWGDryKgHa~N*P*CROP*YearCode + (1|Rep:P)+(1|Plot:Rep:P), data=forage_data_fall_2)
summary(modIFF)
hist(residuals(modIFF)) # check normality; look for normal distribution, ideally not too narrow
plot(predict(modIFF),residuals(modIFF)) # check for homoscedasisity; each point distribution, no fan shape
modIFF_resid<-resid(modIFF)
qqnorm(modIFF_resid)
qqline(modIFF_resid)
plot(modIFF_resid)

anova(modIFF) # print anova results
emmeans(modIFF, ~N*P*CROP*YearCode, cov.reduce=FALSE) # estimated marginal means
emtrends(modIFF, ~N+P+YearCode, var="N", infer=TRUE) # slope different than zero
emtrends(modIFF, pairwise~YearCode|CROP+P, var="N", infer=TRUE) # slope different by cropP
```
# Two quick figures for fun (not cleaned up)
```{r}
ggplot(forage_data_fall_2, aes(x=N, y=PlotIWGDryKgHa, color=YearCode))+geom_point()+facet_grid(CROP~P)+geom_smooth(method="lm", se=FALSE)

emmip(modIFF, YearCode~N | CROP*P, cov.reduce=FALSE, CIs = TRUE)+ #model predicted vales
    scale_x_continuous(breaks = c(0, 40, 80, 120, 160), labels = c("0", "40", "80", "120", "160"))
#emmip(modTFS, N~YearCode | CROP*P, cov.reduce=FALSE, CIs = TRUE) #model predicted vales (I don't like this orientation)
```
# percent change in grain yield per unit increase in nitrogen
```{r}
# percent change in grain yield per unit increase in nitrogen
# pvalue is showing slopes that are signifcanly different than zero (significant percent change in yield with N)

# N*CROP*Year
# N slopes
emtrends_result<-emtrends(modIFF,~ CROP+YearCode, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
  emtrends_df$plvl <-
    ifelse(emtrends_df$p.value == 0.05, ".",
    ifelse(emtrends_df$p.value < 0.05  & emtrends_df$p.value >= 0.01, "*",
    ifelse(emtrends_df$p.value < 0.01  & emtrends_df$p.value >= 0.001, "**",
    ifelse(emtrends_df$p.value < 0.001, "***", "")))) # slope different than zero
# Intercepts at N=0
emmeans_results<-emmeans(modIFF, ~CROP+YearCode, at=list(N=0)) 
emmeans_df <- as.data.frame(emmeans_results)
# Merge slopes and intercepts
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("YearCode", "CROP")) %>%
  select(YearCode, CROP, emmean, N.trend, SE.x, plvl) 
View(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
# Create a new data frame with the calculated column
new_df <- merged_df %>%
    mutate(equation = sprintf("=%.2f+(%.4fN)", emmean, N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", N.trend / emmean * 100))%>%
    select(-emmean, -N.trend) 
sorted_df <- new_df %>%
  arrange(YearCode, CROP)
View(sorted_df)
```
# relationship of location, cropping system, and year
```{r}
emtrends(modIFF, pairwise~YearCode|CROP+P, var="N", infer=TRUE) # slope different by cropP
emmeans(modIFF, ~N*P*CROP*YearCode, cov.reduce=FALSE) # estimated marginal means
emmeans(modIFF, ~P*CROP*YearCode, cov.reduce=FALSE) # estimated marginal means

# box and wisker plot with post-hoc compact letter display for sig differences?

IFFemms <- emmeans(modIFF, ~ P*CROP*YearCode, type = "response") # Obtain estimated marginal means
emmsIFF_df <- as.data.frame(IFFemms)
cld_dataIFF <- cld(IFFemms, Letters=custom_letters)
cldIFF_df <-as.data.frame(cld_dataIFF)
mergedIFF_df <- merge(emmsIFF_df, cldIFF_df,by = c("P", "CROP", "YearCode"))
# custom cld position 
mergedIFF_df <- mergedIFF_df %>%
  left_join(
    forage_data_fall_2 %>%
      group_by(P, CROP, YearCode) %>%
      dplyr::summarise(label_y = if (all(is.na(PlotIWGDryKgHa))) {NA_real_} else {max(PlotIWGDryKgHa, na.rm = TRUE) * 0.9}, .groups = "drop"),
    by = c("P", "CROP", "YearCode")
  )
# Custom X-axis labels
IFF_CPY <- ggplot(forage_data_fall_2, aes(x = YearCode, y = PlotIWGDryKgHa, colour= CROP)) +
  geom_boxplot(position = position_dodge(width = 0.8)) + # blank
  geom_text(data = mergedIFF_df, aes(x = YearCode, y = label_y, label = .group, colour = CROP, group = CROP),
            position = position_dodge(width = 0.8), size = 6, show.legend = FALSE)+
  facet_wrap(~P, scales = "free", ncol = 2) +
  scale_colour_manual(values = c(inter = "#DDCC77", monoA = "#332288", monoI = "#661100")) +
  labs(x = "Year", y = "IWG Forage (kg/ha)")+ #title=""
  theme(axis.text.y=element_text(size=14), #change font size of axis text
        axis.text.x=element_text(size=16),
        axis.title=element_text(size=22))
IFF_CPY
# 1500x1200
```

## Proportion of species in Total Forage Yield
From Megan: values and analysis of proportion of each species in total forage yield for intercropped plots. Not proportional partial LER, but just proportion of normal yields in the total.
# proportion of species in Total Forage Yield of intercropped plots calculations
```{r}
# Year 1 S - proportion of species in total forage intercropped plots
NdXSPrIA <- shortenXS %>%
  filter(Intercropped == "y")%>%
  group_by(N, P, Plot, Rep, YearCode) %>%
  reframe(
    PropIWG = (PlotIWGDryKgHa) / (PlotTotForageKgHa), 
    PropALF = (PlotAlfDryKgHa) / (PlotTotForageKgHa), 
    Tot = (PropIWG + PropALF)
  )
# Year 1 F - proportion of species in total forage intercropped plots
NdXFPrIA <- shortenXF %>%
  filter(Intercropped == "y")%>%
  group_by(N, P, Plot, Rep, YearCode) %>%
  reframe(
    PropIWG = (PlotIWGDryKgHa) / (PlotTotForageKgHa), 
    PropALF = (PlotAlfDryKgHa) / (PlotTotForageKgHa), 
    Tot = (PropIWG + PropALF)
  )
# Year 2 S - proportion of species in total forage intercropped plots
NdYSPrIA <- shortenYS %>%
  filter(Intercropped == "y")%>%
  group_by(N, P, Plot, Rep, YearCode) %>%
  reframe(
    PropIWG = (PlotIWGDryKgHa) / (PlotTotForageKgHa), 
    PropALF = (PlotAlfDryKgHa) / (PlotTotForageKgHa), 
    Tot = (PropIWG + PropALF)
  )
# Year 2 F - proportion of species in total forage intercropped plots
NdYFPrIA <- shortenYF %>%
  filter(Intercropped == "y")%>%
  group_by(N, P, Plot, Rep, YearCode) %>%
  reframe(
    PropIWG = (PlotIWGDryKgHa) / (PlotTotForageKgHa), 
    PropALF = (PlotAlfDryKgHa) / (PlotTotForageKgHa), 
    Tot = (PropIWG + PropALF)
  )
# Year 3 S - proportion of species in total forage intercropped plots
NdZSPrIA <- shortenZS %>%
  filter(Intercropped == "y")%>%
  group_by(N, P, Plot, Rep, YearCode) %>%
  reframe(
    PropIWG = (PlotIWGDryKgHa) / (PlotTotForageKgHa), 
    PropALF = (PlotAlfDryKgHa) / (PlotTotForageKgHa), 
    Tot = (PropIWG + PropALF)
  )
# Year 3 F - proportion of species in total forage intercropped plots
NdZFPrIA <- shortenZF %>%
  filter(Intercropped == "y")%>%
  filter(!is.na(PlotIWGDryKgHa), !is.na(PlotAlfDryKgHa)) %>%   # drop rows where either forage amount is NA
  group_by(N, P, Plot, Rep, YearCode) %>%
  reframe(
    PropIWG = (PlotIWGDryKgHa) / (PlotTotForageKgHa), 
    PropALF = (PlotAlfDryKgHa) / (PlotTotForageKgHa), 
    Tot = (PropIWG + PropALF)
  )

PrIA1 <- rbind(NdXSPrIA, NdXFPrIA)
PrIA2 <- rbind(NdYSPrIA, NdYFPrIA)
PrIA3 <- rbind(NdZSPrIA, NdZFPrIA)
PrIA4 <- rbind(PrIA1, PrIA2) 
PrIA <- rbind(PrIA4, PrIA3)
```
# anova
```{r}
# want N to be numeric
is.numeric(PrIA$N)
# want P, CROP, and Year to be factors
is.factor(PrIA$P)
is.factor(PrIA$YearCode)
# PrIA$YearCode <- as.factor(PrIA$YearCode)
# Rep and Plot should also be factors
is.factor(PrIA$Rep)
is.factor(PrIA$Plot)
# PrIA$Plot <- as.character(PrIA$Plot)

modIPrIA<-lmer(PropIWG~N*P*YearCode + (1|Rep:P)+(1|Plot:Rep:P), data = PrIA) # IWG proportion
anova(modIPrIA)
modAPrIA<-lmer(PropALF~N*P*YearCode + (1|Rep)+(1|Plot:Rep:P), data = PrIA) # ALF proportion
anova(modAPrIA)

# manipulate into long format
PrIA_long <- PrIA %>%
  pivot_longer(cols = starts_with("Prop"),
               names_to = "Species",
               values_to = "Prop")
# get mean proportion of each species at a given N within a P
PrIA_long2 <- PrIA_long %>%
  dplyr::group_by(YearCode, P, N, Species) %>%
  dplyr::summarise(meanProp = mean(Prop),
                   Tot = first(Tot),
                   .groups = "drop")%>%
  mutate(N = factor(N))%>%
  mutate(Species = factor(Species, levels = c("PropIWG", "PropALF")))
```
# pairwise comparison
```{r}
# IWG pairwise comparisons between N rates
PrIA$N <- factor(PrIA$N)
modIPrIA <- update(modIPrIA)
emmsN <- emmeans(modIPrIA, pairwise ~ N|P+YearCode) 
cld_dataIPrIA <- cld(emmsN, Letters=custom_letters) # Create compact letter display
cld_dataIPrIA$response <- format(cld_dataIPrIA$response, digits = 5)
rownames(cld_dataIPrIA) <- NULL
cld_dataIPrIA<- cld_dataIPrIA %>%
  select(YearCode, N, P, SE, lower.CL, upper.CL, .group)
cld_dataIPrIA  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)
# alfalfa pairwise comparisons between N rates
modAPrIA <- update(modAPrIA)
emmsN <- emmeans(modAPrIA, pairwise ~ N|P+YearCode) 
cld_dataAPrIA <- cld(emmsN, Letters=custom_letters) # Create compact letter display
cld_dataAPrIA$response <- format(cld_dataAPrIA$response, digits = 5)
rownames(cld_dataAPrIA) <- NULL
cld_dataAPrIA<- cld_dataAPrIA %>%
  select(YearCode, N, SE, lower.CL, upper.CL, .group)
cld_dataAPrIA  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)
```
# visualize
```{r}
PrIAplot <- ggplot(PrIA_long2, aes(x = N, y = meanProp, fill = Species)) +
  geom_bar(stat = "identity", position = "stack")+
  facet_wrap(P~YearCode, ncol = 3) +
  labs(y = "Proportion Species", x = "N Rate") +
  scale_fill_discrete(name = "Species",
  labels = c(PropALF = "Alfalfa", PropIWG = "IWG"))
PrIAplot
```

## LER
# LER calculations 
```{r}
# Nd SW 0 
#IWG partial LER 
NdSW0IWGLER <- forage_data %>%
  group_by(Rep, P, YearCode, Harvest) %>%
  reframe(
    PartialLERIWGSW0 = (PlotIWGDryKgHa[Treatment == 10]) / (PlotIWGDryKgHa[Treatment == 5])
  )
#Alf partial LER 
NdSW0ALFLER <- forage_data %>%
  group_by(Rep, P, YearCode, Harvest) %>%
  reframe(
    PartialLERAlfSW0 = (PlotAlfDryKgHa[Treatment == 10]) / (PlotAlfDryKgHa[Treatment == 15])
  )
#Total LER 
NdSW0TotalLER <- forage_data %>%
  group_by(Rep, P, YearCode, Harvest) %>%
  reframe(
    TotalLERSW0 = (PlotIWGDryKgHa[Treatment == 10]) / (PlotIWGDryKgHa[Treatment == 5]) + (PlotAlfDryKgHa[Treatment == 10]) / (PlotAlfDryKgHa[Treatment == 15])
  ) 
#Join together first two tables
LERresults1<-left_join(NdSW0IWGLER, NdSW0ALFLER, by = c("Rep", "P", "YearCode", "Harvest"))
#join together new joined table and third table 
LERresultsNdSW0<-left_join(LERresults1, NdSW0TotalLER, by = c("Rep", "P", "YearCode", "Harvest"))

# Nd SW 40 
#IWG partial LER 
NdSW40IWGLER <- forage_data %>%
  group_by(Rep, P, YearCode, Harvest) %>%
  reframe(
    PartialLERIWGSW40 = (PlotIWGDryKgHa[Treatment == 11]) / (PlotIWGDryKgHa[Treatment == 6])
  )
#Alf partial LER 
NdSW40ALFLER <- forage_data %>%
  group_by(Rep, P, YearCode, Harvest) %>%
  reframe(
    PartialLERAlfSW40 = (PlotAlfDryKgHa[Treatment == 11]) / (PlotAlfDryKgHa[Treatment == 16])
  )
#Total LER 
NdSW40TotalLER <- forage_data %>%
  group_by(Rep, P, YearCode, Harvest) %>%
  reframe(
    TotalLERSW40 = (PlotIWGDryKgHa[Treatment == 11]) / (PlotIWGDryKgHa[Treatment == 6]) + (PlotAlfDryKgHa[Treatment == 11]) / (PlotAlfDryKgHa[Treatment == 16])
  ) 
#Join together first two tables
LERresults2<-left_join(NdSW40IWGLER, NdSW40ALFLER, by = c("Rep", "P", "YearCode", "Harvest"))
#join together new joined table and third table 
LERresultsNdSW40<-left_join(LERresults2, NdSW40TotalLER, by = c("Rep", "P", "YearCode", "Harvest"))

#Nd SW 80
#IWG partial LER 
NdSW80IWGLER <- forage_data %>%
  group_by(Rep, P, YearCode, Harvest) %>%
  reframe(
    PartialLERIWGSW80 = (PlotIWGDryKgHa[Treatment == 12]) / (PlotIWGDryKgHa[Treatment == 7])
  )
#Alf partial LER 
NdSW80ALFLER <- forage_data %>%
  group_by(Rep, P, YearCode, Harvest) %>%
  reframe(
    PartialLERAlfSW80 = (PlotAlfDryKgHa[Treatment == 12]) / (PlotAlfDryKgHa[Treatment == 17])
  )
#Total LER 
NdSW80TotalLER <- forage_data %>%
  group_by(Rep, P, YearCode, Harvest) %>%
  reframe(
    TotalLERSW80 = (PlotIWGDryKgHa[Treatment == 12]) / (PlotIWGDryKgHa[Treatment == 7]) + (PlotAlfDryKgHa[Treatment == 12]) / (PlotAlfDryKgHa[Treatment == 17])
  ) 
#Join together first two tables
LERresults3<-left_join(NdSW80IWGLER, NdSW80ALFLER, by = c("Rep", "P", "YearCode", "Harvest"))
#join together new joined table and third table 
LERresultsNdSW80<-left_join(LERresults3, NdSW80TotalLER, by = c("Rep", "P", "YearCode", "Harvest"))

#Nd SW 120
#IWG partial LER 
NdSW120IWGLER <- forage_data %>%
  group_by(Rep, P, YearCode, Harvest) %>%
  reframe(
    PartialLERIWGSW120 = (PlotIWGDryKgHa[Treatment == 13]) / (PlotIWGDryKgHa[Treatment == 8])
  )
#Alf partial LER 
NdSW120ALFLER <- forage_data %>%
  group_by(Rep, P, YearCode, Harvest) %>%
  reframe(
    PartialLERAlfSW120 = (PlotAlfDryKgHa[Treatment == 13]) / (PlotAlfDryKgHa[Treatment == 18])
  )
#Total LER 
NdSW120TotalLER <- forage_data %>%
  group_by(Rep, P, YearCode, Harvest) %>%
  reframe(
    TotalLERSW120 = (PlotIWGDryKgHa[Treatment == 13]) / (PlotIWGDryKgHa[Treatment == 8]) + (PlotAlfDryKgHa[Treatment == 13]) / (PlotAlfDryKgHa[Treatment == 18])
  ) 
#Join together first two tables
LERresults4<-left_join(NdSW120IWGLER, NdSW120ALFLER, by = c("Rep", "P", "YearCode", "Harvest"))
#join together new joined table and third table 
LERresultsNdSW120<-left_join(LERresults4, NdSW120TotalLER, by = c("Rep", "P", "YearCode", "Harvest"))

#Nd SW 160
#IWG partial LER 
NdSW160IWGLER <- forage_data %>%
  group_by(Rep, P, YearCode, Harvest) %>%
  reframe(
    PartialLERIWGSW160= (PlotIWGDryKgHa[Treatment == 14]) / (PlotIWGDryKgHa[Treatment == 9])
  )
#Alf partial LER 
NdSW160ALFLER <- forage_data %>%
  group_by(Rep, P, YearCode, Harvest) %>%
  reframe(
    PartialLERAlfSW160 = (PlotAlfDryKgHa[Treatment == 14]) / (PlotAlfDryKgHa[Treatment == 19])
  )
#Total LER 
NdSW160TotalLER <- forage_data %>%
  group_by(Rep, P, YearCode, Harvest) %>%
  reframe(
    TotalLERSW160 = (PlotIWGDryKgHa[Treatment == 14]) / (PlotIWGDryKgHa[Treatment == 9]) + (PlotAlfDryKgHa[Treatment == 14]) / (PlotAlfDryKgHa[Treatment == 19])
  ) 
#Join together first two tables
LERresults5<-left_join(NdSW160IWGLER, NdSW160ALFLER, by = c("Rep", "P", "YearCode", "Harvest"))
#join together new joined table and third table 
LERresultsNdSW160<-left_join(LERresults5, NdSW160TotalLER, by = c("Rep", "P", "YearCode", "Harvest"))

#merge all LER results into one data frame
LERresults6<-left_join(LERresultsNdSW0, LERresultsNdSW40, by = c("Rep", "P", "YearCode", "Harvest"))
LERresults7<-left_join(LERresults6, LERresultsNdSW80, by = c("Rep", "P", "YearCode", "Harvest"))
LERresults8<-left_join(LERresults7, LERresultsNdSW120, by = c("Rep", "P", "YearCode", "Harvest"))
LERresultsNdSWALL<-left_join(LERresults8, LERresultsNdSW160, by = c("Rep", "P", "YearCode", "Harvest"))

#Rearrange dataframe
LERresultsNdSWALL_long <- LERresultsNdSWALL %>%
  pivot_longer(cols = starts_with("PartialLER") | starts_with("TotalLER"),
               names_to = "Nrate",
               values_to = "LER")

#try to make the dataframe more usable

#cut off total and partial 
LERresultsNdSWALL_long$Type <- sub("^(Partial|Total)", "", LERresultsNdSWALL_long$Nrate)
LERresultsNdSWALL_long$tot_or_part <- sub("^(Partial|Total).*", "\\1", LERresultsNdSWALL_long$Nrate)

#cut off LERIWGSW and LERAlfSW and LERSW
LERresultsNdSWALL_long$NRATE <- sub("^(LERIWGSW|LERAlfSW|LERSW)", "", LERresultsNdSWALL_long$Type)
LERresultsNdSWALL_long$PlotType <- sub("^(LERIWGSW|LERAlfSW|LERSW).*", "\\1", LERresultsNdSWALL_long$Type)

#get rid of pesky NA results (caused by missing plots inherent in year 1 KS summer data)
LERresultsNdSWALL_longNONA<- na.omit(LERresultsNdSWALL_long)

LERresultsNdSWALL_longNONA$NRATE<-as.numeric(LERresultsNdSWALL_longNONA$NRATE)

#includes total and partial until it doesn't...used for some pairwise comparison thingy. 
LERResultsAllX<-LERresultsNdSWALL_longNONA[LERresultsNdSWALL_longNONA$YearCode == 'X',]
LERResultsAllY<-LERresultsNdSWALL_longNONA[LERresultsNdSWALL_longNONA$YearCode == 'Y',]
LERResultsAllZ<-LERresultsNdSWALL_longNONA[LERresultsNdSWALL_longNONA$YearCode == 'Z',]
LERResultsAllXS<-LERResultsAllX[LERResultsAllX$Harvest == 'Summer',]
  LERResultsTotXS<-LERResultsAllXS[LERResultsAllXS$tot_or_part == 'Total',]
  LERResultsPartIWGXS<-LERResultsAllXS[LERResultsAllXS$tot_or_part == 'Partial' & LERResultsAllXS$PlotType == 'LERIWGSW' ,]
  LERResultsPartAlfXS<-LERResultsAllXS[LERResultsAllXS$tot_or_part == 'Partial' & LERResultsAllXS$PlotType == 'LERAlfSW' ,]
LERResultsAllXF<-LERResultsAllX[LERResultsAllX$Harvest == 'Fall',]
  LERResultsTotXF<-LERResultsAllXF[LERResultsAllXF$tot_or_part == 'Total',]
  LERResultsPartIWGXF<-LERResultsAllXF[LERResultsAllXF$tot_or_part == 'Partial' & LERResultsAllXF$PlotType == 'LERIWGSW' ,]
  LERResultsPartAlfXF<-LERResultsAllXF[LERResultsAllXF$tot_or_part == 'Partial' & LERResultsAllXF$PlotType == 'LERAlfSW' ,]
LERResultsAllYS<-LERResultsAllY[LERResultsAllY$Harvest == 'Summer',]
  LERResultsTotYS<-LERResultsAllYS[LERResultsAllYS$tot_or_part == 'Total',]
  LERResultsPartIWGYS<-LERResultsAllYS[LERResultsAllYS$tot_or_part == 'Partial' & LERResultsAllYS$PlotType == 'LERIWGSW' ,]
  LERResultsPartAlfYS<-LERResultsAllYS[LERResultsAllYS$tot_or_part == 'Partial' & LERResultsAllYS$PlotType == 'LERAlfSW' ,]
LERResultsAllYF<-LERResultsAllY[LERResultsAllY$Harvest == 'Fall',]
  LERResultsTotYF<-LERResultsAllYF[LERResultsAllYF$tot_or_part == 'Total',]
  LERResultsPartIWGYF<-LERResultsAllYF[LERResultsAllYF$tot_or_part == 'Partial' & LERResultsAllYF$PlotType == 'LERIWGSW' ,]
  LERResultsPartAlfYF<-LERResultsAllYF[LERResultsAllYF$tot_or_part == 'Partial' & LERResultsAllYF$PlotType == 'LERAlfSW' ,]
LERResultsAllZS<-LERResultsAllZ[LERResultsAllZ$Harvest == 'Summer',]
  LERResultsTotZS<-LERResultsAllZS[LERResultsAllZS$tot_or_part == 'Total',]
  LERResultsPartIWGZS<-LERResultsAllZS[LERResultsAllZS$tot_or_part == 'Partial' & LERResultsAllZS$PlotType == 'LERIWGSW' ,]
  LERResultsPartAlfZS<-LERResultsAllZS[LERResultsAllZS$tot_or_part == 'Partial' & LERResultsAllZS$PlotType == 'LERAlfSW' ,]
LERResultsAllZF<-LERResultsAllZ[LERResultsAllZ$Harvest == 'Fall',]
  LERResultsTotZF<-LERResultsAllZF[LERResultsAllZF$tot_or_part == 'Total',]
  LERResultsPartIWGZF<-LERResultsAllZF[LERResultsAllZF$tot_or_part == 'Partial' & LERResultsAllZF$PlotType == 'LERIWGSW' ,]
  LERResultsPartAlfZF<-LERResultsAllZF[LERResultsAllZF$tot_or_part == 'Partial' & LERResultsAllZF$PlotType == 'LERAlfSW' ,]
  
# change Inf values to NA
LERresultsNdSWALL_longNONA
LERresultsNdSWALL_longNONA['LER'][LERresultsNdSWALL_longNONA['LER'] == 'Inf'] <- NA
  
#okay now I should be able to split by total and partial
TotalLERresults<-LERresultsNdSWALL_longNONA[LERresultsNdSWALL_longNONA$tot_or_part == 'Total',]
  TotLERX<-TotalLERresults[TotalLERresults$YearCode == 'X',]
  TotLERY<-TotalLERresults[TotalLERresults$YearCode == 'Y',]
  TotLERZ<-TotalLERresults[TotalLERresults$YearCode == 'Z',]
  TotLERXS<-TotLERX[TotLERX$Harvest == 'Summer',]
  TotLERXF<-TotLERX[TotLERX$Harvest == 'Fall',]
  TotLERYS<-TotLERY[TotLERY$Harvest == 'Summer',]
  TotLERYF<-TotLERY[TotLERY$Harvest == 'Fall',]
  TotLERZS<-TotLERZ[TotLERZ$Harvest == 'Summer',]
  TotLERZF<-TotLERZ[TotLERZ$Harvest == 'Fall',]
IWGPartialLERresults<-LERresultsNdSWALL_longNONA[LERresultsNdSWALL_longNONA$PlotType == 'LERIWGSW',]
IWGPartialLERresults$NRATE<- as.numeric(IWGPartialLERresults$NRATE)
  IWGPLERX<-IWGPartialLERresults[IWGPartialLERresults$YearCode == 'X',]
  IWGPLERY<-IWGPartialLERresults[IWGPartialLERresults$YearCode == 'Y',]
  IWGPLERZ<-IWGPartialLERresults[IWGPartialLERresults$YearCode == 'Z',]
  IWGPLERXS<-IWGPLERX[IWGPLERX$Harvest == 'Summer',]
  IWGPLERXF<-IWGPLERX[IWGPLERX$Harvest == 'Fall',]
  IWGPLERYS<-IWGPLERY[IWGPLERY$Harvest == 'Summer',]
  IWGPLERYF<-IWGPLERY[IWGPLERY$Harvest == 'Fall',]
  IWGPLERZS<-IWGPLERZ[IWGPLERZ$Harvest == 'Summer',]
  IWGPLERZF<-IWGPLERZ[IWGPLERZ$Harvest == 'Fall',]
AlfPartialLERresults<-LERresultsNdSWALL_longNONA[LERresultsNdSWALL_longNONA$PlotType == 'LERAlfSW',]
AlfPartialLERresults$NRATE<- as.numeric(AlfPartialLERresults$NRATE)
  AlfPLERX<-AlfPartialLERresults[AlfPartialLERresults$YearCode == 'X',]
  AlfPLERY<-AlfPartialLERresults[AlfPartialLERresults$YearCode == 'Y',]
  AlfPLERZ<-AlfPartialLERresults[AlfPartialLERresults$YearCode == 'Z',]
  AlfPLERXS<-AlfPLERX[AlfPLERX$Harvest == 'Summer',]
  AlfPLERXF<-AlfPLERX[AlfPLERX$Harvest == 'Fall',]
  AlfPLERYS<-AlfPLERY[AlfPLERY$Harvest == 'Summer',]
  AlfPLERYF<-AlfPLERY[AlfPLERY$Harvest == 'Fall',]
  AlfPLERZS<-AlfPLERZ[AlfPLERZ$Harvest == 'Summer',]
  AlfPLERZF<-AlfPLERZ[AlfPLERZ$Harvest == 'Fall',]
  
#Check for outliers
identify_outliers(TotalLERresults[, 6]) #33 outliers 
identify_outliers(IWGPartialLERresults[, 6]) #46 outliers
identify_outliers(AlfPartialLERresults[, 6]) #18 outliers 

#rename variables in dataframes to make life easier 
# Function to add new columns to a dataframe
add_new_columns <- function(df) {
  df$N <- df$NRATE
  return(df)
}
# List of dataframes (replace these with your actual dataframes)
df_list <- list(TotLERXS, TotLERYS, TotLERZS, 
                TotLERXF, TotLERYF, TotLERZF, 
                IWGPLERXS, IWGPLERYS, IWGPLERZS, 
                IWGPLERXF, IWGPLERYF, IWGPLERZF, 
                AlfPLERXS, AlfPLERYS, AlfPLERZS,
                AlfPLERXF, AlfPLERYF, AlfPLERZF)
# Apply the function to each dataframe in the list
df_list <- lapply(df_list, add_new_columns)
# Access the modified dataframes in df_list
TotLERXS <- df_list[[1]]
TotLERYS <- df_list[[2]]
TotLERZS <- df_list[[3]]
TotLERXF <- df_list[[4]]
TotLERYF<- df_list[[5]]
TotLERZF<- df_list[[6]]
IWGPLERXS<- df_list[[7]]
IWGPLERYS<- df_list[[8]]
IWGPLERZS<- df_list[[9]]
IWGPLERXF<- df_list[[10]]
IWGPLERYF<- df_list[[11]]
IWGPLERZF<- df_list[[12]]
AlfPLERXS<- df_list[[13]]
AlfPLERYS<- df_list[[14]]
AlfPLERZS<- df_list[[15]]
AlfPLERXF<- df_list[[16]]
AlfPLERYF<- df_list[[17]]
AlfPLERZF<- df_list[[18]]
```
# anova
```{r}
TotalLERresults$N<-TotalLERresults$NRATE
TotalLERresults$N<- as.numeric(TotalLERresults$N)
#linear
modTotLER<-lmer(LER~N*P*YearCode + (1|Rep:P), data= TotalLERresults)
anova(modTotLER)
```
# Two quick figures for fun (not cleaned up)
```{r}
ggplot(TotalLERresults, aes(x=N, y=LER, color=YearCode))+geom_point()+facet_grid(~P)+geom_smooth(method="lm", se=FALSE)

emmip(modTotLER, YearCode~N | P, cov.reduce=FALSE, CIs = TRUE)+ #model predicted vales
    scale_x_continuous(breaks = c(0, 40, 80, 120, 160), labels = c("0", "40", "80", "120", "160"))
#emmip(modTFS, N~YearCode | CROP*P, cov.reduce=FALSE, CIs = TRUE) #model predicted vales (I don't like this orientation)
```
# percent change in grain yield per unit increase in nitrogen
```{r}
# percent change in grain yield per unit increase in nitrogen
# pvalue is showing slopes that are signifcanly different than zero (significant percent change in yield with N)

# N*Location*Year
# N slopes
emtrends_result<-emtrends(modTotLER,~ P+YearCode, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
  emtrends_df$plvl <-
    ifelse(emtrends_df$p.value == 0.05, ".",
    ifelse(emtrends_df$p.value < 0.05  & emtrends_df$p.value >= 0.01, "*",
    ifelse(emtrends_df$p.value < 0.01  & emtrends_df$p.value >= 0.001, "**",
    ifelse(emtrends_df$p.value < 0.001, "***", "")))) # slope different than zero
# Intercepts at N=0
emmeans_results<-emmeans(modTotLER, ~P+YearCode, at=list(N=0)) 
emmeans_df <- as.data.frame(emmeans_results)
# Merge slopes and intercepts
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("YearCode", "P")) %>%
  select(YearCode, P, emmean, N.trend, SE.x, plvl) 
View(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
# Create a new data frame with the calculated column
new_df <- merged_df %>%
    mutate(equation = sprintf("=%.2f+(%.4fN)", emmean, N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", N.trend / emmean * 100))%>%
    select(-emmean, -N.trend) 
sorted_df <- new_df %>%
  arrange(YearCode, P)
View(sorted_df)
```

## Competitive Ratio of IWG
(PLER IWG / PLER Alf ) * seeding rate ratio
our seeding rate ratio is 50/50 so the term is 1
# Competitive Ratio Calculation
```{r}
# SW0, SW40, SW80, SW120, SW160
CRresultsNdSWALL <- LERresultsNdSWALL %>%
  select(Rep, P, YearCode, Harvest, PartialLERIWGSW0, TotalLERSW0, PartialLERIWGSW40, TotalLERSW40, PartialLERIWGSW80, TotalLERSW80, PartialLERIWGSW120, TotalLERSW120, PartialLERIWGSW160, TotalLERSW160)%>%
  mutate(CRSW0 = PartialLERIWGSW0 / TotalLERSW0)%>%
  mutate(CRSW40 = PartialLERIWGSW40 / TotalLERSW40)%>%
  mutate(CRSW80 = PartialLERIWGSW80 / TotalLERSW80)%>%
  mutate(CRSW120 = PartialLERIWGSW120 / TotalLERSW120)%>%
  mutate(CRSW160 = PartialLERIWGSW160 / TotalLERSW160)%>%
  select(Rep, P, YearCode, Harvest, CRSW0, CRSW40, CRSW80, CRSW120, CRSW160)
```
# Competitive Ratio Compile data
```{r}
#Rearrange dataframe
CRresultsNdSWALL_long <- CRresultsNdSWALL %>%
  pivot_longer(cols = starts_with("CRSW"),
               names_to = "Nrate",
               values_to = "CR")

#try to make the dataframe more usable

#cut off total and partial 
CRresultsNdSWALL_long$Type <- sub("^(CR)", "", CRresultsNdSWALL_long$Nrate)
#LERresultsNdSWALL_long$tot_or_part <- sub("^(Partial|Total).*", "\\1", LERresultsNdSWALL_long$Nrate)

#cut off SW
CRresultsNdSWALL_long$NRATE <- sub("^(SW|SW|SW)", "", CRresultsNdSWALL_long$Type)
CRresultsNdSWALL_long$PlotType <- sub("^(CRSW|CRSW|CRSW).*", "\\1", CRresultsNdSWALL_long$Type)

#get rid of pesky NA results (caused by missing plots inherent in year 1 KS summer data)
CRresultsNdSWALL_longNONA<- na.omit(CRresultsNdSWALL_long)

CRresultsNdSWALL_longNONA$NRATE<-as.numeric(CRresultsNdSWALL_longNONA$NRATE)

#includes total and partial until it doesn't...used for some pairwise comparison thingy. 
CRResultsAllX<-CRresultsNdSWALL_longNONA[CRresultsNdSWALL_longNONA$YearCode == 'X',]
CRResultsAllY<-CRresultsNdSWALL_longNONA[CRresultsNdSWALL_longNONA$YearCode == 'Y',]
CRResultsAllZ<-CRresultsNdSWALL_longNONA[CRresultsNdSWALL_longNONA$YearCode == 'Z',]
CRResultsAllXS<-CRResultsAllX[CRResultsAllX$Harvest == 'Summer',]
CRResultsAllXF<-CRResultsAllX[CRResultsAllX$Harvest == 'Fall',]
CRResultsAllYS<-CRResultsAllY[CRResultsAllY$Harvest == 'Summer',]
CRResultsAllYF<-CRResultsAllY[CRResultsAllY$Harvest == 'Fall',]
CRResultsAllZS<-CRResultsAllZ[CRResultsAllZ$Harvest == 'Summer',]
CRResultsAllZF<-CRResultsAllZ[CRResultsAllZ$Harvest == 'Fall',]

#rename variables in dataframes to make life easier 
# Function to add new columns to a dataframe
add_new_columns <- function(df) {
  df$N <- df$NRATE
  return(df)
}

# List of dataframes (replace these with your actual dataframes)
df_list <- list(CRResultsAllXS, CRResultsAllXF, 
                CRResultsAllYS, CRResultsAllYF, 
                CRResultsAllZS, CRResultsAllZF)

# Apply the function to each dataframe in the list
df_list <- lapply(df_list, add_new_columns)
# Access the modified dataframes in df_list
CRXS <- df_list[[1]]
CRXF <- df_list[[2]]
CRYS <- df_list[[3]]
CRYF <- df_list[[4]]
CRZS <- df_list[[5]]
CRZF <- df_list[[6]]
```
# anova
```{r}
CRresultsNdSWALL_longNONA$N<-CRresultsNdSWALL_longNONA$NRATE
CRresultsNdSWALL_longNONA$N<- as.numeric(CRresultsNdSWALL_longNONA$N)
#linear
modCR<-lmer(CR~N*P*YearCode + (1|Rep:P), data= CRresultsNdSWALL_longNONA)
anova(modCR)
```


### STOPED HERE ###


## Forage Quality
#N RFV calculations 
```{r}
#IWG 
forage_data_summer$IWGRFV<-((88.9 - (0.779 * forage_data_summer$IWGADF)) * (120 / forage_data_summer$IWGaNDF) ) / 1.29
forage_data_fall$IWGRFV<-((88.9 - (0.779 * forage_data_fall$IWGADF)) * (120 / forage_data_fall$IWGaNDF) ) / 1.29


#REMOVE outliers KSY314I, KSY315I
#NdYSI<-NdYSI[-107,]
#NdYSI<-NdYSI[-107,]

#make big df for deltas 
NdXSIdf <- forage_data_summer %>%
  select(YearCode, Rep, P, CROP, N, Harvest, IWGRFV)
NdXFIdf <- forage_data_fall %>%
  select(YearCode, Rep, P, CROP, N, Harvest, IWGRFV)

NRFVIdf<-bind_rows(NdXSIdf, NdXFIdf)


#Alf
NdXSA$ALFaNDF<-as.numeric(NdXSA$ALFaNDF)
NdXFA$ALFaNDF<-as.numeric(NdXFA$ALFaNDF)
NdYSA$ALFaNDF<-as.numeric(NdYSA$ALFaNDF)
NdYFA$ALFaNDF<-as.numeric(NdYFA$ALFaNDF)

NdXSA$ALFRFV<-((88.9 - (0.779 * NdXSA$ALFADF)) * (120 / NdXSA$ALFaNDF) ) / 1.29
NdXFA$ALFRFV<-((88.9 - (0.779 * NdXFA$ALFADF)) * (120 / NdXFA$ALFaNDF) ) / 1.29
NdYSA$ALFRFV<-((88.9 - (0.779 * NdYSA$ALFADF)) * (120 / NdYSA$ALFaNDF) ) / 1.29
NdYFA$ALFRFV<-((88.9 - (0.779 * NdYFA$ALFADF)) * (120 / NdYFA$ALFaNDF) ) / 1.29

#REMOVE outliers KSX202A missing, KSX209A
#NdXSA<-NdXSA[-88,]
#NdXSA<-NdXSA[-92,]

#REMOVE NYS212A, NYS215A, NYS217A, NYS219A, NYS220A, NYS223A, NYS304A (some already gone... maybe a variety thing)
#NdYSA<-NdYSA[-17,]
#NdYSA<-NdYSA[-18,]
#NdYSA<-NdYSA[-19,]

#make big df for deltas 
NdXSAdf <- NdXSA %>%
  select(YearCode, Rep, P, CROP, N, Harvest, ALFRFV)
NdXFAdf <- NdXFA %>%
  select(YearCode, Rep, P, CROP, N, Harvest, ALFRFV)
NdYSAdf <- NdYSA %>%
  select(YearCode, Rep, P, CROP, N, Harvest, ALFRFV)
NdYFAdf <- NdYFA %>%
  select(YearCode, Rep, P, CROP, N, Harvest, ALFRFV)
NRFVAdf<-bind_rows(NdXSAdf, NdXFAdf)
NRFVAdf<-bind_rows(NRFVAdf, NdYSAdf)
NRFVAdf<-bind_rows(NRFVAdf, NdYFAdf)
```

#making proportion stuff for total FQ CP and RFV 
```{r}
#NEEDS TO JUST BE INTERCROPPED PLOTS BUT LIKE ALSO NEED TO COMPARE INTERCROP TO MONOCULTURE SOO LIKE .... WUT 
#make proportions
NdXSI$propI<-((NdXSI$PlotIWGDryKgHa)/(NdXSI$PlotTotForageKgHa))
NdXFI$propI<-((NdXFI$PlotIWGDryKgHa)/(NdXFI$PlotTotForageKgHa))
NdYSI$propI<-((NdYSI$PlotIWGDryKgHa)/(NdYSI$PlotTotForageKgHa))
NdYFI$propI<-((NdYFI$PlotIWGDryKgHa)/(NdYFI$PlotTotForageKgHa))

NdXSA$propA<-((NdXSA$PlotAlfDryKgHa)/(NdXSA$PlotTotForageKgHa))
NdXFA$propA<-((NdXFA$PlotAlfDryKgHa)/(NdXFA$PlotTotForageKgHa))
NdYSA$propA<-((NdYSA$PlotAlfDryKgHa)/(NdYSA$PlotTotForageKgHa))
NdYFA$propA<-((NdYFA$PlotAlfDryKgHa)/(NdYFA$PlotTotForageKgHa))

#make adjusted CP values 
NdXSI$propCPI<-(NdXSI$IWGCP)*(NdXSI$propI)
NdXFI$propCPI<-(NdXFI$IWGCP)*(NdXFI$propI)
NdYSI$propCPI<-(NdYSI$IWGCP)*(NdYSI$propI)
NdYFI$propCPI<-(NdYFI$IWGCP)*(NdYFI$propI)

NdXSA$propCPA<-(NdXSA$ALFCP)*(NdXSA$propA)
NdXFA$propCPA<-(NdXFA$ALFCP)*(NdXFA$propA)
NdYSA$propCPA<-(NdYSA$ALFCP)*(NdYSA$propA)
NdYFA$propCPA<-(NdYFA$ALFCP)*(NdYFA$propA)

#Somehow make CP totals
  #XS
NdXSj<- NdXSI %>%
  select(propCPI, N, P, CROP, Plot, Harvest, YearCode, Rep)
NdXSk<- NdXSA %>%
  select(propCPA, N, P, CROP, Plot, Harvest, YearCode, Rep)
NdXSf<- merge(NdXSj, NdXSk, by = c("N", "P", "CROP", "Plot", "Harvest", "YearCode", "Rep"), all = TRUE)
NdXSf[is.na(NdXSf)] <- 0
NdXSf$totCP<-((NdXSf$propCPI)+(NdXSf$propCPA))
  #XF
NdXFj<- NdXFI %>%
  select(propCPI, N, P, CROP, Plot, Harvest, YearCode, Rep)
NdXFk<- NdXFA %>%
  select(propCPA, N, P, CROP, Plot, Harvest, YearCode, Rep)
NdXFf<- merge(NdXFj, NdXFk, by = c("N", "P", "CROP", "Plot", "Harvest", "YearCode", "Rep"), all = TRUE)
NdXFf[is.na(NdXFf)] <- 0
NdXFf$totCP<-((NdXFf$propCPI)+(NdXFf$propCPA))
  #YS
NdYSj<- NdYSI %>%
  select(propCPI, N, P, CROP, Plot, Harvest, YearCode, Rep)
NdYSk<- NdYSA %>%
  select(propCPA, N, P, CROP, Plot, Harvest, YearCode, Rep)
NdYSf<- merge(NdYSj, NdYSk, by = c("N", "P", "CROP", "Plot", "Harvest", "YearCode", "Rep"), all = TRUE)
NdYSf[is.na(NdYSf)] <- 0
NdYSf$totCP<-((NdYSf$propCPI)+(NdYSf$propCPA))
  #YF
NdYFj<- NdYFI %>%
  select(propCPI, N, P, CROP, Plot, Harvest, YearCode, Rep)
NdYFk<- NdYFA %>%
  select(propCPA, N, P, CROP, Plot, Harvest, YearCode, Rep)
NdYFf<- merge(NdYFj, NdYFk, by = c("N", "P", "CROP", "Plot", "Harvest", "YearCode", "Rep"), all = TRUE)
NdYFf[is.na(NdYFf)] <- 0
NdYFf$totCP<-((NdYFf$propCPI)+(NdYFf$propCPA))


#make adjusted RFV values 
NdXSI$propRFVI<-(NdXSI$IWGRFV)*(NdXSI$propI)
NdXFI$propRFVI<-(NdXFI$IWGRFV)*(NdXFI$propI)
NdYSI$propRFVI<-(NdYSI$IWGRFV)*(NdYSI$propI)
NdYFI$propRFVI<-(NdYFI$IWGRFV)*(NdYFI$propI)

NdXSA$propRFVA<-(NdXSA$ALFRFV)*(NdXSA$propA)
NdXFA$propRFVA<-(NdXFA$ALFRFV)*(NdXFA$propA)
NdYSA$propRFVA<-(NdYSA$ALFRFV)*(NdYSA$propA)
NdYFA$propRFVA<-(NdYFA$ALFRFV)*(NdYFA$propA)

#Somehow make RFV totals
  #XS
NdXSm<- NdXSI %>%
  select(propRFVI, N, P, CROP, Plot, Harvest, YearCode, Rep)
NdXSn<- NdXSA %>%
  select(propRFVA, N, P, CROP, Plot, Harvest, YearCode, Rep)
NdXSo<- merge(NdXSm, NdXSn, by = c("N", "P", "CROP", "Plot", "Harvest", "YearCode", "Rep"), all = TRUE)
NdXSo[is.na(NdXSo)] <- 0
NdXSo$totRFV<-((NdXSo$propRFVI)+(NdXSo$propRFVA))
  #XF
NdXFm<- NdXFI %>%
  select(propRFVI, N, P, CROP, Plot, Harvest, YearCode, Rep)
NdXFn<- NdXFA %>%
  select(propRFVA, N, P, CROP, Plot, Harvest, YearCode, Rep)
NdXFo<- merge(NdXFm, NdXFn, by = c("N", "P", "CROP", "Plot", "Harvest", "YearCode", "Rep"), all = TRUE)
NdXFo[is.na(NdXFo)] <- 0
NdXFo$totRFV<-((NdXFo$propRFVI)+(NdXFo$propRFVA))
  #YS
NdYSm<- NdYSI %>%
  select(propRFVI, N, P, CROP, Plot, Harvest, YearCode, Rep)
NdYSn<- NdYSA %>%
  select(propRFVA, N, P, CROP, Plot, Harvest, YearCode, Rep)
NdYSo<- merge(NdYSm, NdYSn, by = c("N", "P", "CROP", "Plot", "Harvest", "YearCode", "Rep"), all = TRUE)
NdYSo[is.na(NdYSo)] <- 0
NdYSo$totRFV<-((NdYSo$propRFVI)+(NdYSo$propRFVA))
  #YF
NdYFm<- NdYFI %>%
  select(propRFVI, N, P, CROP, Plot, Harvest, YearCode, Rep)
NdYFn<- NdYFA %>%
  select(propRFVA, N, P, CROP, Plot, Harvest, YearCode, Rep)
NdYFo<- merge(NdYFm, NdYFn, by = c("N", "P", "CROP", "Plot", "Harvest", "YearCode", "Rep"), all = TRUE)
NdYFo[is.na(NdYFo)] <- 0
NdYFo$totRFV<-((NdYFo$propRFVI)+(NdYFo$propRFVA))
```






