---
title: "IWG-ALF Parts for Paper"
author: "Leah Treffer"
date: "2025-07-18"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# just loading these in, unsure which exactly are still used
```{r}
library(dplyr)
library(tidyr)
library(flextable)
library(ggplot2)
library(ggpubr)
library(gridExtra)
library(reshape2)
library(ggthemes)
library(gapminder)
library(multcomp)
library(emmeans)
library(multcompView)
library(lmerTest)
library(scales)
library(tidyverse)
library(readxl)
library(lme4)
library(gvlma)
library(rstatix)
library(sjPlot)
library(gt)
library(car)
library(Rmisc)
library(nlme)
library(pgirmess)
library(MuMIn)
library(sjPlot)
library(grateful)
library(cowplot)
library(kableExtra)
library(MuMIn)
library(ggpmisc)
library(bestNormalize)
```

# making emmeans functions 
```{r}
# Define a 3 WAY function for year 1 summer
compute_emmeansNXS <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P*CROP, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "1", Harvest = "Summer")
  
  return(emm_df)}

# Define a 3 WAY  function for year 1 fall
compute_emmeansNXF <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P*CROP, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "1", Harvest = "Fall")
  return(emm_df)}

# Define a 3 WAY  function for year 2 Summer
compute_emmeansNYS <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P*CROP, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "2", Harvest = "Summer")
  return(emm_df)}

# Define a 3 WAY function for year 2 Fall
compute_emmeansNYF <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P*CROP, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "2", Harvest = "Fall")
  return(emm_df)}

# Define a 3 WAY function for year 3 summer
compute_emmeansNZS <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P*CROP, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "3", Harvest = "Summer")
  
  return(emm_df)}

# Define a 3 WAY  function for year 3 fall
compute_emmeansNZF <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P*CROP, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "3", Harvest = "Fall")
  return(emm_df)}



# Define a NP function for year 1 summer
compute_emmeansNXS2 <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "1", Harvest = "Summer")
  return(emm_df)}

# Define a NP  function for year 1 fall
compute_emmeansNXF2 <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "1", Harvest = "Fall")
  return(emm_df)}

# Define a NP  function for year 2 Summer
compute_emmeansNYS2 <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "2", Harvest = "Summer")
  return(emm_df)}

# Define a NP function for year 2 Fall
compute_emmeansNYF2 <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "2", Harvest = "Fall")
  return(emm_df)}

# Define a NP function for year 3 summer
compute_emmeansNZS2 <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "3", Harvest = "Summer")
  return(emm_df)}

# Define a NP  function for year 3 fall
compute_emmeansNZF2 <- function(model_name) {
  N_levels <- c(0, 40, 80, 120, 160)
  # Get the model object using the provided name
  mod <- get(model_name)
  # Compute estimated marginal means
  emm <- emmeans(mod, specs = ~ N*P, at = list(N = N_levels))
  emm <- update(emm, type = "response")
  # Summarize the results
  summary_emm <- summary(emm)
  # Convert to data frame
  emm_df <- as.data.frame(summary_emm)
  # Add additional columns
  emm_df <- emm_df %>%
    mutate(Year = "3", Harvest = "Fall")
  return(emm_df)}
```

### Land Equivalent Ratio (LER)

Land Equivalent Ratio (LER) was calculated to compare the performance of intercrops to that of monocultures... Indicates a relative total forage yield advantage for intercropped plots if the TLER is greater than 1(Mead & Willey, 1980). 

Total LER: TLER= LA+LB= YA/SA + YB/SB
where LA and LB are the partial land equivalent ratio (PLER) for the individual crops. YA and YB are the yields of an individual crop within the intercropped plot, and SA and SB are the yields of an individual crop within a monoculture plot (Mead & Willey, 1980). 

Proportional LER (PrLER) was calculated for each species’ biomass yield to determine each species’ relative contribution to the total LER (Oyejola & Mead, 1982). PLERs can be compared to determine competitive effects between the species in intercrop... A PLER greater than 0.5 indicates a relative yield advantage for a single crop in intercrop compared to its yield at the same seeding rate in monoculture. The proportional partial land equivalent ratio (PrPLER) is the proportion of component crop A to the TLER and can be used to understand how much each intercropped crop contributes to the TLER. 

Proportional LER: PrPLER= LA/TLER
where LA is the partial land equivalent ratio (PLER) for an individual crops and TLER is the total land equivalent ratio for an intercropped plot. 


TLER, PLER, and PrLER were calculated using plots of the same N rate to allow for comparison in the performance of the intercropped system at different N rates (Oyejola & Mead, 1982). TLER and PrLER could not be calculated for grain yields, as IWG only represented one grain-bearing crop in the intercrop, but PLER was calculated for grain yield to allow for comparison between N rates

### Effects and interactions of N rate (N), cropping system (CROP), and environment (E)

Log-linear mixed-effects models with replication as a random effect (ϵ) 
log(Response variable) ~ N*E*C + ϵ
Models for each year-harvest ( Year 1 Summer, Year 1 Fall, Year 2 Summer, Year 2 Fall, Year 3 Summer, Year 3 Fall) as Summer and Fall harvests were expected to have large differences in yield, and so that the change in response variables between years could be easily captured and compared.

Response variables: Yields
- Total forage yield 
- IWG forage yield
- Alfalfa forage yield 
Response variables: LER
- TLER
- PLER of IWG
- PLER of alfalfa 
- PrPLER of IWG 
- PrPLER of alfalfa 
Cropping system (C) was not included as a fixed effect for LER, as LER values are calculated as a ratio of yield in intercropping to yield in monoculture.
Response variables: Forage quality
- Total forage CP and RFV 
- IWG forage CP and RFV
- Alfalfa CP and RFV
Forage quality only on year 1 and year 2 harvests

Analysis of covariance (ANCOVA) was used to determine significant differences (P<0.05) between independent variables and their interactions. Estimated marginal means (EMMs) were calculated and pairwise comparisons were used to understand and rank results between independent variables. 

### Data prep for analysis 

```{r}
data<-read.csv('data/Original_Data/MasterDataSpreadsheet.csv')
```
# Rows to remove due to missing data
NY 208 s22 missing alfalfa 
MN 1122 s23 missing grain 
```{r}
# 2022 Summer NY 208 is the first row in the data table
data <- data[-1, ] # 2022 Summer NY 208
# then the new row 1 becomes the next row needing to be taken out
data <- data[-1, ] # 2023 Summer MN 1122
```
# Rename variables to match models 
```{r}
data2 <- data |> 
  separate_wider_delim(Crop, delim = " + ", 
                       names = c("first_value", "second_value"), 
                       too_few = "align_start") |> 
  mutate(C = if_else(is.na(second_value), "monoculture", "intercrop")) |> 
  mutate(CROP = case_when(
    Intercropped == "y" ~ "Intercropped",  # If intercrop is "y", set CROP to intercrop
    Monocrop == "y" & ALF == "y" ~ "Mono_ALF",  # If monoculture is "y" and alfalfa is "y", set CROP to alfalfa
    Monocrop == "y" & IWG == "y" ~ "Mono_IWG",  # If monoculture is "y" and iwg is "y", set CROP to iwg
    Monocrop == "y" ~ "NA",  # If monoculture is "y" and neither alfalfa nor iwg is "y", set CROP to NA
    TRUE ~ NA_character_  # If no condition matches, assign NA
  ))

V<-data2$first_value #Variety (IWG, Shockwave, Higest, WL)
data2$V<-as.factor(V)
N<-data2$NRate # Nitrogen Rate (0, 40, 80, 120, 160)
data2$N<-as.numeric(N)
P<-data2$Location # Location ("MN", "NY", "WI", "KS")
data2$P<-as.factor(P)
data2$Rep<-as.factor(data2$Rep) # (1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16)
data2$C<-as.factor(data2$C) # Crop (intercrop, monoculture)
data2$CROP <- as.factor(data2$CROP) # Crop (intercrop, monoculture_IWG, monoculture_Alfalfa)
```

# Grain conversion

```{r}
#need to calculate the fractions 
# data points from imaging giving proportionss
# for yr 1 and 2 there are columns with plot individual info for this
data3 <- data2%>%filter(YearCode %in% c("X", "Y"))
#hull fraction 
data3$hullNHd<-data3$hull_N/(data3$hull_N+data3$nkd_N+data3$spklt_N)
#naked seed fraction 
data3$NdkNHd<-data3$nkd_N/(data3$hull_N+data3$nkd_N+data3$spklt_N)
#spiklet fraction 
data3$SpkltNHd <- ifelse(data3$spklt_N == 0, 0, data3$spklt_N / (data3$hull_N + data3$nkd_N + data3$spklt_N))

#new equation from Lee
# converted grain wieghts 
data3$WhSamDH = (0.905045351733363*data3$image_sample_wt_g)-((1.10627799960595E-05)*data3$hullNHd*data3$hull_A)+((4.10249606987368E-06)*data3$NdkNHd*data3$nkd_A)-((2.01262650442053E-05)* ifelse(is.nan(data3$SpkltNHd), 0, data3$SpkltNHd) * ifelse(is.nan(data3$spklt_A), 0, data3$spklt_A)) 

#fix below to create the right proportion and save it  
#samples sent for imaging were a subset, so have to apply the conversion factor to the subsample, need to calculate up to the whole plot samples
data3$G<-((data3$WhSamDH)/(data3$image_sample_wt_g))*(data3$PlotThreshedGrainKgHa)

# Year 3 adjustments 
# need to have naked seed weights to match the adjustments made in yr 1 and yr 2
# NY yr3 was hand threshed, so looks clean as is. No need for adjustments or dehulling
# KS, WI, and MN sending to NY to dehull
## weigh a subset of these after they are threshed. then clean that subset. Find the r^2 and if good (~80) then use to estimate a clean weight for the rest of the samples
data4 <- data2%>%filter(YearCode == "Z")
data4$hullNHd <- ""
data4$NdkNHd <- ""
data4$SpkltNHd <- ""
data4$WhSamDH <- ""
data4$G <- data4$PlotThreshedGrainKgHa
data_fixed <- rbind(data3,data4)
```

# Making things numeric as needed 
```{r}
data_fixed$G<-as.numeric(data_fixed$G)
data_fixed$PlotIWGDryKgHa<-as.numeric(data_fixed$PlotIWGDryKgHa)
data_fixed$PlotAlfDryKgHa<-as.numeric(data_fixed$PlotAlfDryKgHa)
data_fixed$PlotTotForageKgHa<-as.numeric(data_fixed$PlotTotForageKgHa)
data_fixed$IWGCP<-as.numeric(data_fixed$IWGCP)
data_fixed$IWGdNDF48<-as.numeric(data_fixed$IWGdNDF48)
data_fixed$IWGLignin<-as.numeric(data_fixed$IWGLignin)
data_fixed$ALFCP<-as.numeric(data_fixed$ALFCP)
data_fixed$ALFdNDF48<-as.numeric(data_fixed$ALFdNDF48)
data_fixed$ALFLignin<-as.numeric(data_fixed$ALFLignin)
data_fixed$ALFADF<-as.numeric(data_fixed$ALFADF)
data_fixed$IWGADF<-as.numeric(data_fixed$IWGADF)
data_fixed$ALFaNDF<-as.numeric(data_fixed$ALFaNDF)
custom_letters <- c("a", "b", "c", "d", "e", "f", "g","h","i","j","k","l","m","n","o","p","q","r","s","t","u","v","w","x","y","z")  # Customize the letters as needed
```

# Nrate data isolation
```{r}
#Just shockwave 
Nd<-data_fixed[data_fixed$first_value != "WL" & data_fixed$first_value != "Higest" ,]

Nd <- Nd %>%
  mutate(CROP = case_when(
    `Crop1` == "Shockwave" ~ "monoA",
    `Crop1` == "IWG" ~ "monoI",
    `Crop1` == "Shockwave + IWG" ~ "inter",
    TRUE ~ NA_character_  # Handle other cases if any
  ))

# MN 2024 has some Filler plots which get the NA character, but code later in this script dosn't like it. 
# So removing these here
Nd <- Nd %>%
  filter(!is.na(CROP))
```

```{r}
#Year
NdX<-Nd[Nd$YearCode == "X",]
NdY<-Nd[Nd$YearCode == "Y",]
NdZ<-Nd[Nd$YearCode == "Z",]

#REMOVE this once you get the corrected year 2 grain values in 
NdY$G<-NdY$PlotThreshedGrainKgHa

#Harvest 
NdXS<-NdX[NdX$Harvest == "Summer",]
NdXF<-NdX[NdX$Harvest == "Fall",]

NdYS<-NdY[NdY$Harvest == "Summer",]
NdYF<-NdY[NdY$Harvest == "Fall",]

NdZS<-NdZ[NdZ$Harvest == "Summer",]
NdZF<-NdZ[NdZ$Harvest == "Fall",]

#IWG vs ALF 
NdXSI<-NdXS[NdXS$Crop1 != "Shockwave",]
NdXSA<-NdXS[NdXS$Crop1 != "IWG",]

NdXFI<-NdXF[NdXF$Crop1 != "Shockwave",]
NdXFA<-NdXF[NdXF$Crop1 != "IWG",]

NdYSI<-NdYS[NdYS$Crop1 != "Shockwave" ,]
NdYSA<-NdYS[NdYS$Crop1 != "IWG",]

NdYFI<-NdYF[NdYF$Crop1 != "Shockwave",]
NdYFA<-NdYF[NdYF$Crop1 != "IWG",]

NdZSI<-NdZS[NdZS$Crop1 != "Shockwave" ,]
NdZSA<-NdZS[NdZS$Crop1 != "IWG",]

NdZFI<-NdZF[NdZF$Crop1 != "Shockwave",]
NdZFA<-NdZF[NdZF$Crop1 != "IWG",]
```

```{r}
#adding year 1 mn grain to the G column because they were actually dehulled instead of imaged for using the equation
NdXSInoMN<-NdXSI[NdXSI$Location != "MN",]
NdXSIMN<-NdXSI[NdXSI$Location == "MN",]
NdXSIMN$G<-NdXSIMN$X2023MNGrainDeHulledKgHa
NdXSIG<-rbind(NdXSInoMN, NdXSIMN)
```

## Total Forage Yield 

* Table (Estimated effect of nitrogen rate on total forage yield for each environment (Site) and cropping system across harvests) : combine the "sorted_df" that is created at the end of the chunk for each forage model

* Figure (Total forage yield response to environment and cropping system for Year 2 Fall) : total forage figure E:C (YF)

# Total forage year 1 summer
```{r}
#linear
modNXST<-lmer(PlotTotForageKgHa~N*P*CROP + (1|Rep), data=NdXS)
anova(modNXST)
#Check Assumptions
NXST_resid<-resid(modNXST)
qqnorm(NXST_resid)
qqline(NXST_resid)
plot(modNXST)
#Logtransform
modNXST1<-lmer(log(PlotTotForageKgHa)~N*P*CROP + (1|Rep), data=NdXS)
anova(modNXST1)
summary(modNXST1)
#check assumptions logtransform
NXST_resid1<-resid(modNXST1)
qqnorm(NXST_resid1)
qqline(NXST_resid1)
plot(modNXST1)


modNXST1_summary <- summary(modNXST1)
modNXST1_coeff <- as.data.frame(modNXST1_summary$coefficients)%>%
  filter(`Pr(>|t|)` < 0.05)
colnames(modNXST1_coeff)[5]<-"Pr(>t)"
# Create custom table using kable and kableExtra
save_kable(
   knitr::kable(modNXST1_coeff, 
                caption = "Y1 Summer Mixed-Effects Model: log(PlotTotForageKgHa) ~ Nrate * Location * CROPsystem + (1 | Rep)") %>%
       kable_styling(full_width = TRUE, 
                     position = "center", 
                     bootstrap_options = c("striped", "hover", "condensed")),
   file = "figures/forage/table_significant_coeff_yr1S.html")

desired_order_P <- c("MN", "NY", "KS", "WI")
N_levels <- c(0, 40, 80, 120, 160)



#plot log-linear by location (log)
NdXS$predicted <- predict(modNXST1, newdata = NdXS, re.form = NA)
ggplot(NdXS, aes(x = N, y = PlotTotForageKgHa , color = CROP, group = CROP)) +
    geom_point() + 
  geom_line(aes(N, exp(predicted)))+ #regression through backtransformed predicted values
  labs(x = "N-Rate (Kg/ha)", y = "Grain Yield (log scale)") +
  ggtitle("Yr 1 S Relationship between Total Forage Yield and Nrate") +
  scale_x_continuous(breaks = c(0, 40, 80, 120, 160)) +
  ylim(0,15000)+
  facet_wrap(~P, scales = "free_y", ncol = 2) +
  scale_color_discrete(name = "Cropping System")
# save figures/forage/totalforage_Nrate_yr1S.jpeg  775x630

### redoing figure for paper 
#N:E:CROP
# Define the desired order of 'P'
desired_order <- c("MN", "NY", "KS", "WI")
NdXS$P <- factor(NdXS$P, levels = desired_order)
# finding values for the function for each yr:location  
emtrends_resultX<-emtrends(modNXST1,~ N*P*CROP, var= "N", infer=TRUE)
  emtrends_dfX <- as.data.frame(emtrends_resultX)
  emtrends_dfX$plvl <-
    ifelse(emtrends_dfX$p.value == 0.05, ".",
    ifelse(emtrends_dfX$p.value < 0.05  & emtrends_dfX$p.value >= 0.01, "*",
    ifelse(emtrends_dfX$p.value < 0.01  & emtrends_dfX$p.value >= 0.001, "**",
    ifelse(emtrends_dfX$p.value < 0.001, "***", ""))))
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_dfX$PC <- paste0(emtrends_dfX$P,emtrends_dfX$CROP)
  emtrends_dfX$P <- factor(emtrends_dfX$P, levels = desired_order_P)
emmeans_resultsX<-emmeans(modNXST1, ~N*P*CROP, at=list(N=0))
  emmeans_dfX <- as.data.frame(emmeans_resultsX)
  emmeans_dfX$PC <- paste0(emmeans_dfX$P,emmeans_dfX$CROP)
mergedX <- emtrends_dfX %>%
  inner_join(emmeans_dfX, by = c("PC")) %>%
  dplyr::select(PC, P.x, CROP.x, emmean, N.trend, SE.x, plvl)
  colnames(mergedX)[2] <- "P"
  colnames(mergedX)[3] <- "CROP"
mergedX$P <- factor(mergedX$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
X_df <- mergedX %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sortedX <- X_df %>%
  arrange(P)
sortedX
sortedX_I <- subset(sortedX, CROP== "inter")
sortedX_M <- subset(sortedX, CROP== "monoI")
sortedX_A <- subset(sortedX, CROP== "monoA")

sym_I <- sortedX_I %>%
  distinct(P) %>%
  mutate(
    x_sym = 0,
    y_sym = 15000
  )
sym_M <- sortedX_M %>%
  distinct(P) %>%
  mutate(
    x_sym = 0,
    y_sym = 14000
  )
sym_A <- sortedX_A %>%
  distinct(P) %>%
  mutate(
    x_sym = 0,
    y_sym = 14500
  )

#plot
TFcomboplotNEXS <- ggplot(data=NdXS) +
  geom_point(data = NdXS, aes(x = N, y = PlotTotForageKgHa, shape = CROP)) +
  labs(x = "N-Rate (Kg ha-1)", y = "Total Forage", linetype = "Cropping System", shape = "Cropping System", color = "Harvest")+
  scale_x_continuous(breaks = c(0, 40, 80, 120, 160)) +
 # ylim(0, 1000) +
  facet_wrap(~P, scales = "free_y", ncol = 2) +
  scale_shape_manual(values = c(4, 1, 25),labels = c("Intercropped","Monoculture Alfalfa", "Monoculture IWG"))+
  # functions come from equation in sorted
  geom_function(data=subset(NdXS, P== "MN" & CROP == "inter"), fun=~3721.48*exp(0.0005*.x),color='darkgrey')+
  geom_function(data=subset(NdXS, P== "MN" & CROP == "monoA"), fun=~3843.28*exp(-0.0014*.x),color='darkgrey')+
  geom_function(data=subset(NdXS, P== "MN" & CROP == "monoI"), fun=~2148.29*exp(0.0031*.x),color='darkgrey')+
  geom_function(data=subset(NdXS, P== "NY" & CROP == "inter"), fun=~6934.49*exp(-0.0003*.x),color='darkgrey')+
  geom_function(data=subset(NdXS, P== "NY" & CROP == "monoA"), fun=~6121.53*exp(-0.0007*.x),color='darkgrey')+
  geom_function(data=subset(NdXS, P== "NY" & CROP == "monoI"), fun=~4217.30*exp(0.0047*.x),color='darkgrey')+
  geom_function(data=subset(NdXS, P== "KS" & CROP == "inter"), fun=~9330.66*exp(0.0005*.x),color='darkgrey')+
  geom_function(data=subset(NdXS, P== "KS" & CROP == "monoA"), fun=~7425.63*exp(0.0010*.x),color='darkgrey')+
  geom_function(data=subset(NdXS, P== "KS" & CROP == "monoI"), fun=~11257.42*exp(0.0004*.x),color='darkgrey')+
  geom_function(data=subset(NdXS, P== "WI" & CROP == "inter"), fun=~7398.95*exp(0.0002*.x),color='darkgrey')+
  geom_function(data=subset(NdXS, P== "WI" & CROP == "monoA"), fun=~5647.65*exp(0.0004*.x),color='darkgrey')+
  geom_function(data=subset(NdXS, P== "WI" & CROP == "monoI"), fun=~8774.71*exp(0.0008*.x),color='darkgrey')+
  geom_text(data = sortedX_I, mapping = aes(x = 30, y = 15000, label = equation),  size=2)+ # add equation to figure
  geom_point(data = sym_I, aes(x = x_sym, y = y_sym), shape = 4, size = 1, inherit.aes = FALSE)+
  geom_text(data = sortedX_A, mapping = aes(x = 30, y = 14500, label = equation),  size=2)+ # add equation to figure
  geom_point(data = sym_A, aes(x = x_sym, y = y_sym), shape = 1, size = 2, inherit.aes = FALSE)+
  geom_text(data = sortedX_M, mapping = aes(x = 30, y = 14000, label = equation),  size=2)+ # add equation to figure
  geom_point(data = sym_M, aes(x = x_sym, y = y_sym), shape = 25, size = 1, fill = "lightgrey", stroke = 0.6, inherit.aes = FALSE)+
  geom_text(data = sortedX, mapping = aes(x = 60, y = 15000, label = plvl)) # add stars to figure
print(TFcomboplotNEXS)
# ggsave("figures/forage/TFcomboplotNEXS.jpg", plot = TFcomboplotNEXS, width = 10, height = 8, dpi = 300)



#Three way means
NXST1emm <- compute_emmeansNXS("modNXST1")
#write.csv(NXST1emm, 'data/Final_Data/NXST1emm.csv')

#Pairwise N:P:C
emmsNPC <- emmeans(modNXST1, ~ N*P*CROP,at= list(N = N_levels), type= "response") 
cld_dataNXSTNPC <- cld(emmsNPC, Letters=custom_letters) # Create compact letter display
cld_dataNXSTNPC$response <- format(cld_dataNXSTNPC$response, digits = 5)
rownames(cld_dataNXSTNPC) <- NULL
cld_dataNXSTNPC<- cld_dataNXSTNPC %>%
  select(N, P, CROP, response, .group)
colnames(cld_dataNXSTNPC) <- c("N", "Site", "Cropping System", "Total Forage (kg ha-1)", "Group")
cld_dataNXSTNPC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)

#This gives us the slope for each interactions as well as a P value indicating significance level for that slope
emtrends(modNXST1,~ P*CROP, var= "N", infer=TRUE)
  summary(modNXST1)
emtrends(modNXST1,~ P, var= "N", infer=TRUE)
emtrends(modNXST1,~ CROP, var= "N", infer=TRUE)

#emmeans for intercepts! via erika
emtrends_result<-emtrends(modNXST1,~ P*CROP, var= "N", infer=TRUE)
emtrends_df <- as.data.frame(emtrends_result)
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
emmeans_results<-emmeans(modNXST1, ~P*CROP, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("P", "CROP")) %>%
  select(P, CROP, emmean, N.trend, SE.x)
#view(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
merged_df$CROP <- factor(merged_df$CROP, levels = c("inter", "monoI","monoA"))  # Preferred order for CROP
# Create a new data frame with the calculated column
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sorted_df <- new_df %>%
  arrange(P, CROP)
#View(sorted_df)
#write.csv(sorted_df, "data/Final_Data/Nrate_esteff_totalforage_yr1S.csv")


#P:C scatter plot
emmsPC <- emmeans(modNXST1, ~ P*CROP, type = "response") # Obtain estimated marginal means (excluding N)
emms_df <- as.data.frame(emmsPC)
cld_dataXSPC <- cld(emmsPC, Letters=custom_letters)
cld_df <-as.data.frame(cld_dataXSPC)
merged_df <- merge(emms_df, cld_df,by = c("P", "CROP"))

custom_labels <- c("Intercrop", "Monoculture Alfalfa","Monoculture IWG")
custom_colors <- c("darkmagenta","coral1", "cyan") 

TFXSPC<-ggplot(NdXS, aes(x = P, y = exp(predicted), color = CROP)) +
  geom_jitter(width = 0.2, height = 0, size = 3, alpha = 0.7) +
  labs(x = "Environment", y = "Total Forage Yield") +
  geom_point(data = emms_df, aes(x = P, y = response), 
             size = 4, shape = 18, color = "black")+ 
  geom_errorbar(data = emms_df, aes(x = P, ymin = lower.CL, ymax = upper.CL), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  geom_text(data = merged_df, aes(x = P, y = response.x, label = .group), 
            color = "black", vjust = 0, hjust = 2.5)+
  scale_color_manual(name = "Cropping System", labels = custom_labels,values = custom_colors)+
  theme(plot.title = element_text(hjust = 0.5))

print(TFXSPC)
#ggsave("figures/forage/TFXSPC.jpg", plot = TFXSPC, width = 10, height = 8, dpi = 300)
```

# Total forage year 1 fall 
```{r}
#linear
NdXF$PlotTotForageKgHa<-as.numeric(NdXF$PlotTotForageKgHa)
modNXFT<-lmer(PlotTotForageKgHa~N*P*CROP + (1|Rep), data=NdXF)
anova(modNXFT)
summary(modNXFT)
#Check Assumptions
NXFT_resid<-resid(modNXFT)
qqnorm(NXFT_resid)
qqline(NXFT_resid)
plot(modNXFT)
#Check Assumptions Linear logtrans
modNXFT1<-lmer(log(PlotTotForageKgHa)~N*P*CROP + (1|Rep), data=NdXF)
anova(modNXFT1)
NXFT1_resid<-resid(modNXFT1)
qqnorm(NXFT1_resid)
qqline(NXFT1_resid)
plot(modNXFT1)

modNXFT1_summary <- summary(modNXFT1)
modNXFT1_coeff <- as.data.frame(modNXFT1_summary$coefficients)%>%
  filter(`Pr(>|t|)` < 0.05)
colnames(modNXFT1_coeff)[5]<-"Pr(>t)"
 #Create custom table using kable and kableExtra
save_kable(
   knitr::kable(modNXFT1_coeff, 
                caption = "Y1 Fall Mixed-Effects Model: log(PlotTotForageKgHa) ~ Nrate * Location * CROPsystem + (1 | Rep)") %>%
       kable_styling(full_width = TRUE, 
                     position = "center", 
                     bootstrap_options = c("striped", "hover", "condensed")),
   file = "figures/forage/table_significant_coeff_yr1F.html")
# save table_significant_coeff_yr1F

#plots
NdXF$predicted <- predict(modNXFT1, newdata = NdXF, re.form = NA)
ggplot(NdXF, aes(x = N, y = PlotTotForageKgHa, color = CROP, group= CROP)) +
    geom_point() + 
  geom_line(aes(N, exp(predicted)))+ #regression through backtransformed predicted values
  labs(x = "N-Rate (Kg/ha)", y = "Total Forage Yield (Kg/ha)") +  # Label the axes
  ggtitle("Yr 1 F Relationship between Total Forage Yield and N-rate") +  # Add a title
scale_x_continuous(breaks = c(0, 40, 80, 120, 160))+ #fix x axis scale
  ylim(0, 3300) +
  facet_wrap(~P, scales = "free_y",ncol=2)+ #make it by location (remove to make it across locations)
  scale_color_discrete(name = "Cropping System")  #legend for colors
# save figures/forage/totalforage_Nrate_yr1F.jpeg  775x630

#N:E:CROP
# Define the desired order of 'P'
desired_order <- c("MN", "NY", "WI")
NdXF$P <- factor(NdXF$P, levels = desired_order)
# finding values for the function for each yr:location  
emtrends_resultXF<-emtrends(modNXFT1,~ N*P*CROP, var= "N", infer=TRUE)
  emtrends_dfXF <- as.data.frame(emtrends_resultXF)
  emtrends_dfXF$plvl <-
    ifelse(emtrends_dfXF$p.value == 0.05, ".",
    ifelse(emtrends_dfXF$p.value < 0.05  & emtrends_dfXF$p.value >= 0.01, "*",
    ifelse(emtrends_dfXF$p.value < 0.01  & emtrends_dfXF$p.value >= 0.001, "**",
    ifelse(emtrends_dfXF$p.value < 0.001, "***", ""))))
  desired_order_P <- c("MN", "NY", "WI")
  emtrends_dfXF$PC <- paste0(emtrends_dfXF$P,emtrends_dfXF$CROP)
  emtrends_dfXF$P <- factor(emtrends_dfXF$P, levels = desired_order_P)
emmeans_resultsXF<-emmeans(modNXFT1, ~N*P*CROP, at=list(N=0))
  emmeans_dfXF <- as.data.frame(emmeans_resultsXF)
  emmeans_dfXF$PC <- paste0(emmeans_dfXF$P,emmeans_dfXF$CROP)
mergedXF <- emtrends_dfXF %>%
  inner_join(emmeans_dfXF, by = c("PC")) %>%
  dplyr::select(PC, P.x, CROP.x, emmean, N.trend, SE.x, plvl)
  colnames(mergedXF)[2] <- "P"
  colnames(mergedXF)[3] <- "CROP"
mergedXF$P <- factor(mergedXF$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
XF_df <- mergedXF %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sortedXF <- XF_df %>%
  arrange(P)
sortedXF
sortedXF_I <- subset(sortedXF, CROP== "inter")
sortedXF_M <- subset(sortedXF, CROP== "monoI")
sortedXF_A <- subset(sortedXF, CROP== "monoA")

sym_I <- sortedXF_I %>%
  distinct(P) %>%
  mutate(
    x_sym = 0,
    y_sym = 4000
  )
sym_M <- sortedXF_M %>%
  distinct(P) %>%
  mutate(
    x_sym = 0,
    y_sym = 3750
  )
sym_A <- sortedX_A %>%
  distinct(P) %>%
  mutate(
    x_sym = 0,
    y_sym = 3500
  )

#plot
TFcomboplotNEXF <- ggplot(data=NdXF) +
  geom_point(data = NdXF, aes(x = N, y = PlotTotForageKgHa, shape = CROP)) +
  labs(x = "N-Rate (Kg ha-1)", y = "Total Forage", linetype = "Cropping System", shape = "Cropping System", color = "Harvest")+
  scale_x_continuous(breaks = c(0, 40, 80, 120, 160)) +
 # ylim(0, 1000) +
  facet_wrap(~P, scales = "free_y", ncol = 2) +
  scale_shape_manual(values = c(4, 1, 25),labels = c("Intercropped","Monoculture Alfalfa", "Monoculture IWG"))+
  # functions come from equation in sorted
  geom_function(data=subset(NdXS, P== "MN" & CROP == "inter"), fun=~1981.94*exp(-0.0009*.x),color='darkgrey')+
  geom_function(data=subset(NdXS, P== "MN" & CROP == "monoA"), fun=~1929.21*exp(0.0002*.x),color='darkgrey')+
  geom_function(data=subset(NdXS, P== "MN" & CROP == "monoI"), fun=~945.42*exp(0.0026*.x),color='darkgrey')+
  geom_function(data=subset(NdXS, P== "NY" & CROP == "inter"), fun=~2649.55*exp(-0.0009*.x),color='darkgrey')+
  geom_function(data=subset(NdXS, P== "NY" & CROP == "monoA"), fun=~2904.26*exp(-0.0007*.x),color='darkgrey')+
  geom_function(data=subset(NdXS, P== "NY" & CROP == "monoI"), fun=~179.98*exp(0.0059*.x),color='darkgrey')+
  geom_function(data=subset(NdXS, P== "WI" & CROP == "inter"), fun=~479.80*exp(-0.0005*.x),color='darkgrey')+
  geom_function(data=subset(NdXS, P== "WI" & CROP == "monoA"), fun=~173.11*exp(-0.0002*.x),color='darkgrey')+
  geom_function(data=subset(NdXS, P== "WI" & CROP == "monoI"), fun=~297.71*exp(-0.0006*.x),color='darkgrey')+
  geom_text(data = sortedXF_I, mapping = aes(x = 30, y = 4000, label = equation),  size=2)+ # add equation to figure
  geom_point(data = sym_I, aes(x = x_sym, y = y_sym), shape = 4, size = 1, inherit.aes = FALSE)+
  geom_text(data = sortedXF_A, mapping = aes(x = 30, y = 3750, label = equation),  size=2)+ # add equation to figure
  geom_point(data = sym_A, aes(x = x_sym, y = y_sym), shape = 1, size = 2, inherit.aes = FALSE)+
  geom_text(data = sortedXF_M, mapping = aes(x = 30, y = 3500, label = equation),  size=2)+ # add equation to figure
  geom_point(data = sym_M, aes(x = x_sym, y = y_sym), shape = 25, size = 1, fill = "lightgrey", stroke = 0.6, inherit.aes = FALSE)+
  geom_text(data = sortedXF, mapping = aes(x = 60, y = 3500, label = plvl)) # add stars to figure
print(TFcomboplotNEXF)
# ggsave("figures/forage/TFcomboplotNEXF.jpg", plot = TFcomboplotNEXF, width = 10, height = 8, dpi = 300)





#Threeway means
NXFT1emm <- compute_emmeansNXF("modNXFT1")
#write.csv(NXFT1emm, 'data/Final_Data/NXFT1emm.csv')

#Pairwise N:P:C
emmsNPC <- emmeans(modNXFT1, ~ N*P*CROP,at= list(N = N_levels), type= "response") 
cld_dataNXFTNPC <- cld(emmsNPC, Letters=custom_letters) # Create compact letter display
cld_dataNXFTNPC$response <- format(cld_dataNXFTNPC$response, digits = 5)
rownames(cld_dataNXFTNPC) <- NULL
cld_dataNXFTNPC<- cld_dataNXFTNPC %>%
  select(N, P, CROP, response, .group)
colnames(cld_dataNXFTNPC) <- c("N", "Site", "Cropping System", "Total Forage (kg ha-1)", "Group")
cld_dataNXFTNPC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)

#This gives us the slope for each interactions as well as a P value indicating significance level for that slope
emtrends_result<-emtrends(modNXFT1,~ P*CROP, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
  #view(emtrends_df)
emtrends(modNXFT1,~ P, var= "N", infer=TRUE)
emtrends(modNXFT1,~ CROP, var= "N", infer=TRUE)

#equations table
emtrends_result<-emtrends(modNXFT1,~ P*CROP, var= "N", infer=TRUE)
emtrends_df <- as.data.frame(emtrends_result)
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
emmeans_results<-emmeans(modNXFT1, ~P*CROP, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("P", "CROP")) %>%
  select(P, CROP, emmean, N.trend, SE.x)
#view(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
merged_df$CROP <- factor(merged_df$CROP, levels = c("inter", "monoI","monoA"))  # Preferred order for CROP
# Create a new data frame with the calculated column
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sorted_df <- new_df %>%
  arrange(P, CROP)
#View(sorted_df)
#write.csv(sorted_df, "data/Final_Data/Nrate_esteff_totalforage_yr1F.csv")

#P:C scatter plot
emmsPC <- emmeans(modNXFT1, ~ P*CROP, type = "response") # Obtain estimated marginal means (excluding N)
emms_df <- as.data.frame(emmsPC)
cld_dataXFPC <- cld(emmsPC, Letters=custom_letters)
cld_df <-as.data.frame(cld_dataXFPC)
merged_df <- merge(emms_df, cld_df,by = c("P", "CROP"))

custom_labels <- c("Intercrop", "Monoculture Alfalfa","Monoculture IWG")
custom_colors <- c("darkmagenta","coral1", "cyan") 

TFXFPC<-ggplot(NdXF, aes(x = P, y = exp(predicted), color = CROP)) +
  geom_jitter(width = 0.2, height = 0, size = 3, alpha = 0.7) +
  labs(x = "Environment", y = "Total Forage Yield") +
  geom_point(data = emms_df, aes(x = P, y = response), 
             size = 4, shape = 18, color = "black")+ 
  geom_errorbar(data = emms_df, aes(x = P, ymin = lower.CL, ymax = upper.CL), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  geom_text(data = merged_df, aes(x = P, y = response.x, label = .group), 
            color = "black", vjust = 0, hjust = 2.5)+
  scale_color_manual(name = "Cropping System", labels = custom_labels,values = custom_colors)+
  theme(plot.title = element_text(hjust = 0.5))

print(TFXFPC)
#ggsave("figures/forage/TFXFPC.jpg", plot = TFXFPC, width = 10, height = 8, dpi = 300)
```

# Total forage year 2 summer
```{r}
#linear
modNYST<-lmer(PlotTotForageKgHa~N*P*CROP + (1|Rep), data=NdYS)
anova(modNYST)
#Check Assumptions
NYST_resid<-resid(modNYST)
qqnorm(NYST_resid)
qqline(NYST_resid)
plot(modNYST)
#Logtransform
modNYST1<-lmer(log(PlotTotForageKgHa+0.0001)~N*P*CROP + (1|Rep), data=NdYS)
anova(modNYST1)
summary(modNYST1)
#check assumptions logtransform
NYST_resid1<-resid(modNYST1)
qqnorm(NYST_resid1)
qqline(NYST_resid1)
plot(modNYST1)
# normal looks much better than log transformed 

# rest of analysis done with non-transformed data

modNYST_summary <- summary(modNYST)
modNYST_coeff <- as.data.frame(modNYST_summary$coefficients)%>%
  filter(`Pr(>|t|)` < 0.05)
colnames(modNYST_coeff)[5]<-"Pr(>t)"
# Create custom table using kable and kableExtra
save_kable(
   knitr::kable(modNYST_coeff, 
                caption = "Y2 Summer Mixed-Effects Model: PlotTotForageKgHa ~ Nrate * Location * CROPsystem + (1 | Rep)") %>%
       kable_styling(full_width = TRUE, 
                     position = "center", 
                     bootstrap_options = c("striped", "hover", "condensed")),
   file = "figures/forage/table_significant_coeff_yr2S.html")
# save table_significant_coeff_yr2S


max(NdYS$PlotTotForageKgHa)
#linear plots
NdYS$predicted <- predict(modNYST, newdata = NdYS, re.form = NA)
ggplot(NdYS, aes(x = N, y = PlotTotForageKgHa, color = CROP, group= CROP)) +
  geom_point() +
  geom_line(aes(N, predicted))+ #regression through predicted values
  labs(x = "N-Rate (Kg/ha)", y = "Total Forage Yield (Kg/ha)") +  # Label the axes
  ggtitle("Yr 2 S Relationship between Total Forage Yield and N-rate") +  # Add a title
scale_x_continuous(breaks = c(0, 40, 80, 120, 160))+ #fix x axis scale
  ylim(0, 9000) +
  facet_wrap(~P, scales = "free_y",ncol=2)+ #make it by location (remove to make it across locations)
  scale_color_discrete(name = "Cropping System")  #legend for colors
# save figures/forage/totalforage_Nrate_yr2S.jpeg


#N:E:CROP
# Define the desired order of 'P'
desired_order <- c("MN", "NY", "KS", "WI")
NdYS$P <- factor(NdYS$P, levels = desired_order)
# finding values for the function for each yr:location  
emtrends_resultYS<-emtrends(modNYST,~ N*P*CROP, var= "N", infer=TRUE)
  emtrends_dfYS <- as.data.frame(emtrends_resultYS)
  emtrends_dfYS$plvl <-
    ifelse(emtrends_dfYS$p.value == 0.05, ".",
    ifelse(emtrends_dfYS$p.value < 0.05  & emtrends_dfYS$p.value >= 0.01, "*",
    ifelse(emtrends_dfYS$p.value < 0.01  & emtrends_dfYS$p.value >= 0.001, "**",
    ifelse(emtrends_dfYS$p.value < 0.001, "***", ""))))
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_dfYS$PC <- paste0(emtrends_dfYS$P,emtrends_dfYS$CROP)
  emtrends_dfYS$P <- factor(emtrends_dfYS$P, levels = desired_order_P)
emtrends_resultYS<-emmeans(modNYST, ~N*P*CROP, at=list(N=0))
  emmeans_dfYS <- as.data.frame(emtrends_resultYS)
  emmeans_dfYS$PC <- paste0(emmeans_dfYS$P,emmeans_dfYS$CROP)
mergedYS <- emtrends_dfYS %>%
  inner_join(emmeans_dfYS, by = c("PC")) %>%
  dplyr::select(PC, P.x, CROP.x, emmean, N.trend, SE.x, plvl)
  colnames(mergedYS)[2] <- "P"
  colnames(mergedYS)[3] <- "CROP"
mergedYS$P <- factor(mergedYS$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
YS_df <- mergedYS %>%
  mutate(equation = sprintf("=%.2f+(%.4fN)", emmean, N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", ((N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sortedYS <- YS_df %>%
  arrange(P)
sortedYS_I <- subset(sortedYS, CROP== "inter")
sortedYS_M <- subset(sortedYS, CROP== "monoI")
sortedYS_A <- subset(sortedYS, CROP== "monoA")

sym_I <- sortedYS_I %>%
  distinct(P) %>%
  mutate(
    x_sym = 0,
    y_sym = 8000
  )
sym_M <- sortedYS_M %>%
  distinct(P) %>%
  mutate(
    x_sym = 0,
    y_sym = 7750
  )
sym_A <- sortedYS_A %>%
  distinct(P) %>%
  mutate(
    x_sym = 0,
    y_sym = 7500
  )

#plot
TFcomboplotNEYS <- ggplot(data=NdYS) +
  geom_point(data = NdYS, aes(x = N, y = PlotTotForageKgHa, shape = CROP)) +
  labs(x = "N-Rate (Kg ha-1)", y = "Total Forage", linetype = "Cropping System", shape = "Cropping System", color = "Harvest")+
  scale_x_continuous(breaks = c(0, 40, 80, 120, 160)) +
 # ylim(0, 1000) +
  facet_wrap(~P, scales = "free_y", ncol = 2) +
  scale_shape_manual(values = c(4, 1, 25),labels = c("Intercropped","Monoculture Alfalfa", "Monoculture IWG"))+
  # functions come from equation in sorted
  geom_function(data=subset(NdYS, P== "MN" & CROP == "inter"), fun=~4778.60+(1.6209*.x),color='darkgrey')+
  geom_function(data=subset(NdYS, P== "MN" & CROP == "monoA"), fun=~2246.75+(-2.8717*.x),color='darkgrey')+
  geom_function(data=subset(NdYS, P== "MN" & CROP == "monoI"), fun=~4619.59+(10.0768*.x),color='darkgrey')+
  geom_function(data=subset(NdYS, P== "NY" & CROP == "inter"), fun=~5426.57+(9.3543*.x),color='darkgrey')+
  geom_function(data=subset(NdYS, P== "NY" & CROP == "monoA"), fun=~4068.33+(-3.3676*.x),color='darkgrey')+
  geom_function(data=subset(NdYS, P== "NY" & CROP == "monoI"), fun=~2965.31+(20.9748*.x),color='darkgrey')+
  geom_function(data=subset(NdYS, P== "KS" & CROP == "inter"), fun=~2530.88+(0.2515*.x),color='darkgrey')+
  geom_function(data=subset(NdYS, P== "KS" & CROP == "monoA"), fun=~1469.55+(6.8384*.x),color='darkgrey')+
  geom_function(data=subset(NdYS, P== "KS" & CROP == "monoI"), fun=~2976.99+(1.5081*.x),color='darkgrey')+  
  geom_function(data=subset(NdYS, P== "WI" & CROP == "inter"), fun=~5559.87+(6.2604*.x),color='darkgrey')+
  geom_function(data=subset(NdYS, P== "WI" & CROP == "monoA"), fun=~4073.61+(2.7205*.x),color='darkgrey')+
  geom_function(data=subset(NdYS, P== "WI" & CROP == "monoI"), fun=~3826.49+(23.1963*.x),color='darkgrey')+
  geom_text(data = sortedYS_I, mapping = aes(x = 30, y = 8000, label = equation),  size=2)+ # add equation to figure
  geom_point(data = sym_I, aes(x = x_sym, y = y_sym), shape = 4, size = 1, inherit.aes = FALSE)+
  geom_text(data = sortedYS_A, mapping = aes(x = 30, y = 7750, label = equation),  size=2)+ # add equation to figure
  geom_point(data = sym_A, aes(x = x_sym, y = y_sym), shape = 1, size = 2, inherit.aes = FALSE)+
  geom_text(data = sortedYS_M, mapping = aes(x = 30, y = 7500, label = equation),  size=2)+ # add equation to figure
  geom_point(data = sym_M, aes(x = x_sym, y = y_sym), shape = 25, size = 1, fill = "lightgrey", stroke = 0.6, inherit.aes = FALSE)+
  geom_text(data = sortedYS_I, mapping = aes(x = 60, y = 8000, label = plvl))+
  geom_text(data = sortedYS_M, mapping = aes(x = 60, y = 7500, label = plvl)) # add stars to figure
# add stars to figure
print(TFcomboplotNEYS)
# ggsave("figures/forage/TFcomboplotNEYS.jpg", plot = TFcomboplotNEYS, width = 10, height = 8, dpi = 300)





#Threeway means
NYST1emm <- compute_emmeansNYS("modNYST")
#write.csv(NYST1emm, 'data/NYST1emm.csv')

#Pairwise N:P:C
emmsNPC <- emmeans(modNYST, ~ N*P*CROP,at= list(N = N_levels), type= "response") 
cld_dataNYSTNPC <- cld(emmsNPC, Letters=custom_letters) # Create compact letter display
cld_dataNYSTNPC$response <- format(cld_dataNYSTNPC$emmean, digits = 5) # column is named $emmean not $response 
rownames(cld_dataNYSTNPC) <- NULL
cld_dataNYSTNPC<- cld_dataNYSTNPC %>%
  select(N, P, CROP, response, .group)
colnames(cld_dataNYSTNPC) <- c("N", "Site", "Cropping System", "Total Forage (kg ha-1)", "Group")
cld_dataNYSTNPC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)


#This gives us the slope for each interactions as well as a P value indicating significance level for that slope
emtrends_result<-emtrends(modNYST,~ P*CROP, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
  #view(emtrends_df)
emtrends(modNYST,~ P, var= "N", infer=TRUE)
emtrends(modNYST,~ CROP, var= "N", infer=TRUE)

#equations table
emtrends_result<-emtrends(modNYST,~ P*CROP, var= "N", infer=TRUE)
emtrends_df <- as.data.frame(emtrends_result)
emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
emmeans_results<-emmeans(modNYST, ~P*CROP, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("P", "CROP")) %>%
  select(P, CROP, emmean, N.trend, SE.x)
#view(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
merged_df$CROP <- factor(merged_df$CROP, levels = c("inter", "monoI","monoA"))  # Preferred order for CROP
# Create a new data frame with the calculated column
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", emmean, N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", ((N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sorted_df <- new_df %>%
  arrange(P, CROP)
#View(sorted_df)
#write.csv(sorted_df, "data/Final_Data/Nrate_esteff_totalforage_yr2S_2.csv")

#P:C scatter plot
emmsPC <- emmeans(modNYST, ~ P*CROP, type = "response") # Obtain estimated marginal means (excluding N)
emms_df <- as.data.frame(emmsPC)
cld_dataYSPC <- cld(emmsPC, Letters=custom_letters)
cld_df <-as.data.frame(cld_dataYSPC)
merged_df <- merge(emms_df, cld_df,by = c("P", "CROP"))

custom_labels <- c("Intercrop", "Monoculture Alfalfa","Monoculture IWG")
custom_colors <- c("darkmagenta","coral1", "cyan") 

TFYSPC<-ggplot(NdYS, aes(x = P, y = (predicted), color = CROP)) +
  geom_jitter(width = 0.2, height = 0, size = 3, alpha = 0.7) +
  labs(x = "Environment", y = "Total Forage Yield") +
  geom_point(data = emms_df, aes(x = P, y = emmean), 
             size = 4, shape = 18, color = "black")+ 
  geom_errorbar(data = emms_df, aes(x = P, ymin = lower.CL, ymax = upper.CL), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  geom_text(data = merged_df, aes(x = P, y = emmean.x, label = .group), 
            color = "black", vjust = 0, hjust = 2.5)+
  scale_color_manual(name = "Cropping System", labels = custom_labels,values = custom_colors)+
  theme(plot.title = element_text(hjust = 0.5))

print(TFYSPC)
#ggsave("figures/forage/TFYSPC.jpg", plot = TFYSPC, width = 10, height = 8, dpi = 300)
```

# Total forage year 2 fall
```{r}
#linear
NdYF$PlotTotForageKgHa<-as.numeric(NdYF$PlotTotForageKgHa)
NdYF$N<-as.numeric(NdYF$N)
modNYFT<-lmer(PlotTotForageKgHa~N*P*CROP + (1|Rep), data=NdYF) #linear 
anova(modNYFT)
summary(modNYFT)
#Check Assumptions
NYFT_resid<-resid(modNYFT)
qqnorm(NYFT_resid)
qqline(NYFT_resid)
plot(modNYFT)
abline(h = 0, col="red")
#Logtransform
modNYFT1<-lmer(log(PlotTotForageKgHa)~N*P*CROP + (1|Rep), data=NdYF)
NYFT_resid1<-resid(modNYFT1)
qqnorm(NYFT_resid1)
qqline(NYFT_resid1)
plot(modNYFT1)
anova(modNYFT1)

modNYFT1_summary <- summary(modNYFT1)
modNYFT1_coeff <- as.data.frame(modNYFT1_summary$coefficients)%>%
  filter(`Pr(>|t|)` < 0.05)
colnames(modNYFT1_coeff)[5]<-"Pr(>t)"
# Create custom table using kable and kableExtra
save_kable(
   knitr::kable(modNYFT1_coeff, 
                caption = "Y2 Fall Mixed-Effects Model: log(PlotTotForageKgHa) ~ Nrate * Location * CROPsystem + (1 | Rep)") %>%
       kable_styling(full_width = TRUE, 
                     position = "center", 
                     bootstrap_options = c("striped", "hover", "condensed")),
   file = "figures/forage/table_significant_coeff_yr2F.html")
# save table_significant_coeff_yr2F

#linear plots
NdYF$predicted <- predict(modNYFT1, newdata = NdYF, re.form = NA)
ggplot(NdYF, aes(x = N, y = PlotTotForageKgHa, color = CROP, group= CROP)) +
    geom_point() + geom_line(aes(N, exp(predicted)))+ #regression through backtransformed predicted values
  labs(x = "N-Rate (Kg/ha)", y = "Total Forage Yield (Kg/ha)") +  # Label the axes
  ggtitle("Yr 2 F Relationship between Total Forage Yield and N-rate") +  # Add a title
scale_x_continuous(breaks = c(0, 40, 80, 120, 160))+ #fix x axis scale
  ylim(0, 3500) +
  facet_wrap(~P, scales = "free_y",ncol=2)+ #make it by location (remove to make it across locations)
  scale_color_discrete(name = "Cropping System")  #legend for colors
# save figures/forage/totalforage_Nrate_yr2F.jpeg 775x630




#Threeway means
NYFT1emm <- compute_emmeansNYF("modNYFT1")
#write.csv(NYFT1emm, 'data/Final_Data/NYFT1emm.csv')

#Pairwise NPC
N_levels <- c(0, 40, 80, 120, 160)
emmsNPC <- emmeans(modNYFT1, specs = ~ N*P*CROP, at = list(N = N_levels), type = "response") # Obtain estimated marginal means (excluding N)
cld_dataNYFTNPC <- cld(emmsNPC, Letters=custom_letters )
#Pairwise C
emmsC <- emmeans(modNYFT1, ~ CROP, type = "response") # Obtain estimated marginal means (excluding N)
cld_dataNYFTC <- cld(emmsC, Letters=custom_letters) # Create compact letter display
cld_dataNYFTC$response <- format(cld_dataNYFTC$response, digits = 5)
cld_dataNYFTC<- cld_dataNYFTC %>%
  select(CROP, response, .group)
rownames(cld_dataNYFTC) <- NULL
colnames(cld_dataNYFTC) <- c("Cropping System", "Total Forage (kg ha-1)", "Group")
cld_dataNYFTC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)
#Pairwise N:C
N_levels <- c(0, 40, 80, 120, 160)
emmsNYFT <- emmeans(modNYFT1, specs = ~ N*CROP, at = list(N = N_levels), type = "response")
cld_dataNYFTNC <- cld(emmsNYFT, Letters=custom_letters) # Create compact letter display
cld_dataNYFTNC$response <- format(cld_dataNYFTNC$response, digits = 5)
cld_dataNYFTNC<- cld_dataNYFTNC %>%
  select(N, CROP, response, .group)
rownames(cld_dataNYFTNC) <- NULL
colnames(cld_dataNYFTNC) <- c("N", "Cropping System", "Total Forage (kg ha-1)", "Group")
cld_dataNYFTNC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)
#Pairwise P:C
emmsNYFTPC <- emmeans(modNYFT1, specs = ~ P*CROP, type = "response")
cld_dataNYFTPC <- cld(emmsNYFTPC, Letters=custom_letters) # Create compact letter display
cld_dataNYFTPC$response <- format(cld_dataNYFTPC$response, digits = 5)
cld_dataNYFTPC<- cld_dataNYFTPC %>%
  select(P, CROP, response, .group)
rownames(cld_dataNYFTPC) <- NULL
colnames(cld_dataNYFTPC) <- c("Location", "Cropping System", "Total Forage (kg ha-1)", "Group")
cld_dataNYFTPC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)


#This gives us the slope for each interactions as well as a P value indicating significance level for that slope
emtrends(modNYFT1,~ P*CROP, var= "N", infer=TRUE)
emtrends(modNYFT1,~ P, var= "N", infer=TRUE)
emtrends(modNYFT1,~ CROP, var= "N", infer=TRUE)

#equations table
emtrends_result<-emtrends(modNYFT1,~ P*CROP, var= "N", infer=TRUE)
emtrends_df <- as.data.frame(emtrends_result)
emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
emmeans_results<-emmeans(modNYFT1, ~P*CROP, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("P", "CROP")) %>%
  select(P, CROP, emmean, N.trend, SE.x)
#view(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
merged_df$CROP <- factor(merged_df$CROP, levels = c("inter", "monoI","monoA"))  # Preferred order for CROP
# Create a new data frame with the calculated column
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", emmean, N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", ((N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sorted_df <- new_df %>%
  arrange(P, CROP)
#View(sorted_df)
#write.csv(sorted_df, "data/Final_Data/Nrate_esteff_totalforage_yr2F.csv")

#P:C scatter plot
emmsPC <- emmeans(modNYFT1, ~ P*CROP, type = "response") # Obtain estimated marginal means (excluding N)
emms_df <- as.data.frame(emmsPC)
cld_dataYFPC <- cld(emmsPC, Letters=custom_letters)
cld_df <-as.data.frame(cld_dataYFPC)
merged_df <- merge(emms_df, cld_df,by = c("P", "CROP"))

custom_labels <- c("Intercrop", "Monoculture Alfalfa","Monoculture IWG")
custom_colors <- c("darkmagenta","coral1", "cyan") 

TFYFPC<-ggplot(NdYF, aes(x = P, y = exp(predicted), color = CROP)) +
  geom_jitter(width = 0.2, height = 0, size = 3, alpha = 0.7) +
  labs(x = "Environment", y = "Total Forage Yield") +
  geom_point(data = emms_df, aes(x = P, y = response), 
             size = 4, shape = 18, color = "black")+ 
  geom_errorbar(data = emms_df, aes(x = P, ymin = lower.CL, ymax = upper.CL), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  geom_text(data = merged_df, aes(x = P, y = response.x, label = .group), 
            color = "black", vjust = 0, hjust = 2.5)+
  scale_color_manual(name = "Cropping System", labels = custom_labels,values = custom_colors)+
  theme(plot.title = element_text(hjust = 0.5))

print(TFYFPC)
#ggsave("figures/forage/TFYFPC.jpg", plot = TFYFPC, width = 10, height = 8, dpi = 300)
```

# Total forage year 3 summer
```{r}
NdZS_2 <- subset(NdZS, PlotTotForageKgHa != 0|is.na(PlotTotForageKgHa)) # remove rows where the total forage was 0

#linear
modNZST<-lmer(PlotTotForageKgHa~N*P*CROP + (1|Rep), data=NdZS_2)
anova(modNZST)
#Check Assumptions
NZST_resid<-resid(modNZST)
qqnorm(NZST_resid)
qqline(NZST_resid)
plot(modNZST)
#Logtransform
modNZST1<-lmer(log(PlotTotForageKgHa)~N*P*CROP + (1|Rep), data=NdZS_2) 
anova(modNZST1)
summary(modNZST1)
#check assumptions logtransform
NZST_resid1<-resid(modNZST1)
qqnorm(NZST_resid1)
qqline(NZST_resid1)
plot(modNZST1)

modNZST1_summary <- summary(modNZST1)
modNZST1_coeff <- as.data.frame(modNZST1_summary$coefficients)%>%
  filter(`Pr(>|t|)` < 0.05)
colnames(modNZST1_coeff)[5]<-"Pr(>t)"
# Create custom table using kable and kableExtra
save_kable(
   knitr::kable(modNZST1_coeff, 
                caption = "Y3 Summer Mixed-Effects Model: log(PlotTotForageKgHa) ~ Nrate * Location * CROPsystem + (1 | Rep)") %>%
       kable_styling(full_width = TRUE, 
                     position = "center", 
                     bootstrap_options = c("striped", "hover", "condensed")),
   file = "figures/forage/table_significant_coeff_yr3S.html")
# save table_significant_coeff_yr3S

#linear plots
NdZS_2$predicted <- predict(modNZST1, newdata = NdZS_2, re.form = NA)
ggplot(NdZS_2, aes(x = N, y = PlotTotForageKgHa, color = CROP, group= CROP)) +
    geom_point() + geom_line(aes(N, exp(predicted)))+ #regression through backtransformed predicted values
  labs(x = "N-Rate (Kg/ha)", y = "Total Forage Yield (Kg/ha)") +  # Label the axes
  ggtitle("Yr 3 S Relationship between Total Forage Yield and N-rate") +  # Add a title
scale_x_continuous(breaks = c(0, 40, 80, 120, 160))+ #fix x axis scale
  #ylim(0, 15000) +
  facet_wrap(~P, scales = "free_y",ncol=2)+ #make it by location (remove to make it across locations)
  scale_color_discrete(name = "Cropping System")  #legend for colors
# save figures/forage/totalforage_Nrate_yr3S.jpeg   775x630

#Threeway means
#NYST1emm <- compute_emmeansNYS("modNYST1")

#Pairwise N:P:C
emmsNPC <- emmeans(modNZST1, ~ N*P*CROP,at= list(N = N_levels), type= "response") 
cld_dataNZSTNPC <- cld(emmsNPC, Letters=custom_letters) # Create compact letter display
cld_dataNZSTNPC$response <- format(cld_dataNZSTNPC$response, digits = 5)
rownames(cld_dataNZSTNPC) <- NULL
cld_dataNZSTNPC<- cld_dataNZSTNPC %>%
  select(N, P, CROP, response, .group)
colnames(cld_dataNZSTNPC) <- c("N", "Site", "Cropping System", "Total Forage (kg ha-1)", "Group")
cld_dataNZSTNPC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)


#This gives us the slope for each interactions as well as a P value indicating significance level for that slope
emtrends_result<-emtrends(modNZST1,~ P*CROP, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
  #view(emtrends_df)
emtrends(modNZST1,~ P, var= "N", infer=TRUE)
emtrends(modNZST1,~ CROP, var= "N", infer=TRUE)

#equations table
emtrends_result<-emtrends(modNZST1,~ P*CROP, var= "N", infer=TRUE)
emtrends_df <- as.data.frame(emtrends_result)
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
emmeans_results<-emmeans(modNZST1, ~P*CROP, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("P", "CROP")) %>%
  select(P, CROP, emmean, N.trend, SE.x)
#view(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
merged_df$CROP <- factor(merged_df$CROP, levels = c("inter", "monoI","monoA"))  # Preferred order for CROP
# Create a new data frame with the calculated column
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sorted_df <- new_df %>%
  arrange(P, CROP)
#View(sorted_df)
#write.csv(sorted_df, "data/Final_Data/Nrate_esteff_totalforage_yr3S.csv")

#P:C scatter plot
emmsPC <- emmeans(modNZST1, ~ P*CROP, type = "response") # Obtain estimated marginal means (excluding N)
emms_df <- as.data.frame(emmsPC)
cld_dataZSPC <- cld(emmsPC, Letters=custom_letters)
cld_df <-as.data.frame(cld_dataZSPC)
merged_df <- merge(emms_df, cld_df,by = c("P", "CROP"))

custom_labels <- c("Intercrop", "Monoculture Alfalfa","Monoculture IWG")
custom_colors <- c("darkmagenta","coral1", "cyan") 

TFZSPC<-ggplot(NdZS_2, aes(x = P, y = exp(predicted), color = CROP)) +
  geom_jitter(width = 0.2, height = 0, size = 3, alpha = 0.7) +
  labs(x = "Environment", y = "Total Forage Yield") +
  geom_point(data = emms_df, aes(x = P, y = response), 
             size = 4, shape = 18, color = "black")+ 
  geom_errorbar(data = emms_df, aes(x = P, ymin = lower.CL, ymax = upper.CL), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  geom_text(data = merged_df, aes(x = P, y = response.x, label = .group), 
            color = "black", vjust = 0, hjust = 2.5)+
  scale_color_manual(name = "Cropping System", labels = custom_labels,values = custom_colors)+
  theme(plot.title = element_text(hjust = 0.5))

print(TFZSPC)
#ggsave("figures/forage/TFZSPC.jpg", plot = TFZSPC, width = 10, height = 8, dpi = 300)
```

# Total forage year 3 fall
```{r}
NdZF_2 <- subset(NdZF, PlotTotForageKgHa != 0|is.na(PlotTotForageKgHa)) # remove rows where the total forage was 0

#linear
NdZF_2$PlotTotForageKgHa<-as.numeric(NdZF_2$PlotTotForageKgHa)
NdZF_2$N<-as.numeric(NdZF_2$N)

modNZFT<-lmer(PlotTotForageKgHa~N*P*CROP + (1|Rep), data=NdZF_2) #linear 
anova(modNYFT)
summary(modNZFT)
#Check Assumptions
NZFT_resid<-resid(modNZFT)
qqnorm(NZFT_resid)
qqline(NZFT_resid)
plot(modNZFT)
abline(h = 0, col="red")
#Logtransform
modNZFT1<-lmer(log(PlotTotForageKgHa)~N*P*CROP + (1|Rep), data=NdZF_2)
NZFT_resid1<-resid(modNZFT1)
qqnorm(NZFT_resid1)
qqline(NZFT_resid1)
plot(modNZFT1)
anova(modNZFT1)

modNZFT1_summary <- summary(modNZFT1)
modNZFT1_coeff <- as.data.frame(modNZFT1_summary$coefficients)%>%
  filter(`Pr(>|t|)` < 0.05)
colnames(modNZFT1_coeff)[5]<-"Pr(>t)"
# Create custom table using kable and kableExtra
save_kable(
   knitr::kable(modNZFT1_coeff, 
                caption = "Y3 Fall Mixed-Effects Model: log(PlotTotForageKgHa) ~ Nrate * Location * CROPsystem + (1 | Rep)") %>%
       kable_styling(full_width = TRUE, 
                     position = "center", 
                     bootstrap_options = c("striped", "hover", "condensed")),
   file = "figures/forage/table_significant_coeff_yr3F.html")
# save table_significant_coeff_yr3S

#linear plots
NdZF_2$predicted <- predict(modNZFT1, newdata = NdZF_2, re.form = NA)
ggplot(NdZF_2, aes(x = N, y = PlotTotForageKgHa, color = CROP, group= CROP)) +
    geom_point() + geom_line(aes(N, exp(predicted)))+ #regression through backtransformed predicted values
  labs(x = "N-Rate (Kg/ha)", y = "Total Forage Yield (Kg/ha)") +  # Label the axes
  ggtitle("Yr 3 F Relationship between Total Forage Yield and N-rate") +  # Add a title
scale_x_continuous(breaks = c(0, 40, 80, 120, 160))+ #fix x axis scale
  #ylim(0, 3500) +
  facet_wrap(~P, scales = "free_y",ncol=2)+ #make it by location (remove to make it across locations)
  scale_color_discrete(name = "Cropping System")  #legend for colors
# save figures/forage/totalforage_Nrate_yr3F.jpeg   775x630

#Threeway means
#NZFT1emm <- compute_emmeansNZF("modNZFT1")

#Pairwise NPC
N_levels <- c(0, 40, 80, 120, 160)
emmsNPC <- emmeans(modNZFT1, specs = ~ N*P*CROP, at = list(N = N_levels), type = "response") # Obtain estimated marginal means (excluding N)
cld_dataNZFTNPC <- cld(emmsNPC, Letters=custom_letters )
#Pairwise C
emmsC <- emmeans(modNZFT1, ~ CROP, type = "response") # Obtain estimated marginal means (excluding N)
cld_dataNZFTC <- cld(emmsC, Letters=custom_letters) # Create compact letter display
cld_dataNZFTC$response <- format(cld_dataNZFTC$response, digits = 5)
cld_dataNZFTC<- cld_dataNZFTC %>%
  select(CROP, response, .group)
rownames(cld_dataNZFTC) <- NULL
colnames(cld_dataNZFTC) <- c("Cropping System", "Total Forage (kg ha-1)", "Group")
cld_dataNZFTC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)
#Pairwise N:C
N_levels <- c(0, 40, 80, 120, 160)
emmsNZFT <- emmeans(modNZFT1, specs = ~ N*CROP, at = list(N = N_levels), type = "response")
cld_dataNZFTNC <- cld(emmsNZFT, Letters=custom_letters) # Create compact letter display
cld_dataNZFTNC$response <- format(cld_dataNZFTNC$response, digits = 5)
cld_dataNZFTNC<- cld_dataNZFTNC %>%
  select(N, CROP, response, .group)
rownames(cld_dataNZFTNC) <- NULL
colnames(cld_dataNZFTNC) <- c("N", "Cropping System", "Total Forage (kg ha-1)", "Group")
cld_dataNZFTNC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)
#Pairwise P:C
emmsNZFTPC <- emmeans(modNZFT1, specs = ~ P*CROP, type = "response")
cld_dataNZFTPC <- cld(emmsNZFTPC, Letters=custom_letters) # Create compact letter display
cld_dataNZFTPC$response <- format(cld_dataNZFTPC$response, digits = 5)
cld_dataNZFTPC<- cld_dataNZFTPC %>%
  select(P, CROP, response, .group)
rownames(cld_dataNZFTPC) <- NULL
colnames(cld_dataNZFTPC) <- c("Location", "Cropping System", "Total Forage (kg ha-1)", "Group")
cld_dataNZFTPC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)


#This gives us the slope for each interactions as well as a P value indicating significance level for that slope
emtrends(modNZFT1,~ P*CROP, var= "N", infer=TRUE)
emtrends(modNZFT1,~ P, var= "N", infer=TRUE)
emtrends(modNZFT1,~ CROP, var= "N", infer=TRUE)

#equations table
emtrends_result<-emtrends(modNZFT1,~ P*CROP, var= "N", infer=TRUE)
emtrends_df <- as.data.frame(emtrends_result)
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
emmeans_results<-emmeans(modNZFT1, ~P*CROP, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("P", "CROP")) %>%
  select(P, CROP, emmean, N.trend, SE.x)
#view(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
merged_df$CROP <- factor(merged_df$CROP, levels = c("inter", "monoI","monoA"))  # Preferred order for CROP
# Create a new data frame with the calculated column
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sorted_df <- new_df %>%
  arrange(P, CROP)
#View(sorted_df)
#write.csv(sorted_df, "data/Final_Data/Nrate_esteff_totalforage_yr3F.csv")

#P:C scatter plot
emmsPC <- emmeans(modNZFT1, ~ P*CROP, type = "response") # Obtain estimated marginal means (excluding N)
emms_df <- as.data.frame(emmsPC)
cld_dataZFPC <- cld(emmsPC, Letters=custom_letters)
cld_df <-as.data.frame(cld_dataZFPC)
merged_df <- merge(emms_df, cld_df,by = c("P", "CROP"))

custom_labels <- c("Intercrop", "Monoculture Alfalfa","Monoculture IWG")
custom_colors <- c("darkmagenta","coral1", "cyan") 

TFZFPC<-ggplot(NdZF_2, aes(x = P, y = exp(predicted), color = CROP)) +
  geom_jitter(width = 0.2, height = 0, size = 3, alpha = 0.7) +
  labs(x = "Environment", y = "Total Forage Yield") +
  geom_point(data = emms_df, aes(x = P, y = response), 
             size = 4, shape = 18, color = "black")+ 
  geom_errorbar(data = emms_df, aes(x = P, ymin = lower.CL, ymax = upper.CL), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  geom_text(data = merged_df, aes(x = P, y = response.x, label = .group), 
            color = "black", vjust = 0, hjust = 2.5)+
  scale_color_manual(name = "Cropping System", labels = custom_labels,values = custom_colors)+
  theme(plot.title = element_text(hjust = 0.5))

print(TFZFPC)
#ggsave("figures/forage/TFZFPC.jpg", plot = TFZFPC, width = 10, height = 8, dpi = 300)
```


# Total Forage anovas Table 
```{r}
aov.tableXS <- anova(modNXST1)
tableTFXS = flextable(data = aov.tableXS %>%
                    #filter(`Pr(>F)` < 0.05) %>%
                    mutate(`Pr(>F)` = formatC(`Pr(>F)`, digits = 3)) %>% 
                    select(`Pr(>F)`) %>%
                    rownames_to_column(" ")) 
print(tableTFXS)
# save figures/forage/gt_IFXS 

aov.tableXF <- anova(modNXFT1)
tableTFXF = flextable(data = aov.tableXF %>%
                    #filter(`Pr(>F)` < 0.05) %>%
                    mutate(`Pr(>F)` = formatC(`Pr(>F)`, digits = 3)) %>% 
                    select(`Pr(>F)`) %>%
                    rownames_to_column(" ")) 
print(tableTFXF)
# save figures/forage/gt_IFXF

aov.tableYS <- anova(modNYST) # normal= modNYST; log=modNYST1 
tableTFYS = flextable(data = aov.tableYS %>%
                    #filter(`Pr(>F)` < 0.05) %>%
                    mutate(`Pr(>F)` = formatC(`Pr(>F)`, digits = 3)) %>% 
                    select(`Pr(>F)`) %>%
                    rownames_to_column(" ")) 
print(tableTFYS)
# save figures/forage/gt_IFYS 

aov.tableYF <- anova(modNYFT1)
tableTFYF = flextable(data = aov.tableYF %>%
                    #filter(`Pr(>F)` < 0.05) %>%
                    mutate(`Pr(>F)` = formatC(`Pr(>F)`, digits = 3)) %>% 
                    select(`Pr(>F)`) %>%
                    rownames_to_column(" ")) 
print(tableTFYF)
# save figures/forage/gt_IFYF

aov.tableZS <- anova(modNZST1)
tableTFZS = flextable(data = aov.tableZS %>%
                    #filter(`Pr(>F)` < 0.05) %>%
                    mutate(`Pr(>F)` = formatC(`Pr(>F)`, digits = 3)) %>% 
                    select(`Pr(>F)`) %>%
                    rownames_to_column(" ")) 
print(tableTFZS)
# save figures/forage/gt_IFZS 

aov.tableZF <- anova(modNZFT1)
tableTFZF = flextable(data = aov.tableZF %>%
                    #filter(`Pr(>F)` < 0.05) %>%
                    mutate(`Pr(>F)` = formatC(`Pr(>F)`, digits = 3)) %>% 
                    select(`Pr(>F)`) %>%
                    rownames_to_column(" ")) 
print(tableTFZF)
# save figures/forage/gt_IFZF




my_modelsNG <- c(modNXST1, modNXFT1, modNYST, modNYFT1, modNZST1, modNZFT1)
anovasNG <- purrr::map(my_modelsNG, ~anova(.))
names(anovasNG) <- c("Year 1 S", "Year 1 F", "Year 2 S", "Year 2 F", "Year 3 S", "Year 3 F")

# Function to format p-values as stars
format_p_value <- function(p_val) {
  stars <- ifelse(p_val < 0.001, "***", ifelse(p_val < 0.01, "**", ifelse(p_val < 0.05, "*", "")))
  return(stars)
}

# Apply the function to your ANOVA results
NG_stars_tibble <- map(anovasNG, as_tibble, rownames="term") %>%
  bind_rows(.id = "model") %>%
  mutate(stars = map_chr(`Pr(>F)`, format_p_value))

NG_stars_tibble <- NG_stars_tibble %>%
  mutate(term = ifelse(term == "P", "E", term)) %>%
  mutate(term = ifelse(term == "N:P", "N:E", term))%>%
  mutate(term = ifelse(term == "P:CROP", "E:CROP", term))%>%
  mutate(term = ifelse(term == "N:P:CROP", "N:E:CROP", term))

# Print the tibble
print(NG_stars_tibble)

NG_stars <-NG_stars_tibble |> 
  select(model, term, stars) |>
  pivot_wider(names_from = term, values_from = stars)

gt_NG <- gt(NG_stars)

gt_NG |> gtsave("figures/forage/gt_IF_2.png", expand = 10)
```

# total forage combined years plots E:C
```{r}

TFPC <- ggarrange(
TFXSPC + ggtitle("Year 1 S"),
TFXFPC + ggtitle("Year 1 F"),
TFYSPC + ggtitle("Year 2 S"),
TFYFPC + ggtitle("Year 2 F"),
TFZSPC + ggtitle("Year 3 S"),
TFZFPC + ggtitle("Year 3 F"),
nrow = 3, 
ncol = 2,
common.legend = TRUE,
legend = "right"
)
TFPC
#save figures/forage/TFPC.jpg   2000x1800
```



## IWG Forage Yield 

# IWG forage year 1 summer
```{r}
#Linear
modNXSI<-lmer(PlotIWGDryKgHa~N*P*CROP + (1|Rep), data=NdXSI)
anova(modNXSI)
#Check Assumptions
NXSI_resid<-resid(modNXSI)
qqnorm(NXSI_resid)
qqline(NXSI_resid)
plot(modNXSI)
#log transform 
modNXSI1<-lmer(log(PlotIWGDryKgHa)~N*P*CROP + (1|Rep), data=NdXSI)
anova(modNXSI1)
#Check Assumptions
NXSI1_resid<-resid(modNXSI1)
qqnorm(NXSI1_resid)
qqline(NXSI1_resid)
plot(modNXSI1)

modNXSI1_summary <- summary(modNXSI1)
modNXSI1_coeff <- as.data.frame(modNXSI1_summary$coefficients)%>%
  filter(`Pr(>|t|)` < 0.05)
colnames(modNXSI1_coeff)[5]<-"Pr(>t)"
# Create custom table using kable and kableExtra
save_kable(
  knitr::kable(modNXSI1_coeff, 
               caption = "Y1 Summer Mixed-Effects Model: log(IWGForageKgHa) ~ Nrate * Location * CROPsystem + (1 | Rep)") %>%
    kable_styling(full_width = TRUE, 
                  position = "center", 
                  bootstrap_options = c("striped", "hover", "condensed")),
  file = "figures/forage/IWG_table_significant_coeff_yr1S.html")
# save iwg_table_significant_coeff_yr1S


max(NdXSI$PlotIWGDryKgHa)
#linear plots
NdXSI$predicted <- predict(modNXSI1, newdata = NdXSI, re.form = NA)
ggplot(NdXSI, aes(x = N, y = PlotIWGDryKgHa, color = CROP, group= CROP)) +
    geom_point() + geom_line(aes(N, exp(predicted)))+ #regression through backtransformed predicted values
  labs(x = "N-Rate (Kg/ha)", y = "IWG Forage Yield (Kg/ha)") +  # Label the axes
  ggtitle("Yr 1 S Relationship between IWG Forage Yield and N-rate") +  # Add a title
scale_x_continuous(breaks = c(0, 40, 80, 120, 160))+ #fix x axis scale
#  ylim(0, 15000) +
  facet_wrap(~P, scales = "free_y",ncol=2)+ #make it by location (remove to make it across locations)
  scale_color_discrete(name = "Cropping System")  #legend for colors
# save figures/forage/IWG_forage_Nrate_yr1S.jpeg    775x630

#Threeway means
NXSI1emm <- compute_emmeansNXS("modNXSI1")
#write.csv(NXSI1emm, 'data/Final_Data/NXSI1emm.csv')

#Pairwise P
emmsP <- emmeans(modNXSI1, ~ P, type = "response") # Obtain estimated marginal means
cld_dataNXSIP <- cld(emmsP, Letters=custom_letters) # Create compact letter display
#Pairwise C
emmsC <- emmeans(modNXSI1, ~ CROP, type = "response") # Obtain estimated marginal means 
cld_dataNXSIC <- cld(emmsC, Letters=custom_letters) # Create compact letter display
#Pairwise N
N_levels <- c(0, 40, 80, 120, 160)
emmsN <- emmeans(modNXSI1, specs = ~ N, at = list(N = N_levels), type = "response")
cld_dataNXSIN <- cld(emmsN, Letters=custom_letters) # Create compact letter display
#Pairwise P:C
emmsPC <- emmeans(modNXSI1, ~ P*CROP, type= "response") # Obtain estimated marginal means
cld_dataNXSIPC <- cld(emmsPC, Letters=custom_letters) # Create compact letter display
cld_dataNXSIPC$response <- format(cld_dataNXSIPC$response, digits = 5)
rownames(cld_dataNXSIPC) <- NULL
cld_dataNXSIPC<- cld_dataNXSIPC %>%
  select(P, CROP, response, .group)
colnames(cld_dataNXSIPC) <- c("Site", "Cropping System", "IWG Forage (kg ha-1)", "Group")
cld_dataNXSIPC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)
#Pairwise N:P
emmsNP <- emmeans(modNXSI1, ~ N*P,at = list(N = N_levels), type= "response") # Obtain estimated marginal means
cld_dataNXSINP <- cld(emmsNP, Letters=custom_letters) # Create compact letter display
cld_dataNXSINP$response <- format(cld_dataNXSINP$response, digits = 5)
rownames(cld_dataNXSINP) <- NULL
cld_dataNXSINP<- cld_dataNXSINP %>%
  select(N,P, response, .group)
colnames(cld_dataNXSINP) <- c("N", "Site", "IWG Forage (kg ha-1)", "Group")
cld_dataNXSINP  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)

#This gives us the slope for each interactions as well as a P value indicating significance level for that slope
emtrends(modNXSI1,~ P*CROP, var= "N", infer=TRUE)
emtrends_result<-emtrends(modNXSI1,~ P, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
  #view(emtrends_df)
emtrends(modNXSI1,~ CROP, var= "N", infer=TRUE)

#equations table
emtrends_result<-emtrends(modNXSI1,~ P*CROP, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
emmeans_results<-emmeans(modNXSI1, ~P*CROP, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("P", "CROP")) %>%
  select(P, CROP, emmean, N.trend, SE.x)
#view(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
merged_df$CROP <- factor(merged_df$CROP, levels = c("inter", "monoI"))  # Preferred order for CROP
# Create a new data frame with the calculated column
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sorted_df <- new_df %>%
  arrange(P, CROP)
#view(sorted_df)
#write.csv(sorted_df, "data/Final_Data/Nrate_esteff_IWGforage_yr1S.csv")

#equations table (N equations across cropping system)
emtrends_result<-emtrends(modNXSI1,~ CROP, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
emmeans_results<-emmeans(modNXSI1, ~ CROP, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("CROP")) %>%
  select(CROP, emmean, N.trend, SE.x)
merged_df$CROP <- factor(merged_df$CROP, levels = c("inter", "monoI"))  # Preferred order for CROP
# Create a new data frame with the calculated column
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sorted_df2 <- new_df %>%
  arrange(CROP)
#view(sorted_df2)
#write.csv(sorted_df, "data/Final_Data/Nrate_esteff_IWGforage_yr1S_2.csv")
emtrends_result<-emtrends(modNXSI1,~ P, var= "N", infer=TRUE)
emtrends_df <- as.data.frame(emtrends_result)
desired_order_P <- c("MN", "NY", "KS", "WI")
emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
emmeans_results<-emmeans(modNXSI1, ~P, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
inner_join(emmeans_df, by = c("P")) %>%
select(P, emmean, N.trend, SE.x)
#view(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
# Create a new data frame with the calculated column
new_df <- merged_df %>%
mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
select(-emmean, -N.trend)
sorted_df3 <- new_df %>%
arrange(P)
#view(sorted_df3)
#write.csv(sorted_df3, "data/Final_Data/Nrate_esteff_IWGforage_yr1S_3.csv")


# IWG forage figure E:C (XS)
XSIemmsPC <- emmeans(modNXSI1, ~ P*CROP, type = "response") # Obtain estimated marginal means
emms_df <- as.data.frame(XSIemmsPC)
cld_dataXSIPC <- cld(XSIemmsPC, Letters=custom_letters)
cld_df <-as.data.frame(cld_dataXSIPC)
merged_df <- merge(emms_df, cld_df,by = c("P", "CROP"))
custom_labels <- c("Intercrop", "Monoculture IWG")
custom_colors <- c("darkmagenta", "cyan") 
IXSPC<-ggplot(NdXSI, aes(x = P, y = exp(predicted), color = CROP)) +
  geom_jitter(width = 0.2, height = 0, size = 3, alpha = 0.7) +
  labs(x = "Environment", y = "IWG Forage Yield") +
  geom_point(data = emms_df, aes(x = P, y = response), 
             size = 4, shape = 18, color = "black")+ 
  geom_errorbar(data = emms_df, aes(x = P, ymin = lower.CL, ymax = upper.CL), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  geom_text(data = merged_df, aes(x = P, y = response.x, label = .group), 
            color = "black", vjust = 0, hjust = 2)+
  scale_color_manual(name = "Cropping System", labels = custom_labels,values = custom_colors)+
     ggtitle("Year 1 Summer")+
  theme(plot.title = element_text(hjust = 0.5))+
   guides(color = "none")+
  scale_y_continuous(breaks = c(2000,4000,6000,8000,10000,12000, 14000), limits = c(0, 14000))
print(IXSPC)
##ggsave("figures/forage/IXSPC.jpg", plot = IXSPC, width = 10, height = 8, dpi = 300)

#N:E
# Define the desired order of 'P'
desired_order <- c("MN", "NY", "KS", "WI")
NdXSI$P <- factor(NdXSI$P, levels = desired_order)
# finding values for the function for each yr:location  
emtrends_resultX<-emtrends(modNXSI1,~ N*P*CROP, var= "N", infer=TRUE)
  emtrends_dfX <- as.data.frame(emtrends_resultX)
  emtrends_dfX$plvl <-
    ifelse(emtrends_dfX$p.value == 0.05, ".",
    ifelse(emtrends_dfX$p.value < 0.05  & emtrends_dfX$p.value >= 0.01, "*",
    ifelse(emtrends_dfX$p.value < 0.01  & emtrends_dfX$p.value >= 0.001, "**",
    ifelse(emtrends_dfX$p.value < 0.001, "***", ""))))
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_dfX$PC <- paste0(emtrends_dfX$P,emtrends_dfX$CROP)
  emtrends_dfX$P <- factor(emtrends_dfX$P, levels = desired_order_P)
emmeans_resultsX<-emmeans(modNXSI1, ~N*P*CROP, at=list(N=0))
  emmeans_dfX <- as.data.frame(emmeans_resultsX)
  emmeans_dfX$PC <- paste0(emmeans_dfX$P,emmeans_dfX$CROP)
mergedX <- emtrends_dfX %>%
  inner_join(emmeans_dfX, by = c("PC")) %>%
  dplyr::select(PC, P.x, CROP.x, emmean, N.trend, SE.x, plvl)
  colnames(mergedX)[2] <- "P"
  colnames(mergedX)[3] <- "CROP"
mergedX$P <- factor(mergedX$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
X_df <- mergedX %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sortedX <- X_df %>%
  arrange(P)
sortedX_I <- subset(sortedX, CROP== "inter")
sortedX_M <- subset(sortedX, CROP== "monoI")

sym_I <- sortedX_I %>%
  distinct(P) %>%
  mutate(
    x_sym = 0,
    y_sym = 15500
  )
sym_M <- sortedX_M %>%
  distinct(P) %>%
  mutate(
    x_sym = 0,
    y_sym = 15000
  )

#plot
IcomboplotNEXS <- ggplot(data=NdXSI) +
  geom_point(data = NdXSI, aes(x = N, y = PlotTotForageKgHa, shape = CROP)) +
  labs(x = "N-Rate (Kg ha-1)", y = "Total Forage", linetype = "Cropping System", shape = "Cropping System", color = "Harvest")+
  scale_x_continuous(breaks = c(0, 40, 80, 120, 160)) +
 # ylim(0, 1000) +
  facet_wrap(~P, scales = "free_y", ncol = 2) +
  scale_shape_manual(values = c(4, 25),labels = c("Intercropped", "Monoculture IWG"))+
  # functions come from equation in sorted
  geom_function(data=subset(NdXSI, P== "MN" & CROP == "inter"), fun=~1423.08*exp(0.0022*.x),color='darkgrey')+
  geom_function(data=subset(NdXSI, P== "MN" & CROP == "monoI"), fun=~2121.42*exp(0.0032*.x),color='darkgrey')+
  geom_function(data=subset(NdXSI, P== "NY" & CROP == "inter"), fun=~1723.23*exp(0.0053*.x),color='darkgrey')+
  geom_function(data=subset(NdXSI, P== "NY" & CROP == "monoI"), fun=~4217.30*exp(0.0047*.x),color='darkgrey')+
  geom_function(data=subset(NdXSI, P== "KS" & CROP == "inter"), fun=~4809.53*exp(0.0010*.x),color='darkgrey')+
  geom_function(data=subset(NdXSI, P== "KS" & CROP == "monoI"), fun=~11257.42*exp(0.0004*.x),color='darkgrey')+
  geom_function(data=subset(NdXSI, P== "WI" & CROP == "inter"), fun=~5336.82*exp(0.0009*.x),color='darkgrey')+
  geom_function(data=subset(NdXSI, P== "WI" & CROP == "monoI"), fun=~8774.71*exp(0.0008*.x),color='darkgrey')+
  geom_text(data = sortedX_I, mapping = aes(x = 30, y = 15500, label = equation),  size=2)+ # add equation to figure
  geom_point(data = sym_I, aes(x = x_sym, y = y_sym), shape = 4, size = 1, inherit.aes = FALSE)+
  geom_text(data = sortedX_M, mapping = aes(x = 30, y = 15000, label = equation),  size=2)+ # add equation to figure
  geom_point(data = sym_M, aes(x = x_sym, y = y_sym), shape = 25, size = 1, fill = "lightgrey", stroke = 0.6, inherit.aes = FALSE)+
  geom_text(data = sortedX_I, mapping = aes(x = 60, y = 15500, label = plvl))+
  geom_text(data = sortedX_M, mapping = aes(x = 60, y = 15000, label = plvl)) # add stars to figure
# add stars to figure
print(IcomboplotNEXS)
# ggsave("figures/forage/IcomboplotNEXS.jpg", plot = IcomboplotNEXS, width = 10, height = 8, dpi = 300)
```

# IWG forage year 1 fall
*** sigularity issue *** 
```{r}
#linear 
modNXFI<-lmer(PlotIWGDryKgHa~N*P*CROP + (1|Rep), data=NdXFI)
# boundary (singular) fit: see help('isSingular')
modNXFI<-lm(PlotIWGDryKgHa~N*P*CROP, data=NdXFI)
anova(modNXFI)
summary(modNXFI)
#Check Assumptions
NXFI_resid<-resid(modNXFI)
qqnorm(NXFI_resid)
qqline(NXFI_resid)
#plot(modNXFI)
#log transform
modNXFI1<-lmer(log(PlotIWGDryKgHa)~N*P*CROP + (1|Rep), data=NdXFI)
# boundary (singular) fit: see help('isSingular')
modNXFI1<-lm(log(PlotIWGDryKgHa)~N*P*CROP, data=NdXFI)
anova(modNXFI1)
NXFI1_resid<-resid(modNXFI1)
qqnorm(NXFI1_resid)
qqline(NXFI1_resid)
#plot(modNXFI1)

modNXFI1_summary <- summary(modNXFI1)
modNXFI1_coeff <- as.data.frame(modNXFI1_summary$coefficients)%>%
  filter(`Pr(>|t|)` < 0.05)
# Create custom table using kable and kableExtra
save_kable(
  knitr::kable(modNXFI1_coeff, 
               caption = "Y1 Fall Mixed-Effects Model: log(IWGForageKgHa) ~ Nrate * Location * CROPsystem + (1 | Rep)") %>%
    kable_styling(full_width = TRUE, 
                  position = "center", 
                  bootstrap_options = c("striped", "hover", "condensed")),
  file = "figures/forage/IWG_table_significant_coeff_yr1F.html")
# save iwg_table_significant_coeff_yr1F


max(NdXFI$PlotIWGDryKgHa)
#linear plots
NdXFI$predicted <- predict(modNXFI1, newdata = NdXFI, re.form = NA)
ggplot(NdXFI, aes(x = N, y = PlotIWGDryKgHa, color = CROP, group= CROP)) +
    geom_point() + geom_line(aes(N, exp(predicted)))+ #regression through backtransformed predicted values
  labs(x = "N-Rate (Kg/ha)", y = "IWG Forage Yield (Kg/ha)") +  # Label the axes
  ggtitle("Yr 1 F Relationship between IWG Forage Yield and N-rate") +  # Add a title
scale_x_continuous(breaks = c(0, 40, 80, 120, 160))+ #fix x axis scale
#  ylim(0, 2800) +
  facet_wrap(~P, scales = "free_y",ncol=2)+ #make it by location (remove to make it across locations)
  scale_color_discrete(name = "Cropping System")  #legend for colors
# save figures/forage/IWG_forage_Nrate_yr1F.jpeg    775x630

#Threeway means
NXFI1emm <- compute_emmeansNXF("modNXFI1")
#write.csv(NXFI1emm, 'data/Final_Data/NXFI1emm.csv')

#Pairwise P
emmsP <- emmeans(modNXFI1, ~ P, type = "response") # Obtain estimated marginal means
cld_dataNXFIP <- cld(emmsP, Letters=custom_letters) # Create compact letter display
#Pairwise C
emmsC <- emmeans(modNXFI1, ~ CROP, type = "response") # Obtain estimated marginal means 
cld_dataNXFIC <- cld(emmsC, Letters=custom_letters) # Create compact letter display
#Pairwise N
N_levels <- c(0, 40, 80, 120, 160)
emmsN <- emmeans(modNXFI1, specs = ~ N, at = list(N = N_levels), type = "response")
cld_dataNXFIN <- cld(emmsN, Letters=custom_letters) # Create compact letter display
#Pairwise P:C
emmsPC <- emmeans(modNXFI1, ~ P*CROP, type= "response") # Obtain estimated marginal means
cld_dataNXFIPC <- cld(emmsPC, Letters=custom_letters) # Create compact letter display
cld_dataNXFIPC$response <- format(cld_dataNXFIPC$response, digits = 5)
rownames(cld_dataNXFIPC) <- NULL
cld_dataNXFIPC<- cld_dataNXFIPC %>%
  select(P, CROP, response, .group)
colnames(cld_dataNXFIPC) <- c("Site", "Cropping System", "IWG Forage (kg ha-1)", "Group")
cld_dataNXFIPC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)
#Pairwise N:P
emmsNP <- emmeans(modNXFI1, ~ N*P,at = list(N = N_levels), type= "response") # Obtain estimated marginal means
cld_dataNXFINP <- cld(emmsNP, Letters=custom_letters) # Create compact letter display
cld_dataNXFINP$response <- format(cld_dataNXFINP$response, digits = 5)
rownames(cld_dataNXFINP) <- NULL
cld_dataNXFINP<- cld_dataNXFINP %>%
  select(N, P, response, .group)
colnames(cld_dataNXFINP) <- c("N", "Site", "IWG Forage (kg ha-1)", "Group")
cld_dataNXFINP  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)

#slope stuff
emtrends_result<-emtrends(modNXFI1,~ P, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
  #view(emtrends_df)
  
#equations table
emtrends_result<-emtrends(modNXFI1,~ P*CROP, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
emmeans_results<-emmeans(modNXFI1, ~P*CROP, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("P", "CROP")) %>%
  select(P, CROP, emmean, N.trend, SE.x)
#view(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
merged_df$CROP <- factor(merged_df$CROP, levels = c("inter", "monoI"))  # Preferred order for CROP
# Create a new data frame with the calculated column
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sorted_df <- new_df %>%
  arrange(P, CROP)
#view(sorted_df)
#write.csv(sorted_df, "data/Final_Data/Nrate_esteff_IWGforage_yr1F.csv")

#equations table (N equations across cropping system)
emtrends_result<-emtrends(modNXFI1,~ CROP, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
emmeans_results<-emmeans(modNXFI1, ~ CROP, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("CROP")) %>%
  select(CROP, emmean, N.trend, SE.x)
merged_df$CROP <- factor(merged_df$CROP, levels = c("inter", "monoI"))  # Preferred order for CROP
# Create a new data frame with the calculated column
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sorted_df2 <- new_df %>%
  arrange(CROP)
#view(sorted_df2)
#write.csv(sorted_df2, "data/Final_Data/Nrate_esteff_IWGforage_yr1F_2.csv")
emtrends_result<-emtrends(modNXFI1,~ P, var= "N", infer=TRUE)
emtrends_df <- as.data.frame(emtrends_result)
desired_order_P <- c("MN", "NY", "KS", "WI")
emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
emmeans_results<-emmeans(modNXFI1, ~P, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
inner_join(emmeans_df, by = c("P")) %>%
select(P, emmean, N.trend, SE.x)
#view(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
# Create a new data frame with the calculated column
new_df <- merged_df %>%
mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
select(-emmean, -N.trend)
sorted_df3 <- new_df %>%
arrange(P)
#view(sorted_df3)
#write.csv(sorted_df3, "data/Final_Data/Nrate_esteff_IWGforage_yr1F_3.csv")

#IWG forage figure E:C (XF)
XFIemmsPC <- emmeans(modNXFI1, ~ P*CROP, type = "response") # Obtain estimated marginal means
emms_df <- as.data.frame(XFIemmsPC)
cld_dataXFIPC <- cld(XFIemmsPC, Letters=custom_letters)
cld_df <-as.data.frame(cld_dataXFIPC)
merged_df <- merge(emms_df, cld_df,by = c("P", "CROP"))
custom_labels <- c("Intercrop", "Monoculture IWG")
custom_colors <- c("darkmagenta", "cyan") 
IXFPC<-ggplot(NdXFI, aes(x = P, y = exp(predicted), color = CROP)) +
  geom_jitter(width = 0.2, height = 0, size = 3, alpha = 0.7) +
  labs(x = "Environment", y = "IWG Forage Yield") +
  geom_point(data = emms_df, aes(x = P, y = response), 
             size = 4, shape = 18, color = "black")+ 
  geom_errorbar(data = emms_df, aes(x = P, ymin = lower.CL, ymax = upper.CL), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  geom_text(data = merged_df, aes(x = P, y = response.x, label = .group), 
            color = "black", vjust = 0, hjust = 2)+
  scale_color_manual(name = "Cropping System", labels = custom_labels,values = custom_colors)+
     ggtitle("Year 1 Fall")+
  theme(plot.title = element_text(hjust = 0.5))+
   guides(color = "none")+
  scale_y_continuous(breaks = c(250, 500, 750, 1000, 1250, 1500), limits = c(0, 1500))
print(IXFPC)
#ggsave("figures/forage/IXFPC.jpg", plot = IXFPC, width = 10, height = 8, dpi = 300)

#N:E
# Define the desired order of 'P'
desired_order <- c("MN", "NY", "KS", "WI")
NdXFI$P <- factor(NdXFI$P, levels = desired_order)
# finding values for the function for each yr:location  
emtrends_resultX<-emtrends(modNXFI1,~ N*P*CROP, var= "N", infer=TRUE)
  emtrends_dfX <- as.data.frame(emtrends_resultX)
  emtrends_dfX$plvl <-
    ifelse(emtrends_dfX$p.value == 0.05, ".",
    ifelse(emtrends_dfX$p.value < 0.05  & emtrends_dfX$p.value >= 0.01, "*",
    ifelse(emtrends_dfX$p.value < 0.01  & emtrends_dfX$p.value >= 0.001, "**",
    ifelse(emtrends_dfX$p.value < 0.001, "***", ""))))
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_dfX$PC <- paste0(emtrends_dfX$P,emtrends_dfX$CROP)
  emtrends_dfX$P <- factor(emtrends_dfX$P, levels = desired_order_P)
emmeans_resultsX<-emmeans(modNXFI1, ~N*P*CROP, at=list(N=0))
  emmeans_dfX <- as.data.frame(emmeans_resultsX)
  emmeans_dfX$PC <- paste0(emmeans_dfX$P,emmeans_dfX$CROP)
mergedX <- emtrends_dfX %>%
  inner_join(emmeans_dfX, by = c("PC")) %>%
  dplyr::select(PC, P.x, CROP.x, emmean, N.trend, SE.x, plvl)
  colnames(mergedX)[2] <- "P"
  colnames(mergedX)[3] <- "CROP"
mergedX$P <- factor(mergedX$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
X_df <- mergedX %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sortedX <- X_df %>%
  arrange(P)
sortedX_I <- subset(sortedX, CROP== "inter")
sortedX_M <- subset(sortedX, CROP== "monoI")

sym_I <- sortedX_I %>%
  distinct(P) %>%
  mutate(
    x_sym = 0,
    y_sym = 3250
  )
sym_M <- sortedX_M %>%
  distinct(P) %>%
  mutate(
    x_sym = 0,
    y_sym = 3100
  )

#plot
IcomboplotNEXF <- ggplot(data=NdXFI) +
  geom_point(data = NdXFI, aes(x = N, y = PlotTotForageKgHa, shape = CROP)) +
  labs(x = "N-Rate (Kg ha-1)", y = "Total Forage", linetype = "Cropping System", shape = "Cropping System", color = "Harvest")+
  scale_x_continuous(breaks = c(0, 40, 80, 120, 160)) +
 # ylim(0, 1000) +
  facet_wrap(~P, scales = "free_y", ncol = 2) +
  scale_shape_manual(values = c(4, 25),labels = c("Intercropped", "Monoculture IWG"))+
  # functions come from equation in sorted
  geom_function(data=subset(NdXFI, P== "MN" & CROP == "inter"), fun=~449.57*exp(0.0013*.x),color='darkgrey')+
  geom_function(data=subset(NdXFI, P== "MN" & CROP == "monoI"), fun=~945.42*exp(0.0026*.x),color='darkgrey')+
  geom_function(data=subset(NdXFI, P== "NY" & CROP == "inter"), fun=~386.79*exp(0.0028*.x),color='darkgrey')+
  geom_function(data=subset(NdXFI, P== "NY" & CROP == "monoI"), fun=~179.98*exp(0.0059*.x),color='darkgrey')+
  geom_function(data=subset(NdXFI, P== "WI" & CROP == "inter"), fun=~269.09*exp(-0.0014*.x),color='darkgrey')+
  geom_function(data=subset(NdXFI, P== "WI" & CROP == "monoI"), fun=~297.71*exp(-0.0006*.x),color='darkgrey')+
  geom_text(data = sortedX_I, mapping = aes(x = 30, y = 3250, label = equation),  size=2)+ # add equation to figure
  geom_point(data = sym_I, aes(x = x_sym, y = y_sym), shape = 4, size = 1, inherit.aes = FALSE)+
  geom_text(data = sortedX_M, mapping = aes(x = 30, y = 3100, label = equation),  size=2)+ # add equation to figure
  geom_point(data = sym_M, aes(x = x_sym, y = y_sym), shape = 25, size = 1, fill = "lightgrey", stroke = 0.6, inherit.aes = FALSE)+
  geom_text(data = sortedX_I, mapping = aes(x = 60, y = 3250, label = plvl))+
  geom_text(data = sortedX_M, mapping = aes(x = 60, y = 3100, label = plvl)) # add stars to figure
# add stars to figure
print(IcomboplotNEXF)
# ggsave("figures/forage/IcomboplotNEXF.jpg", plot = IcomboplotNEXF, width = 10, height = 8, dpi = 300)
```

#IWG forage year 2 summer
*** singularity issue *** 
```{r}
#LINEAR
modNYSI<-lmer(PlotIWGDryKgHa~N*P*CROP + (1|Rep), data=NdYSI)
# boundary (singular) fit: see help('isSingular')
modNYSI<-lm(PlotIWGDryKgHa~N*P*CROP, data=NdYSI)
anova(modNYSI)
#Check Assumptions
NYSI_resid<-resid(modNYSI)
qqnorm(NYSI_resid)
qqline(NYSI_resid)
#plot(modNYSI)
#Logtransform
modNYSI1<-lmer(log(PlotIWGDryKgHa)~N*P*CROP + (1|Rep), data=NdYSI)
# boundary (singular) fit: see help('isSingular')
modNYSI1<-lm(log(PlotIWGDryKgHa)~N*P*CROP, data=NdYSI)
anova(modNYSI1)
#check assumptions logtransform (makes it BETTER)
NYSI_resid1<-resid(modNYSI1)
qqnorm(NYSI_resid1)
qqline(NYSI_resid1)
#plot(modNYSI1)

modNYSI1_summary <- summary(modNYSI1)
modNYSI1_coeff <- as.data.frame(modNYSI1_summary$coefficients)%>%
  filter(`Pr(>|t|)` < 0.05)
# Create custom table using kable and kableExtra
save_kable(
  knitr::kable(modNYSI1_coeff, 
               caption = "Y2 Summer Mixed-Effects Model: log(IWGForageKgHa) ~ Nrate * Location * CROPsystem + (1 | Rep)") %>%
    kable_styling(full_width = TRUE, 
                  position = "center", 
                  bootstrap_options = c("striped", "hover", "condensed")),
  file = "figures/forage/IWG_table_significant_coeff_yr2S.html")
# save iwg_table_significant_coeff_yr2S


max(NdYSI$PlotIWGDryKgHa)
#linear plots
NdYSI$predicted <- predict(modNYSI1, newdata = NdYSI, re.form = NA)
ggplot(NdYSI, aes(x = N, y = PlotIWGDryKgHa, color = CROP, group= CROP)) +
    geom_point() + geom_line(aes(N, exp(predicted)))+ #regression through backtransformed predicted values
  labs(x = "N-Rate (Kg/ha)", y = "IWG Forage Yield (Kg/ha)") +  # Label the axes
  ggtitle("Yr 2 S Relationship between IWG Forage Yield and N-rate") +  # Add a title
scale_x_continuous(breaks = c(0, 40, 80, 120, 160))+ #fix x axis scale
#  ylim(0, 2800) +
  facet_wrap(~P, scales = "free_y",ncol=2)+ #make it by location (remove to make it across locations)
  scale_color_discrete(name = "Cropping System")  #legend for colors
# save figures/forage/IWG_forage_Nrate_yr2S.jpeg    775x630

#Threeway means
NYSI1emm <- compute_emmeansNXF("modNYSI1")
#write.csv(NYSI1emm, 'data/Final_Data/NYSI1emm.csv')

#Pairwise P
emmsP <- emmeans(modNYSI1, ~ P, type = "response") # Obtain estimated marginal means (excluding N)
cld_dataNYSIP <- cld(emmsP, Letters=custom_letters) # Create compact letter display
#Pairwise C
emmsC <- emmeans(modNYSI1, ~ CROP, type = "response") # Obtain estimated marginal means (excluding N)
cld_dataNYSIC <- cld(emmsC, Letters=custom_letters) # Create compact letter display
cld_dataNYSIC$response <- format(cld_dataNYSIC$response, digits = 5)
rownames(cld_dataNYSIC) <- NULL
cld_dataNYSIC<- cld_dataNYSIC %>%
  select(CROP, response, .group)
colnames(cld_dataNYSIC) <- c("Cropping System", "IWG Forage (kg ha-1)", "Group")
cld_dataNYSIC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)
#Pairwise N
N_levels <- c(0, 40, 80, 120, 160)
emmsN <- emmeans(modNYSI1, specs = ~ N, at = list(N = N_levels), type = "response")
cld_dataNYSIN <- cld(emmsN, Letters=custom_letters) # Create compact letter display
#Pairwise N:P
emmsNP <- emmeans(modNYSI1, ~ N*P,at = list(N = N_levels), type= "response") # Obtain estimated marginal means
cld_dataNYSINP <- cld(emmsNP, Letters=custom_letters) # Create compact letter display
cld_dataNYSINP$response <- format(cld_dataNYSINP$response, digits = 5)
rownames(cld_dataNYSINP) <- NULL
cld_dataNYSINP<- cld_dataNYSINP %>%
  select(N, P, response, .group)
colnames(cld_dataNYSINP) <- c("N", "Site", "IWG Forage (kg ha-1)", "Group")
cld_dataNYSINP  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)

#slope stuff
emtrends_result<-emtrends(modNYSI1,~ P, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
  #view(emtrends_df)

#equations table
emtrends_result<-emtrends(modNYSI1,~ P*CROP, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
emmeans_results<-emmeans(modNYSI1, ~P*CROP, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("P", "CROP")) %>%
  select(P, CROP, emmean, N.trend, SE.x)
#view(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
merged_df$CROP <- factor(merged_df$CROP, levels = c("inter", "monoI"))  # Preferred order for CROP
# Create a new data frame with the calculated column
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sorted_df <- new_df %>%
  arrange(P, CROP)
#view(sorted_df)
#write.csv(sorted_df, "data/Final_Data/Nrate_esteff_IWGforage_yr2S.csv")

#equations table (N equations across cropping system)
emtrends_result<-emtrends(modNYSI1,~ CROP, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
emmeans_results<-emmeans(modNYSI1, ~ CROP, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("CROP")) %>%
  select(CROP, emmean, N.trend, SE.x)
merged_df$CROP <- factor(merged_df$CROP, levels = c("inter", "monoI"))  # Preferred order for CROP
# Create a new data frame with the calculated column
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sorted_df2 <- new_df %>%
  arrange(CROP)
#view(sorted_df2)
#write.csv(sorted_df2, "data/Final_Data/Nrate_esteff_IWGforage_yr2S_2.csv")
emtrends_result<-emtrends(modNYSI1,~ P, var= "N", infer=TRUE)
emtrends_df <- as.data.frame(emtrends_result)
desired_order_P <- c("MN", "NY", "KS", "WI")
emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
emmeans_results<-emmeans(modNYSI1, ~P, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
inner_join(emmeans_df, by = c("P")) %>%
select(P, emmean, N.trend, SE.x)
#view(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
# Create a new data frame with the calculated column
new_df <- merged_df %>%
mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
select(-emmean, -N.trend)
sorted_df3 <- new_df %>%
arrange(P)
#view(sorted_df3)
#write.csv(sorted_df3, "data/Final_Data/Nrate_esteff_IWGforage_yr2S_3.csv")

#IWG forage figure E:C (YS)
YSIemmsPC <- emmeans(modNYSI1, ~ P*CROP, type = "response") # Obtain estimated marginal means
emms_df <- as.data.frame(YSIemmsPC)
cld_dataYSIPC <- cld(YSIemmsPC, Letters=custom_letters)
cld_df <-as.data.frame(cld_dataYSIPC)
merged_df <- merge(emms_df, cld_df,by = c("P", "CROP"))
custom_labels <- c("Intercrop", "Monoculture IWG")
custom_colors <- c("darkmagenta", "cyan") 
IYSPC<-ggplot(NdYSI, aes(x = P, y = exp(predicted), color = CROP)) +
  geom_jitter(width = 0.2, height = 0, size = 3, alpha = 0.7) +
  labs(x = "Environment", y = "IWG Forage Yield") +
  geom_point(data = emms_df, aes(x = P, y = response, colour = CROP), 
             size = 4, shape = 18, color = "black")+ 
  geom_errorbar(data = emms_df, aes(x = P, ymin = lower.CL, ymax = upper.CL), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  geom_text(data = merged_df, aes(x = P, y = response.x, label = .group), 
            color = "black", vjust = 0, hjust = 2)+
  scale_color_manual(name = "Cropping System", labels = custom_labels,values = custom_colors)+
     ggtitle("Year 2 Summer")+
  theme(plot.title = element_text(hjust = 0.5))+
   guides(color = "none")#+
#  scale_y_continuous(breaks = c(0,1250,1500,1750,2000,2250,2500,2750,3000,3250,3500,3750,4000,4250,4500)) +
#  coord_cartesian(ylim = c(0,4500))
print(IYSPC)
#ggsave("figures/forage/IYSPC.jpg", plot = IYSPC, width = 10, height = 8, dpi = 300)

#N:E
# Define the desired order of 'P'
desired_order <- c("MN", "NY", "KS", "WI")
NdYSI$P <- factor(NdYSI$P, levels = desired_order)
# finding values for the function for each yr:location  
emtrends_resultY<-emtrends(modNYSI1,~ N*P*CROP, var= "N", infer=TRUE)
  emtrends_dfY <- as.data.frame(emtrends_resultY)
  emtrends_dfY$plvl <-
    ifelse(emtrends_dfY$p.value == 0.05, ".",
    ifelse(emtrends_dfY$p.value < 0.05  & emtrends_dfY$p.value >= 0.01, "*",
    ifelse(emtrends_dfY$p.value < 0.01  & emtrends_dfY$p.value >= 0.001, "**",
    ifelse(emtrends_dfY$p.value < 0.001, "***", ""))))
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_dfY$PC <- paste0(emtrends_dfY$P,emtrends_dfY$CROP)
  emtrends_dfY$P <- factor(emtrends_dfY$P, levels = desired_order_P)
emmeans_resultsY<-emmeans(modNYSI1, ~N*P*CROP, at=list(N=0))
  emmeans_dfY <- as.data.frame(emmeans_resultsY)
  emmeans_dfY$PC <- paste0(emmeans_dfY$P,emmeans_dfY$CROP)
mergedY <- emtrends_dfY %>%
  inner_join(emmeans_dfY, by = c("PC")) %>%
  dplyr::select(PC, P.x, CROP.x, emmean, N.trend, SE.x, plvl)
  colnames(mergedY)[2] <- "P"
  colnames(mergedY)[3] <- "CROP"
mergedY$P <- factor(mergedY$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
Y_df <- mergedY %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sortedY <- Y_df %>%
  arrange(P)
sortedY_I <- subset(sortedY, CROP== "inter")
sortedY_M <- subset(sortedY, CROP== "monoI")

sym_I <- sortedY_I %>%
  distinct(P) %>%
  mutate(
    x_sym = 0,
    y_sym = 8500
  )
sym_M <- sortedY_M %>%
  distinct(P) %>%
  mutate(
    x_sym = 0,
    y_sym = 8250
  )

#plot
IcomboplotNEYS <- ggplot(data=NdYSI) +
  geom_point(data = NdYSI, aes(x = N, y = PlotTotForageKgHa, shape = CROP)) +
  labs(x = "N-Rate (Kg ha-1)", y = "Total Forage", linetype = "Cropping System", shape = "Cropping System", color = "Harvest")+
  scale_x_continuous(breaks = c(0, 40, 80, 120, 160)) +
 # ylim(0, 1000) +
  facet_wrap(~P, scales = "free_y", ncol = 2) +
  scale_shape_manual(values = c(4, 25),labels = c("Intercropped", "Monoculture IWG"))+
  # functions come from equation in sorted
  geom_function(data=subset(NdYSI, P== "MN" & CROP == "inter"), fun=~3388.19*exp(0.0016*.x),color='darkgrey')+
  geom_function(data=subset(NdYSI, P== "MN" & CROP == "monoI"), fun=~4540.37*exp(0.0020*.x),color='darkgrey')+
  geom_function(data=subset(NdYSI, P== "NY" & CROP == "inter"), fun=~2328.72*exp(0.0053*.x),color='darkgrey')+
  geom_function(data=subset(NdYSI, P== "NY" & CROP == "monoI"), fun=~3102.77*exp(0.0045*.x),color='darkgrey')+
  geom_function(data=subset(NdYSI, P== "KS" & CROP == "inter"), fun=~1606.71*exp(0.0009*.x),color='darkgrey')+
  geom_function(data=subset(NdYSI, P== "KS" & CROP == "monoI"), fun=~2865.24*exp(0.0007*.x),color='darkgrey')+
  geom_function(data=subset(NdYSI, P== "WI" & CROP == "inter"), fun=~2898.08*exp(0.0040*.x),color='darkgrey')+
  geom_function(data=subset(NdYSI, P== "WI" & CROP == "monoI"), fun=~3792.37*exp(0.0044*.x),color='darkgrey')+
  geom_text(data = sortedY_I, mapping = aes(x = 30, y = 8500, label = equation),  size=2)+ # add equation to figure
  geom_point(data = sym_I, aes(x = x_sym, y = y_sym), shape = 4, size = 1, inherit.aes = FALSE)+
  geom_text(data = sortedY_M, mapping = aes(x = 30, y = 8250, label = equation),  size=2)+ # add equation to figure
  geom_point(data = sym_M, aes(x = x_sym, y = y_sym), shape = 25, size = 1, fill = "lightgrey", stroke = 0.6, inherit.aes = FALSE)+
  geom_text(data = sortedY_I, mapping = aes(x = 60, y = 8500, label = plvl))+
  geom_text(data = sortedY_M, mapping = aes(x = 60, y = 8250, label = plvl)) # add stars to figure
# add stars to figure
print(IcomboplotNEYS)
#ggsave("figures/forage/IcomboplotNEYS.jpg", plot = IcomboplotNEYS, width = 10, height = 8, dpi = 300)
```

#IWG forage year 2 fall
```{r}
#LINEAR 
modNYFI<-lmer(PlotIWGDryKgHa~N*P*CROP + (1|Rep), data=NdYFI)
anova(modNYFI)
#Check assumptions
NYFI_resid<-resid(modNYFI)
qqnorm(NYFI_resid)
qqline(NYFI_resid)
plot(modNYFI)
#log
modNYFI1<-lmer(log(PlotIWGDryKgHa)~N*P*CROP + (1|Rep), data=NdYFI)
anova(modNYFI1)
#Check assumptions
NYFI1_resid<-resid(modNYFI1)
qqnorm(NYFI1_resid)
qqline(NYFI1_resid)
plot(modNYFI1)

modNYFI1_summary <- summary(modNYFI1)
modNYFI1_coeff <- as.data.frame(modNYFI1_summary$coefficients)%>%
  filter(`Pr(>|t|)` < 0.05)
# Create custom table using kable and kableExtra
save_kable(
  knitr::kable(modNYFI1_coeff, 
               caption = "Y2 Fall Mixed-Effects Model: log(IWGForageKgHa) ~ Nrate * Location * CROPsystem + (1 | Rep)") %>%
    kable_styling(full_width = TRUE, 
                  position = "center", 
                  bootstrap_options = c("striped", "hover", "condensed")),
  file = "figures/forage/IWG_table_significant_coeff_yr2F.html")
# save iwg_table_significant_coeff_yr2F

max(NdYFI$PlotIWGDryKgHa)
#LINEAR plots
NdYFI$predicted <- predict(modNYFI1, newdata = NdYFI, re.form = NA)
ggplot(NdYFI, aes(x = N, y = PlotIWGDryKgHa, color = CROP, group= CROP)) +
    geom_point() + geom_line(aes(N, exp(predicted)))+ #regression through backtransformed predicted values
  labs(x = "N-Rate (Kg/ha)", y = "IWG Forage Yield (Kg/ha)") +  # Label the axes
  ggtitle("Yr 2 F Relationship between IWG Forage Yield and N-rate") +  # Add a title
scale_x_continuous(breaks = c(0, 40, 80, 120, 160))+ #fix x axis scale
#  ylim(0, 1600) +
  facet_wrap(~P, scales = "free_y",ncol=2)+ #make it by location (remove to make it across locations)
  scale_color_discrete(name = "Cropping System")  #legend for colors
# save figure/forage/IWG_forage_Nrate_yr2F.jpeg   775x630

#Threeway means
N_levels <- c(0, 40, 80, 120, 160)
emmsNPC <- emmeans(modNYFI1, specs = ~ N*P*CROP, at = list(N = N_levels), type = "response") # Obtain estimated marginal means (excluding N)
cld_dataNYFINPC <- cld(emmsNPC , Letters=custom_letters)

NYFI1emm <- compute_emmeansNYF("modNYFI1")
#write.csv(NYFI1emm, 'data/Final_Data/NYFI1emm.csv')

#Pairwise P
emmsP <- emmeans(modNYFI1, ~ P, type = "response") # Obtain estimated marginal means (excluding N)
cld_dataNYFIP <- cld(emmsP, Letters=custom_letters) # Create compact letter display
#Pairwise C
emmsC <- emmeans(modNYFI1, ~ CROP, type = "response") # Obtain estimated marginal means (excluding N)
cld_dataNYFIC <- cld(emmsC, Letters=custom_letters) # Create compact letter display
#Pairwise N
emmsN <- emmeans(modNYFI1, ~ N,at = list(N = N_levels), type= "response") # Obtain estimated marginal means
cld_dataNYFIN <- cld(emmsN, Letters=custom_letters) # Create compact letter display
#Pairwise N:C
emmsNC <- emmeans(modNYFI1, ~ N*CROP,at = list(N = N_levels), type= "response") # Obtain estimated marginal means
cld_dataNYFINC <- cld(emmsNC, Letters=custom_letters) # Create compact letter display
cld_dataNYFINC$response <- format(cld_dataNYFINC$response, digits = 5)
rownames(cld_dataNYFINC) <- NULL
cld_dataNYFINC<- cld_dataNYFINC %>%
  select(N, CROP, response, .group)
colnames(cld_dataNYFINC) <- c("N", "Cropping System", "IWG Forage (kg ha-1)", "Group")
cld_dataNYFINC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)
#Pairwise P:C
emmsPC <- emmeans(modNYFI1, ~ P*CROP,type= "response") # Obtain estimated marginal means
cld_dataNYFIPC <- cld(emmsPC, Letters=custom_letters) # Create compact letter display
cld_dataNYFIPC$response <- format(cld_dataNYFIPC$response, digits = 5)
rownames(cld_dataNYFIPC) <- NULL
cld_dataNYFIPC<- cld_dataNYFIPC %>%
  select(P, CROP, response, .group)
colnames(cld_dataNYFIPC) <- c("Site", "Cropping System", "IWG Forage (kg ha-1)", "Group")
cld_dataNYFIPC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)

#slope stuff
emtrends_result<-emtrends(modNYFI1,~ CROP, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_C <- c("intercrop", "monoculture")
  emtrends_df$CROP <- factor(emtrends_df$CROP, levels = desired_order_C)
  #view(emtrends_df)
  
#equations table
emtrends_result<-emtrends(modNYFI1,~ P*CROP, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
emmeans_results<-emmeans(modNYFI1, ~P*CROP, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("P", "CROP")) %>%
  select(P, CROP, emmean, N.trend, SE.x)
#view(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
merged_df$CROP <- factor(merged_df$CROP, levels = c("inter", "monoI"))  # Preferred order for CROP
# Create a new data frame with the calculated column
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sorted_df <- new_df %>%
  arrange(P, CROP)
#view(sorted_df)
#write.csv(sorted_df, "data/Final_Data/Nrate_esteff_IWGforage_yr2F.csv")


#equations table (N equations across cropping system)
emtrends_result<-emtrends(modNYFI1,~ CROP, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
emmeans_results<-emmeans(modNYFI1, ~ CROP, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("CROP")) %>%
  select(CROP, emmean, N.trend, SE.x)
merged_df$CROP <- factor(merged_df$CROP, levels = c("inter", "monoI"))  # Preferred order for CROP
# Create a new data frame with the calculated column
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sorted_df2 <- new_df %>%
  arrange(CROP)
#view(sorted_df2)
#write.csv(sorted_df2, "data/Final_Data/Nrate_esteff_IWGforage_yr2F_2.csv")
emtrends_result<-emtrends(modNYFI1,~ P, var= "N", infer=TRUE)
emtrends_df <- as.data.frame(emtrends_result)
desired_order_P <- c("MN", "NY", "KS", "WI")
emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
emmeans_results<-emmeans(modNYFI1, ~P, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
inner_join(emmeans_df, by = c("P")) %>%
select(P, emmean, N.trend, SE.x)
#view(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
# Create a new data frame with the calculated column
new_df <- merged_df %>%
mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
select(-emmean, -N.trend)
sorted_df3 <- new_df %>%
arrange(P)
#view(sorted_df3)
#write.csv(sorted_df3, "data/Final_Data/Nrate_esteff_IWGforage_yr2F_3.csv")


#IWG forage figure E:C (YF)
YFIemmsPC <- emmeans(modNYFI1, ~ P*CROP, type = "response") # Obtain estimated marginal means (excluding N)
emms_df <- as.data.frame(YFIemmsPC)
cld_dataYFIPC <- cld(YFIemmsPC, Letters=custom_letters)
cld_df <-as.data.frame(cld_dataYFIPC)
merged_df <- merge(emms_df, cld_df,by = c("P", "CROP"))
custom_labels <- c("Intercrop", "Monoculture IWG")
custom_colors <- c("darkmagenta", "cyan") 
IYFPC<-ggplot(NdYFI, aes(x = P, y = exp(predicted), color = CROP)) +
  geom_jitter(width = 0.2, height = 0, size = 3, alpha = 0.7) +
  labs(x = "Environment", y = "IWG Forage Yield") +
  geom_point(data = emms_df, aes(x = P, y = response), 
             size = 4, shape = 18, color = "black")+ 
  geom_errorbar(data = emms_df, aes(x = P, ymin = lower.CL, ymax = upper.CL), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  geom_text(data = merged_df, aes(x = P, y = response.x, label = .group), 
            color = "black", vjust = 0, hjust = 2)+
  scale_color_manual(name = "Cropping System", labels = custom_labels,values = custom_colors)+
     ggtitle("Year 2 Fall")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(breaks = c(250, 500, 750, 1000, 1250, 1500), limits = c(0, 1500))
print(IYFPC)
#ggsave("figures/forage/IYFPC.jpg", plot = IYFPC, width = 10, height = 8, dpi = 300)

#N:E
# Define the desired order of 'P'
desired_order <- c("MN", "NY", "KS", "WI")
NdYFI$P <- factor(NdYFI$P, levels = desired_order)
# finding values for the function for each yr:location  
emtrends_resultYF<-emtrends(modNYFI1,~ N*P*CROP, var= "N", infer=TRUE)
  emtrends_dfYF <- as.data.frame(emtrends_resultYF)
  emtrends_dfYF$plvl <-
    ifelse(emtrends_dfYF$p.value == 0.05, ".",
    ifelse(emtrends_dfYF$p.value < 0.05  & emtrends_dfYF$p.value >= 0.01, "*",
    ifelse(emtrends_dfYF$p.value < 0.01  & emtrends_dfYF$p.value >= 0.001, "**",
    ifelse(emtrends_dfYF$p.value < 0.001, "***", ""))))
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_dfYF$PC <- paste0(emtrends_dfYF$P,emtrends_dfYF$CROP)
  emtrends_dfYF$P <- factor(emtrends_dfYF$P, levels = desired_order_P)
emmeans_resultsYF<-emmeans(modNYFI1, ~N*P*CROP, at=list(N=0))
  emmeans_dfYF <- as.data.frame(emmeans_resultsYF)
  emmeans_dfYF$PC <- paste0(emmeans_dfYF$P,emmeans_dfYF$CROP)
mergedYF <- emtrends_dfYF %>%
  inner_join(emmeans_dfYF, by = c("PC")) %>%
  dplyr::select(PC, P.x, CROP.x, emmean, N.trend, SE.x, plvl)
  colnames(mergedYF)[2] <- "P"
  colnames(mergedYF)[3] <- "CROP"
mergedYF$P <- factor(mergedYF$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
YF_df <- mergedYF %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sortedYF <- YF_df %>%
  arrange(P)
sortedYF_I <- subset(sortedYF, CROP== "inter")
sortedYF_M <- subset(sortedYF, CROP== "monoI")

sym_I <- sortedYF_I %>%
  distinct(P) %>%
  mutate(
    x_sym = 0,
    y_sym = 5000
  )
sym_M <- sortedYF_M %>%
  distinct(P) %>%
  mutate(
    x_sym = 0,
    y_sym = 4750
  )

#plot
IcomboplotNEYF <- ggplot(data=NdYFI) +
  geom_point(data = NdYFI, aes(x = N, y = PlotTotForageKgHa, shape = CROP)) +
  labs(x = "N-Rate (Kg ha-1)", y = "Total Forage", linetype = "Cropping System", shape = "Cropping System", color = "Harvest")+
  scale_x_continuous(breaks = c(0, 40, 80, 120, 160)) +
 # ylim(0, 1000) +
  facet_wrap(~P, scales = "free_y", ncol = 2) +
  scale_shape_manual(values = c(4, 25),labels = c("Intercropped", "Monoculture IWG"))+
  # functions come from equation in sorted
  geom_function(data=subset(NdYFI, P== "MN" & CROP == "inter"), fun=~645.60*exp(0.0045*.x),color='darkgrey')+
  geom_function(data=subset(NdYFI, P== "MN" & CROP == "monoI"), fun=~1073.11*exp(0.0007*.x),color='darkgrey')+
  geom_function(data=subset(NdYFI, P== "NY" & CROP == "inter"), fun=~491.15*exp(0.0031*.x),color='darkgrey')+
  geom_function(data=subset(NdYFI, P== "NY" & CROP == "monoI"), fun=~616.55*exp(0.0002*.x),color='darkgrey')+
  geom_function(data=subset(NdYFI, P== "WI" & CROP == "inter"), fun=~581.26*exp(0.0038*.x),color='darkgrey')+
  geom_function(data=subset(NdYFI, P== "WI" & CROP == "monoI"), fun=~265.08*exp(0.0022*.x),color='darkgrey')+
  geom_text(data = sortedYF_I, mapping = aes(x = 30, y = 5000, label = equation),  size=2)+ # add equation to figure
  geom_point(data = sym_I, aes(x = x_sym, y = y_sym), shape = 4, size = 1, inherit.aes = FALSE)+
  geom_text(data = sortedYF_M, mapping = aes(x = 30, y = 4750, label = equation),  size=2)+ # add equation to figure
  geom_point(data = sym_M, aes(x = x_sym, y = y_sym), shape = 25, size = 1, fill = "lightgrey", stroke = 0.6, inherit.aes = FALSE)+
  geom_text(data = sortedYF_I, mapping = aes(x = 60, y = 5000, label = plvl))+
  geom_text(data = sortedYF_M, mapping = aes(x = 60, y = 4750, label = plvl)) # add stars to figure
# add stars to figure
print(IcomboplotNEYF)
# ggsave("figures/forage/IcomboplotNEYF.jpg", plot = IcomboplotNEYF, width = 10, height = 8, dpi = 300)
```

#IWG forage year 3 summer
```{r}
# KS IWG intercrop vaules don't exist 

#LINEAR 
modNZSI<-lmer(PlotIWGDryKgHa~N*P*CROP + (1|Rep), data=NdZSI)
anova(modNZSI)
#Check assumptions
NZSI_resid<-resid(modNZSI)
qqnorm(NZSI_resid)
qqline(NZSI_resid)
plot(modNZSI)
#log
modNZSI1<-lmer(log(PlotIWGDryKgHa)~N*P*CROP + (1|Rep), data=NdZSI)
anova(modNZSI1)
#Check assumptions
NZSI1_resid<-resid(modNZSI1)
qqnorm(NZSI1_resid)
qqline(NZSI1_resid)
plot(modNZSI1)
# normal looks better than log transformed

modNZSI1_summary <- summary(modNZSI1)
modNZSI1_coeff <- as.data.frame(modNZSI1_summary$coefficients)%>%
  filter(`Pr(>|t|)` < 0.05)
# Create custom table using kable and kableExtra
save_kable(
  knitr::kable(modNZSI1_coeff, 
               caption = "Y3 Summer Mixed-Effects Model: log(PlotTotForageKgHa) ~ Nrate * Location * CROPsystem + (1 | Rep)") %>%
    kable_styling(full_width = TRUE, 
                  position = "center", 
                  bootstrap_options = c("striped", "hover", "condensed")),
  file = "figures/forage/IWG_table_significant_coeff_yr3S.html")
# IWG_table_significant_coeff_yr3S

max(NdZSI$PlotIWGDryKgHa)
#LINEAR plots
NdZSI$predicted <- predict(modNZSI1, newdata = NdZSI, re.form = NA)
ggplot(NdZSI, aes(x = N, y = PlotIWGDryKgHa, color = CROP, group= CROP)) +
    geom_point() + geom_line(aes(N, exp(predicted)))+ #regression through backtransformed predicted values
  labs(x = "N-Rate (Kg/ha)", y = "IWG Forage Yield (Kg/ha)") +  # Label the axes
  ggtitle("Yr 3 S Relationship between IWG Forage Yield and N-rate") +  # Add a title
scale_x_continuous(breaks = c(0, 40, 80, 120, 160))+ #fix x axis scale
#  ylim(0, 1600) +
  facet_wrap(~P, scales = "free_y",ncol=2)+ #make it by location (remove to make it across locations)
  scale_color_discrete(name = "Cropping System")  #legend for colors
# save figres/forage/IWGforage_Nrate_yr3S.jpeg  775x630

#Threeway means
N_levels <- c(0, 40, 80, 120, 160)
emmsNPC <- emmeans(modNZSI1, specs = ~ N*P*CROP, at = list(N = N_levels), type = "response") # Obtain estimated marginal means (excluding N)
cld_dataNZSINPC <- cld(emmsNPC , Letters=custom_letters)

NZSI1emm <- compute_emmeansNZS("modNZSI1")
#write.csv(NZSI1emm, 'data/Final_Data/NZSI1emm.csv')

#Pairwise P
emmsP <- emmeans(modNZSI1, ~ P, type = "response") # Obtain estimated marginal means (excluding N)
cld_dataNZSIP <- cld(emmsP, Letters=custom_letters) # Create compact letter display
#Pairwise C
emmsC <- emmeans(modNZSI1, ~ CROP, type = "response") # Obtain estimated marginal means (excluding N)
cld_dataNZSIC <- cld(emmsC, Letters=custom_letters) # Create compact letter display
#Pairwise N
emmsN <- emmeans(modNZSI1, ~ N,at = list(N = N_levels), type= "response") # Obtain estimated marginal means
cld_dataNZSIN <- cld(emmsN, Letters=custom_letters) # Create compact letter display
#Pairwise N:C
emmsNC <- emmeans(modNZSI1, ~ N*CROP,at = list(N = N_levels), type= "response") # Obtain estimated marginal means
cld_dataNZSINC <- cld(emmsNC, Letters=custom_letters) # Create compact letter display
cld_dataNZSINC$response <- format(cld_dataNZSINC$response, digits = 5)
rownames(cld_dataNZSINC) <- NULL
cld_dataNZSINC<- cld_dataNZSINC %>%
  select(N, CROP, response, .group)
colnames(cld_dataNZSINC) <- c("N", "Cropping System", "IWG Forage (kg ha-1)", "Group")
cld_dataNZSINC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)
#Pairwise P:C
emmsPC <- emmeans(modNZSI1, ~ P*CROP,type= "response") # Obtain estimated marginal means
cld_dataNZSIPC <- cld(emmsPC, Letters=custom_letters) # Create compact letter display
cld_dataNZSIPC$response <- format(cld_dataNZSIPC$response, digits = 5)
rownames(cld_dataNZSIPC) <- NULL
cld_dataNZSIPC<- cld_dataNZSIPC %>%
  select(P, CROP, response, .group)
colnames(cld_dataNZSIPC) <- c("Site", "Cropping System", "IWG Forage (kg ha-1)", "Group")
cld_dataNZSIPC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)

#slope stuff
emtrends_result<-emtrends(modNZSI1,~ CROP, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_C <- c("intercrop", "monoculture")
  emtrends_df$CROP <- factor(emtrends_df$CROP, levels = desired_order_C)
  #view(emtrends_df)
  
#equations table
emtrends_result<-emtrends(modNZSI1,~ P*CROP, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
emmeans_results<-emmeans(modNZSI1, ~P*CROP, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("P", "CROP")) %>%
  select(P, CROP, emmean, N.trend, SE.x)
#view(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
merged_df$CROP <- factor(merged_df$CROP, levels = c("inter", "monoI"))  # Preferred order for CROP
# Create a new data frame with the calculated column
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sorted_df <- new_df %>%
  arrange(P, CROP)
#view(sorted_df)
#write.csv(sorted_df, "data/Final_Data/Nrate_esteff_IWGforage_yr3S.csv")
# first go down to 'IWG forage figure C (ZF)' and run code for model without KS
emtrends_result<-emtrends(modNZSI2,~ P, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
emmeans_results<-emmeans(modNZSI2, ~P, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("P")) %>%
  select(P, emmean, N.trend, SE.x)
#view(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
# Create a new data frame with the calculated column
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sorted_df3 <- new_df %>%
  arrange(P)
#view(sorted_df3)

#IWG forage figure P (ZF)
ZSIemmsP <- emmeans(modNZSI1, ~ P, type = "response") # Obtain estimated marginal means (excluding N)
emms_df <- as.data.frame(ZSIemmsP)
cld_dataZSIP <- cld(ZSIemmsP, Letters=custom_letters)
cld_df <-as.data.frame(cld_dataZSIP)
merged_df <- merge(emms_df, cld_df,by = c("P"))
custom_labels <- c("Intercrop", "Monoculture IWG")
custom_colors <- c("darkmagenta", "cyan") 
IZSP<-ggplot(NdZSI, aes(x = P, y = exp(predicted), color = CROP)) +
  geom_jitter(width = 0.2, height = 0, size = 3, alpha = 0.7) +
  labs(x = "Environment", y = "IWG Forage Yield") +
  geom_point(data = emms_df, aes(x = P, y = response), 
             size = 4, shape = 18, color = "black")+ 
  geom_errorbar(data = emms_df, aes(x = P, ymin = lower.CL, ymax = upper.CL), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  geom_text(data = merged_df, aes(x = P, y = response.x, label = .group), 
            color = "black", vjust = 0, hjust = 2)+
  scale_color_manual(name = "Cropping System", labels = custom_labels,values = custom_colors)+
     ggtitle("Year 3 Summer")+
  theme(plot.title = element_text(hjust = 0.5))#+
#  scale_y_continuous(breaks = c(250, 500, 750, 1000, 1250, 1500), limits = c(0, 1500))
print(IZSP)
#ggsave("figures/forage/IZSP.jpg", plot = IZSP, width = 10, height = 8, dpi = 300)

#IWG forage figure C (ZF)
# this harvest timepoint is an unbalanced design (one level of P (KS) only appears with one level of CROP (mono), while other P levels have both mono and inter)
# estimate CROP differences using valid locations:
NdZSI_2 <- subset(NdZSI, P !="KS")
modNZSI2 <- lmer(log(PlotIWGDryKgHa) ~ N*P*CROP + (1|Rep), data = NdZSI_2)
anova(modNZSI2)
NdZSI_2$predicted <- predict(modNZSI2, newdata = NdZSI_2, re.form = NA)

ZSIemmsC <- emmeans(modNZSI2, ~ CROP, type = "response") # Obtain estimated marginal means (excluding N)
emms_df <- as.data.frame(ZSIemmsC)
cld_dataZSIC <- cld(ZSIemmsC, Letters=custom_letters)
cld_df <-as.data.frame(cld_dataZSIC)
merged_df <- merge(emms_df, cld_df,by = c("CROP"))
custom_labels <- c("Intercrop", "Monoculture IWG")
custom_colors <- c("darkmagenta", "cyan") 
IZSC<-ggplot(NdZSI_2, aes(x = CROP, y = exp(predicted), color = CROP)) +
  geom_jitter(width = 0.2, height = 0, size = 3, alpha = 0.7) +
  labs(x = "Cropping System", y = "IWG Forage Yield") +
  geom_point(data = emms_df, aes(x = CROP, y = response), 
             size = 4, shape = 18, color = "black")+ 
  geom_errorbar(data = emms_df, aes(x = CROP, ymin = lower.CL, ymax = upper.CL), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  geom_text(data = merged_df, aes(x =CROP, y = response.x, label = .group), 
            color = "black", vjust = 0, hjust = 2)+
  scale_color_manual(name = "Cropping System", labels = custom_labels,values = custom_colors)+
     ggtitle("Year 3 Summer")+
  theme(plot.title = element_text(hjust = 0.5))
print(IZSC)
#ggsave("figures/forage/IZSC.jpg", plot = IZSC, width = 6, height = 8, dpi = 300)
```

#IWG forage year 3 fall
```{r}
#LINEAR 
modNZFI<-lmer(PlotIWGDryKgHa~N*P*CROP + (1|Rep), data=NdZFI)
anova(modNZFI)
#Check assumptions
NZFI_resid<-resid(modNZFI)
qqnorm(NZFI_resid)
qqline(NZFI_resid)
plot(modNZFI)
#log
modNZFI1<-lmer(log(PlotIWGDryKgHa)~N*P*CROP + (1|Rep), data=NdZFI)
anova(modNZFI1)
#Check assumptions
NZFI1_resid<-resid(modNZFI1)
qqnorm(NZFI1_resid)
qqline(NZFI1_resid)
plot(modNZFI1)
# normal looks better than log transformed

modNZFI1_summary <- summary(modNZFI1)
modNZFI1_coeff <- as.data.frame(modNZFI1_summary$coefficients)%>%
  filter(`Pr(>|t|)` < 0.05)
# Create custom table using kable and kableExtra
save_kable(
  knitr::kable(modNZFI1_coeff, 
               caption = "Y3 Fall Mixed-Effects Model: log(PlotIWGDryKgHa) ~ Nrate * Location * CROPsystem + (1 | Rep)") %>%
    kable_styling(full_width = TRUE, 
                  position = "center", 
                  bootstrap_options = c("striped", "hover", "condensed")),
  file = "figures/forage/IWG_table_significant_coeff_yr3F.html")
# IWG_table_significant_coeff_yr3F

max(NdZFI$PlotIWGDryKgHa)
#LINEAR plots
NdZFI$predicted <- predict(modNZFI1, newdata = NdZFI, re.form = NA)
ggplot(NdZFI, aes(x = N, y = PlotIWGDryKgHa, color = CROP, group= CROP)) +
    geom_point() + geom_line(aes(N, exp(predicted)))+ #regression through backtransformed predicted values
  labs(x = "N-Rate (Kg/ha)", y = "IWG Forage Yield (Kg/ha)") +  # Label the axes
  ggtitle("Yr 3 F Relationship between IWG Forage Yield and N-rate") +  # Add a title
scale_x_continuous(breaks = c(0, 40, 80, 120, 160))+ #fix x axis scale
#  ylim(0, 1600) +
  facet_wrap(~P, scales = "free_y",ncol=2)+ #make it by location (remove to make it across locations)
  scale_color_discrete(name = "Cropping System")  #legend for colors
# save figures/forage/IWGforage_Nrate_yr3F.jpeg  775x630

#Threeway means
N_levels <- c(0, 40, 80, 120, 160)
emmsNPC <- emmeans(modNZFI1, specs = ~ N*P*CROP, at = list(N = N_levels), type = "response") # Obtain estimated marginal means (excluding N)
cld_dataNZFINPC <- cld(emmsNPC , Letters=custom_letters)

NZFI1emm <- compute_emmeansNZS("modNZFI1")
#write.csv(NZFI1emm, 'data/Final_Data/NZFI1emm.csv')

#Pairwise P
emmsP <- emmeans(modNZFI1, ~ P, type = "response") # Obtain estimated marginal means (excluding N)
cld_dataNZFIP <- cld(emmsP, Letters=custom_letters) # Create compact letter display
#Pairwise C
emmsC <- emmeans(modNZFI1, ~ CROP, type = "response") # Obtain estimated marginal means (excluding N)
cld_dataNZFIC <- cld(emmsC, Letters=custom_letters) # Create compact letter display
#Pairwise N
emmsN <- emmeans(modNZFI1, ~ N,at = list(N = N_levels), type= "response") # Obtain estimated marginal means
cld_dataNZFIN <- cld(emmsN, Letters=custom_letters) # Create compact letter display
#Pairwise N:C
emmsNC <- emmeans(modNZFI1, ~ N*CROP,at = list(N = N_levels), type= "response") # Obtain estimated marginal means
cld_dataNZFINC <- cld(emmsNC, Letters=custom_letters) # Create compact letter display
cld_dataNZFINC$response <- format(cld_dataNZFINC$response, digits = 5)
rownames(cld_dataNZFINC) <- NULL
cld_dataNZFINC<- cld_dataNZFINC %>%
  select(N, CROP, response, .group)
colnames(cld_dataNZFINC) <- c("N", "Cropping System", "IWG Forage (kg ha-1)", "Group")
cld_dataNZFINC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)
#Pairwise P:C
emmsPC <- emmeans(modNZFI1, ~ P*CROP,type= "response") # Obtain estimated marginal means
cld_dataNZFIPC <- cld(emmsPC, Letters=custom_letters) # Create compact letter display
cld_dataNZFIPC$response <- format(cld_dataNZFIPC$response, digits = 5)
rownames(cld_dataNZFIPC) <- NULL
cld_dataNZFIPC<- cld_dataNZFIPC %>%
  select(P, CROP, response, .group)
colnames(cld_dataNZFIPC) <- c("Site", "Cropping System", "IWG Forage (kg ha-1)", "Group")
cld_dataNZFIPC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)

#slope stuff
emtrends_result<-emtrends(modNZFI1,~ CROP, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_C <- c("intercrop", "monoculture")
  emtrends_df$CROP <- factor(emtrends_df$CROP, levels = desired_order_C)
  #view(emtrends_df)
  
#equations table
emtrends_result<-emtrends(modNZFI1,~ P*CROP, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
emmeans_results<-emmeans(modNZFI1, ~P*CROP, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("P", "CROP")) %>%
  select(P, CROP, emmean, N.trend, SE.x)
#view(merged_df)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
merged_df$CROP <- factor(merged_df$CROP, levels = c("inter", "monoI"))  # Preferred order for CROP
# Create a new data frame with the calculated column
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sorted_df <- new_df %>%
  arrange(P, CROP)
#view(sorted_df)
#write.csv(sorted_df, "data/Final_Data/Nrate_esteff_IWGforage_yr3F.csv")
emtrends_result<-emtrends(modNZFI1,~ P, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_P <- c("MN", "NY", "KS", "WI")
  emtrends_df$P <- factor(emtrends_df$P, levels = desired_order_P)
emmeans_results<-emmeans(modNZFI1, ~P, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c("P")) %>%
  select(P, emmean, N.trend, SE.x)
merged_df$P <- factor(merged_df$P, levels = c("MN", "NY", "KS", "WI"))  # Preferred order for P
# Create a new data frame with the calculated column
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sorted_df3 <- new_df %>%
  arrange(P)
#view(sorted_df3)


#IWG forage figure E:C (ZF)
ZFIemmsPC <- emmeans(modNZFI1, ~ P*CROP, type = "response") # Obtain estimated marginal means (excluding N)
emms_df <- as.data.frame(ZFIemmsPC)
cld_dataZFIPC <- cld(ZFIemmsPC, Letters=custom_letters)
cld_df <-as.data.frame(cld_dataZFIPC)
merged_df <- merge(emms_df, cld_df,by = c("P", "CROP"))
custom_labels <- c("Intercrop", "Monoculture IWG")
custom_colors <- c("darkmagenta", "cyan") 
IZFPC<-ggplot(NdZFI, aes(x = P, y = exp(predicted), color = CROP)) +
  geom_jitter(width = 0.2, height = 0, size = 3, alpha = 0.7) +
  labs(x = "Environment", y = "IWG Forage Yield") +
  geom_point(data = emms_df, aes(x = P, y = response), 
             size = 4, shape = 18, color = "black")+ 
  geom_errorbar(data = emms_df, aes(x = P, ymin = lower.CL, ymax = upper.CL), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  geom_text(data = merged_df, aes(x = P, y = response.x, label = .group), 
            color = "black", vjust = 0, hjust = 2)+
  scale_color_manual(name = "Cropping System", labels = custom_labels,values = custom_colors)+
     ggtitle("Year 3 Fall")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(breaks = c(250, 500, 750, 1000, 1250, 1500), limits = c(0, 1500))
print(IZFPC)
#ggsave("figures/forage/IZFPC.jpg", plot = IZFPC, width = 10, height = 8, dpi = 300)
```


# IWG Forage anovas Table 
```{r}
aov.tableXS <- anova(modNXSI1)
tableIFXS = flextable(data = aov.tableXS %>%
                    #filter(`Pr(>F)` < 0.05) %>%
                    mutate(`Pr(>F)` = formatC(`Pr(>F)`, digits = 3)) %>% 
                    select(`Pr(>F)`) %>%
                    rownames_to_column(" ")) 
print(tableIFXS)
# save figures/forage/gt_IFXS 

aov.tableXF <- anova(modNXFI1)
tableIFXF = flextable(data = aov.tableXF %>%
                    #filter(`Pr(>F)` < 0.05) %>%
                    mutate(`Pr(>F)` = formatC(`Pr(>F)`, digits = 3)) %>% 
                    select(`Pr(>F)`) %>%
                    rownames_to_column(" ")) 
print(tableIFXF)
# save figures/forage/gt_IFXF

aov.tableYS <- anova(modNYSI1) 
tableIFYS = flextable(data = aov.tableYS %>%
                    #filter(`Pr(>F)` < 0.05) %>%
                    mutate(`Pr(>F)` = formatC(`Pr(>F)`, digits = 3)) %>% 
                    select(`Pr(>F)`) %>%
                    rownames_to_column(" ")) 
print(tableIFYS)
# save figures/forage/gt_IFYS 

aov.tableYF <- anova(modNYFI1)
tableIFYF = flextable(data = aov.tableYF %>%
                    #filter(`Pr(>F)` < 0.05) %>%
                    mutate(`Pr(>F)` = formatC(`Pr(>F)`, digits = 3)) %>% 
                    select(`Pr(>F)`) %>%
                    rownames_to_column(" ")) 
print(tableIFYF)
# save figures/forage/gt_IFYF

aov.tableZS <- anova(modNZSI1)
tableIFZS = flextable(data = aov.tableZS %>%
                    #filter(`Pr(>F)` < 0.05) %>%
                    mutate(`Pr(>F)` = formatC(`Pr(>F)`, digits = 3)) %>% 
                    select(`Pr(>F)`) %>%
                    rownames_to_column(" ")) 
print(tableIFZS)
# save figures/forage/gt_IFZS 

aov.tableZF <- anova(modNZFI1)
tableIFZF = flextable(data = aov.tableZF %>%
                    #filter(`Pr(>F)` < 0.05) %>%
                    mutate(`Pr(>F)` = formatC(`Pr(>F)`, digits = 3)) %>% 
                    select(`Pr(>F)`) %>%
                    rownames_to_column(" ")) 
print(tableIFZF)
# save figures/forage/gt_IFZF


my_modelsNG <- list(modNXSI1, modNXFI1, modNYSI1, modNYFI1, modNZSI1, modNZFI1)
anovasNG <- purrr::map(my_modelsNG, ~anova(.))
names(anovasNG) <- c("Year 1 S", "Year 1 F", "Year 2 S", "Year 2 F", "Year 3 S", "Year 3 F")

# Function to format p-values as stars
format_p_value <- function(p_val) {
  stars <- ifelse(p_val < 0.001, "***", ifelse(p_val < 0.01, "**", ifelse(p_val < 0.05, "*", "")))
  return(stars)
}

# Apply the function to your ANOVA results
NG_stars_tibble <- map(anovasNG, as_tibble, rownames="term") %>%
  bind_rows(.id = "model") %>%
  mutate(stars = map_chr(`Pr(>F)`, format_p_value))

NG_stars_tibble <- NG_stars_tibble %>%
  mutate(term = ifelse(term == "P", "E", term)) %>%
  mutate(term = ifelse(term == "N:P", "N:E", term))%>%
  mutate(term = ifelse(term == "P:CROP", "E:CROP", term))%>%
  mutate(term = ifelse(term == "N:P:CROP", "N:E:CROP", term))%>%
  filter(term != "Residuals")

# Print the tibble
print(NG_stars_tibble)

NG_stars <-NG_stars_tibble |> 
  select(model, term, stars) |>
  pivot_wider(names_from = term, values_from = stars)

gt_NG <- gt(NG_stars)

gt_NG |> gtsave("figures/forage/gt_IF.png", expand = 10)
```

# combined IWG forage years plots E:C
```{r}
IEC <- ggarrange(
IXSPC,
IXFPC,
IYSPC,
IYFPC,
IZFPC,
nrow = 3, 
ncol = 2,
common.legend = TRUE,
legend = "right"
)
IEC
#save figures/forage/IEC.jpg   2000x1800

# compact letter display is showing E:C interaction for all harvests except Year 3 S which is showing cld for location (E); within Y3S, 
IEC2 <- ggarrange(
IXSPC,
IXFPC,
IYSPC,
IYFPC,
IZSP,
IZFPC,
nrow = 3, 
ncol = 2,
common.legend = TRUE,
legend = "right"
)
IEC2
#save figures/forage/IEC2.jpg   2000x1800
```

#IWG forage combo plot N:E
```{r}
# Layer all the plots together!
colors <- c("Year 1 Summer Harvest" = "red", 
            "Year 1 Fall Harvest" = "pink", 
            "Year 2 Summer Harvest" = "blue", 
            "Year 2 Fall Harvest" = "lightblue", 
            "Year 3 Summer Harvest" = "darkgreen",
            "Year 3 Fall Harvest" = "green")
legend_order <- c("Year 1 Summer Harvest", "Year 1 Fall Harvest", 
                  "Year 2 Summer Harvest", "Year 2 Fall Harvest",
                  "Year 3 Summer Harvest", "Year 3 Fall Harvest")
NdXSI$P <- factor(NdXSI$P, levels = desired_order)
# equations come from sorted_data3 from each harvest year chunk. This is the emmeans of P
IFcomboplot <- ggplot() +
  geom_point(data = NdXSI, aes(x = N, y = PlotIWGDryKgHa, color = "Year 1 Summer Harvest", shape= CROP)) +
  geom_point(data = NdXFI, aes(x = N, y = PlotIWGDryKgHa, color = "Year 1 Fall Harvest", shape= CROP)) +
  geom_point(data = NdYSI, aes(x = N, y = PlotIWGDryKgHa, color = "Year 2 Summer Harvest", shape= CROP)) +
  geom_point(data = NdYFI, aes(x = N, y = PlotIWGDryKgHa, color = "Year 2 Fall Harvest", shape= CROP)) +
  geom_point(data = NdZSI, aes(x = N, y = PlotIWGDryKgHa, color = "Year 3 Summer Harvest", shape= CROP)) +
  geom_point(data = NdZFI, aes(x = N, y = PlotIWGDryKgHa, color = "Year 3 Fall Harvest", shape= CROP)) +  
  labs(x = "N-Rate (kg ha-1)", y = "IWG Forage Yield",
    color = "Harvest", shape = "Cropping System") +
  scale_x_continuous(breaks = c(0, 40, 80, 120, 160)) +
#  ylim(0, 14800) +
  facet_wrap(~P, scales = "free", ncol = 2) +
  scale_color_manual(values = colors, limits = legend_order)+
  scale_shape_manual(values = c(4, 25), labels = c("Intercropped", "Monoculture IWG"))+
  geom_function(data=subset(NdXSI, P== "MN"), fun=~1737.51*exp(0.0027*.x),color='red')+
  geom_function(data=subset(NdXSI, P== "NY"), fun=~2695.81*exp(0.0050*.x),color='red')+
  geom_function(data=subset(NdXSI, P== "KS"), fun=~7357.19*exp(0.0007*.x),color='red')+
  geom_function(data=subset(NdXSI, P== "WI"), fun=~6843.18*exp(0.0009*.x),color='red')+
  geom_function(data=subset(NdXFI, P== "MN"), fun=~651.94*exp(0.0020*.x),color='pink')+
  geom_function(data=subset(NdXFI, P== "NY"), fun=~263.84*exp(0.0044*.x),color='pink')+
  geom_function(data=subset(NdXFI, P== "WI"), fun=~283.04*exp(-0.0010*.x),color='pink')+
  geom_function(data=subset(NdYSI, P== "MN"), fun=~3922.15*exp(0.0018*.x),color='blue')+
  geom_function(data=subset(NdYSI, P== "NY"), fun=~2688.03*exp(0.0049*.x),color='blue')+
  geom_function(data=subset(NdYSI, P== "KS"), fun=~2145.60*exp(0.0008*.x),color='blue')+
  geom_function(data=subset(NdYSI, P== "WI"), fun=~3315.20*exp(0.0042*.x),color='blue')+
  geom_function(data=subset(NdYFI, P== "MN"), fun=~832.34*exp(0.0026*.x),color='lightblue')+
  geom_function(data=subset(NdYFI, P== "NY"), fun=~550.29*exp(0.0016*.x),color='lightblue')+
  geom_function(data=subset(NdYFI, P== "WI"), fun=~392.53*exp(0.0030*.x),color='lightblue')+
  geom_function(data=subset(NdZSI, P== "MN"), fun=~2073.88*exp(0.0028*.x),color='darkgreen')+
  geom_function(data=subset(NdZSI, P== "NY"), fun=~306.88*exp(0.0026*.x),color='darkgreen')+
  geom_function(data=subset(NdZSI, P== "WI"), fun=~6845.80*exp(0.0023*.x),color='darkgreen')+
  geom_function(data=subset(NdZFI, P== "MN"), fun=~407.87*exp(0.0019*.x),color='green')+
  geom_function(data=subset(NdZFI, P== "NY"), fun=~1104.52*exp(0.0007*.x),color='green')+
  geom_function(data=subset(NdZFI, P== "WI"), fun=~758.02*exp(0.0008*.x),color='green')
print(IFcomboplot)
#ggsave("figures/forage/IFcomboplot.jpg", plot = IFcomboplot, width = 12, height = 10, dpi = 300)
```



## Alfalfa Forage Yield 

#Alf forage year 1 summer
```{r}
#LINEAR 
modNXSA<-lmer(PlotAlfDryKgHa~N*P*CROP + (1|P:Rep), data=NdXSA)
anova(modNXSA)
#Check assumptions
NXSA_resid<-resid(modNXSA)
qqnorm(NXSA_resid)
qqline(NXSA_resid)
plot(modNXSA)
#log transform
modNXSA1<-lmer(log(PlotAlfDryKgHa)~N*P*CROP + (1|P:Rep), data=NdXSA)
anova(modNXSA1)
#Check assumptions
NXSA_resid1<-resid(modNXSA1)
qqnorm(NXSA_resid1)
qqline(NXSA_resid1)
plot(modNXSA1)
# could use either, normal is slightly better and includes significance for N:E and N:C

emtrends(modNXSA1, ~P*CROP, var= "N")
emtrends(modNXSA1, ~1, var= "N", infer= TRUE) #(averages 8 slopes across interactions)
emmip(modNXSA1, P~N|CROP, at=list(N=c(40, 80, 120)))

modNXSA1_summary <- summary(modNXSA1)
modNXSA1_coeff <- as.data.frame(modNXSA1_summary$coefficients)%>%
  filter(`Pr(>|t|)` < 0.05)
# Create custom table using kable and kableExtra
save_kable(
  knitr::kable(modNXSA1_coeff, 
               caption = "Y1 Summer Mixed-Effects Model: log(PlotAlfDryKgHa) ~ Nrate * Location * CROPsystem + (1 | Rep)") %>%
    kable_styling(full_width = TRUE, 
                  position = "center", 
                  bootstrap_options = c("striped", "hover", "condensed")),
  file = "figures/forage/ALF_table_significant_coeff_yr1S.html")
# ALF_table_significant_coeff_yr1S    

#(old)
#rec
modNXSA1N<-lmer(log(PlotAlfDryKgHa)~N+P*CROP + (1|P:Rep), data=NdXSA)
emtrends(modNXSA1N, ~1, var= "N", infer= TRUE)
emmip(modNXSA1N, P~N|CROP, at=list(N=c(0, 80, 160)))

max(NdXSA$PlotAlfDryKgHa)
#linear plots
NdXSA$predicted <- predict(modNXSA1, newdata = NdXSA, re.form = NA)
ggplot(NdXSA, aes(x = N, y = PlotAlfDryKgHa, color = C, group= C)) +
    geom_point() + geom_line(aes(N, exp(predicted)))+ #regression through backtransformed predicted values
  labs(x = "N-Rate (Kg/ha)", y = "Alf Forage Yield (Kg/ha)") +  # Label the axes
  ggtitle("Yr 1 S Relationship between Alf Forage Yield and N-rate") +  # Add a title
scale_x_continuous(breaks = c(0, 40, 80, 120, 160))+ #fix x axis scale
#  ylim(0, 11000) +
  facet_wrap(~P, scales = "free_y",ncol=2)+ #make it by location (remove to make it across locations)
  scale_color_discrete(name = "Cropping System")  #legend for colors
# save figures/forage/ALFforage_Nrate_yr1S.jpeg  775x630

#Threeway means
NXSA1emm <- compute_emmeansNXS("modNXSA1")
#write.csv(NXSA1emm, 'data/Final_Data/NXSA1emm.csv')

#Alf forage figure E:C (XS)
max(NdXSA$predicted)
exp(9.08082)
XSAemmsPC <- emmeans(modNXSA1, ~ P*CROP, type = "response") # Obtain estimated marginal means (excluding N)
emms_df <- as.data.frame(XSAemmsPC)
cld_dataXSAPC <- cld(XSAemmsPC, Letters=custom_letters)
cld_df <-as.data.frame(cld_dataXSAPC)
merged_df <- merge(emms_df, cld_df,by = c("P", "CROP"))
custom_labels <- c("Intercrop", "Monoculture Alfalfa")
custom_colors <- c("darkmagenta", "coral1") 
AXSPC<-ggplot(NdXSA, aes(x = P, y = exp(predicted), color = CROP)) +
  geom_jitter(width = 0.2, height = 0, size = 3, alpha = 0.7) +
  labs(x = "Environment", y = "Alfalfa Forage Yield") +
  geom_point(data = emms_df, aes(x = P, y = response), 
             size = 4, shape = 18, color = "black")+ 
  geom_errorbar(data = emms_df, aes(x = P, ymin = lower.CL, ymax = upper.CL), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  geom_text(data = merged_df, aes(x = P, y = response.x, label = .group), 
            color = "black", vjust = 0, hjust = 2)+
  scale_color_manual(name = "Cropping System", labels = custom_labels,values = custom_colors)+
     ggtitle("Year 1 Summer")+
  theme(plot.title = element_text(hjust = 0.5))+
   guides(color = "none")+
  scale_y_continuous(breaks = c(1000, 3000, 5000, 7000,9000), limits = c(0, 9500))
print(AXSPC)
#ggsave("figures/forage/AXSPC.jpg", plot = AXSPC, width = 10, height = 8, dpi = 300)


#alf forage plot N (XS)
#EQUATION tables JUST N 
emtrends_result<-emtrends(modNXSA1,~ 1, var= "N", infer=TRUE)
emtrends_df <- as.data.frame(emtrends_result)
emmeans_results<-emmeans(modNXSA1, ~1, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
emtrends_df <- emtrends_df %>% mutate(key = 1)
emmeans_df <- emmeans_df %>% mutate(key = 1)
merged_df <- inner_join(emtrends_df, emmeans_df, by = "key")%>%
  select(emmean, N.trend, SE.x)
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
new_df
AFplotN <- ggplot() +
  geom_point(data = NdXSA, aes(x = N, y = PlotAlfDryKgHa, shape= CROP), color= "red") +
  labs(x = "N-Rate (kg ha-1)", y = "Alfalfa Forage Yield") +
  scale_x_continuous(breaks = c(0, 40, 80, 120, 160)) +
  scale_shape_manual(values = c("intercrop" = 4, "monoculture" = 20), labels = c("Intercropped", "Monoculture Alfalfa")) +
  geom_function(data=NdXSA, fun=~4141.15*exp(-0.0009*.x),color='red')+
  guides(
    shape = guide_legend(title = "Cropping System"))
print(AFplotN)





#Pairwise P
emmsP <- emmeans(modNXSA, ~ P, type = "response") # Obtain estimated marginal means
cld_dataNXSAP <- cld(emmsP, Letters=custom_letters) # Create compact letter display
#Pairwise C
emmsC <- emmeans(modNXSA, ~ CROP, type = "response") # Obtain estimated marginal means 
cld_dataNXSAC <- cld(emmsC, Letters=custom_letters) # Create compact letter display
#Pairwise N
N_levels <- c(0, 40, 80, 120, 160)
emmsN <- emmeans(modNXSA, specs = ~ N, at = list(N = N_levels), type = "response")
cld_dataNXSAN <- cld(emmsN, Letters=custom_letters) # Create compact letter display
cld_dataNXSAN$response <- format(cld_dataNXSAN$response, digits = 5)
cld_dataNXSAN<- cld_dataNXSAN %>%
  select(N, response, .group)
colnames(cld_dataNXSAN) <- c("N","IWG Forage (kg ha-1)", "Group")
cld_dataNXSAN  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)
#Pairwise P:C
emmsPC <- emmeans(modNXSA, ~ P*CROP, type= "response") # Obtain estimated marginal means
cld_dataNXSAPC <- cld(emmsPC, Letters=custom_letters) # Create compact letter display
cld_dataNXSAPC$response <- format(cld_dataNXSAPC$response, digits = 5)
rownames(cld_dataNXSAPC) <- NULL
cld_dataNXSAPC<- cld_dataNXSAPC %>%
  select(P,CROP, response, .group)
colnames(cld_dataNXSAPC) <- c("Site","Cropping System","Alfalfa Forage (kg ha-1)", "Group")
cld_dataNXSAPC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)

#This gives us the slope for each interactions as well as a P value indicating significance level for that slope
emtrends(modNXSA,~ P*CROP, var= "N", infer=TRUE)
emtrends(modNXSA,~ P, var= "N", infer=TRUE)
emtrends(modNXSA,~ CROP, var= "N", infer=TRUE)
emtrends(modNXSA,~N, var= "N", infer=TRUE)
summary(modNXSA)
emtrends(modNXSA,~ P, var= "N", infer=TRUE)
summary(modNXSA)
```

#Alf forage year 1 fall
```{r}
#LINEAR
modNXFA<-lmer(PlotAlfDryKgHa~N*P*CROP + (1|Rep), data=NdXFA)
anova(modNXFA)
#Check assumptions
NXFA_resid<-resid(modNXFA)
qqnorm(NXFA_resid)
qqline(NXFA_resid)
plot(modNXFA)
#log transform
modNXFA1<-lmer(log(PlotAlfDryKgHa)~N*P*CROP + (1|Rep), data=NdXFA)
anova(modNXFA1)
#Check assumptions
NXFA1_resid<-resid(modNXFA1)
qqnorm(NXFA1_resid)
qqline(NXFA1_resid)
plot(modNXFA1)

modNXFA1_summary <- summary(modNXFA1)
modNXFA1_coeff <- as.data.frame(modNXFA1_summary$coefficients)%>%
  filter(`Pr(>|t|)` < 0.05)
# Create custom table using kable and kableExtra
save_kable(
  knitr::kable(modNXFA1_coeff, 
               caption = "Y1 Fall Mixed-Effects Model: log(PlotAlfDryKgHa) ~ Nrate * Location * CROPsystem + (1 | Rep)") %>%
    kable_styling(full_width = TRUE, 
                  position = "center", 
                  bootstrap_options = c("striped", "hover", "condensed")),
  file = "figures/forage/ALF_table_significant_coeff_yr1F.html")
# ALF_table_significant_coeff_yr1F

max(NdXFA$PlotAlfDryKgHa)
#linear plots
NdXFA$predicted <- predict(modNXFA1, newdata = NdXFA, re.form = NA)
ggplot(NdXFA, aes(x = N, y = PlotAlfDryKgHa, color = C, group= C)) +
    geom_point() + geom_line(aes(N, exp(predicted)))+ #regression through backtransformed predicted values
  labs(x = "N-Rate (Kg/ha)", y = "Alf Forage Yield (Kg/ha)") +  # Label the axes
  ggtitle("Yr 1 F Relationship between Alf Forage Yield and N-rate") +  # Add a title
scale_x_continuous(breaks = c(0, 40, 80, 120, 160))+ #fix x axis scale
#  ylim(0, 3300) +
  facet_wrap(~P, scales = "free_y",ncol=2)+ #make it by location (remove to make it across locations)
  scale_color_discrete(name = "Cropping System")  #legend for colors
# save figures/forage/ALFforage_Nrate_yr1F.jpeg  775x630

#Threeway means
NXFA1emm <- compute_emmeansNXF("modNXFA1")
#write.csv(NXFA1emm, 'data/Final_Data/NXFA1emm.csv')

#Alf forage figure E:C (XF)
XFAemmsPC <- emmeans(modNXFA1, ~ P*CROP, type = "response") # Obtain estimated marginal means (excluding N)
emms_df <- as.data.frame(XFAemmsPC)
cld_dataXFAPC <- cld(XFAemmsPC, Letters=custom_letters)
cld_df <-as.data.frame(cld_dataXFAPC)
merged_df <- merge(emms_df, cld_df,by = c("P", "CROP"))
custom_labels <- c("Intercrop", "Monoculture Alfalfa")
custom_colors <- c("darkmagenta", "coral1") 
AXFPC<-ggplot(NdXFA, aes(x = P, y = exp(predicted), color = CROP)) +
  geom_jitter(width = 0.2, height = 0, size = 3, alpha = 0.7) +
  labs(x = "Environment", y = "Alfalfa Forage Yield") +
  geom_point(data = emms_df, aes(x = P, y = response), 
             size = 4, shape = 18, color = "black")+ 
  geom_errorbar(data = emms_df, aes(x = P, ymin = lower.CL, ymax = upper.CL), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  geom_text(data = merged_df, aes(x = P, y = response.x, label = .group), 
            color = "black", vjust = 0, hjust = 2)+
  scale_color_manual(name = "Cropping System", labels = custom_labels,values = custom_colors)+
     ggtitle("Year 1 Fall")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(breaks = c(1000, 3000, 5000, 7000,9000), limits = c(0, 3500))
print(AXFPC)
#ggsave("figures/forage/AXFPC.jpg", plot = AXFPC, width = 10, height = 8, dpi = 300)





#Pairwise P
emmsP <- emmeans(modNXFA1, ~ P, type = "response") # Obtain estimated marginal means
cld_dataNXFAP <- cld(emmsP, Letters=custom_letters) # Create compact letter display
#Pairwise P:C
emmsPC <- emmeans(modNXFA1, ~ P*CROP, type= "response") # Obtain estimated marginal means
cld_dataNXFAPC <- cld(emmsPC, Letters=custom_letters) # Create compact letter display
cld_dataNXFAPC$response <- format(cld_dataNXFAPC$response, digits = 5)
rownames(cld_dataNXFAPC) <- NULL
cld_dataNXFAPC<- cld_dataNXFAPC %>%
  select(P,CROP, response, .group)
colnames(cld_dataNXFAPC) <- c("Site","Cropping System","IWG Forage (kg ha-1)", "Group")
cld_dataNXFAPC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)

emtrends_result<-emtrends(modNXFA1,~ 1, var= "N", infer=TRUE)
emtrends_df <- as.data.frame(emtrends_result)
emmeans_results<-emmeans(modNXFA1, ~1, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
emtrends_df <- emtrends_df %>% mutate(key = 1)
emmeans_df <- emmeans_df %>% mutate(key = 1)
merged_df <- inner_join(emtrends_df, emmeans_df, by = "key")%>%
  select(emmean, N.trend, SE.x)
view(merged_df)
```

#Alf forage year 2 summer
```{r}
# remove MN plot 1222, it only has 0 for values
NdYSA <- NdYSA %>%
  filter(Plot != 1222)

#LINEAR 
modNYSA<-lmer(PlotAlfDryKgHa~N*P*CROP + (1|Rep), data=NdYSA)
anova(modNYSA)
#Check assumptions
NYSA_resid<-resid(modNYSA)
qqnorm(NYSA_resid)
qqline(NYSA_resid)
plot(modNYSA)
#Logtransform
modNYSA1<-lmer(log(PlotAlfDryKgHa)~N*P*CROP + (1|Rep), data=NdYSA)
anova(modNYSA1)
#check assumptions logtransform
NYSA_resid1<-resid(modNYSA1)
qqnorm(NYSA_resid1)
qqline(NYSA_resid1)
plot(modNYSA1)
# normal is slightly better and has additional significance for N:E and N:C

modNYSA1_summary <- summary(modNYSA1)
modNYSA1_coeff <- as.data.frame(modNYSA1_summary$coefficients)%>%
  filter(`Pr(>|t|)` < 0.05)
# Create custom table using kable and kableExtra
save_kable(
  knitr::kable(modNYSA1_coeff, 
               caption = "Y2 Summer Mixed-Effects Model: log(PlotAlfDryKgHa) ~ Nrate * Location * CROPsystem + (1 | Rep)") %>%
    kable_styling(full_width = TRUE, 
                  position = "center", 
                  bootstrap_options = c("striped", "hover", "condensed")),
  file = "figures/forage/ALF_table_significant_coeff_yr2S.html")
# ALF_table_significant_coeff_yr2S

max(NdYSA$PlotAlfDryKgHa)
#LINEAR plots
NdYSA$predicted <- predict(modNYSA1, newdata = NdYSA, re.form = NA)
ggplot(NdYSA, aes(x = N, y = PlotAlfDryKgHa, color = CROP, group= CROP)) +
    geom_point() + geom_line(aes(N, exp(predicted)))+ #regression through backtransformed predicted values
  labs(x = "N-Rate (Kg/ha)", y = "Alf Forage Yield (Kg/ha)") +  # Label the axes
  ggtitle("Yr 2 S Relationship between Alf Forage Yield and N-rate") +  # Add a title
scale_x_continuous(breaks = c(0, 40, 80, 120, 160))+ #fix x axis scale
  facet_wrap(~P, scales = "free_y",ncol=2)+ #make it by location (remove to make it across locations)
  scale_color_discrete(name = "Cropping System")  #legend for colors
# save figures/forage/ALFforage_Nrate_yr2S.jpeg  775x630

#Threeway means
NYSA1emm <- compute_emmeansNYS("modNYSA1")
#write.csv(NYSA1emm, 'data/Final_Data/NYSA1emm.csv')

#Alf forage E plot (YS)
NYSAemmsP <- emmeans(modNYSA1, ~ P, type = "response") 
emms_df <- as.data.frame(NYSAemmsP)
cld_dataNYSAP <- cld(NYSAemmsP, Letters=custom_letters)
cld_df <-as.data.frame(cld_dataNYSAP)
merged_df <- merge(emms_df, cld_df,by = c("P"))
AYSE<-ggplot(NdYSA, aes(x = P, y = exp(predicted))) +
  geom_jitter(width = 0.2, height = 0, size = 3, alpha = 0.7, color="darkgreen") +
  labs(x = "Environment", y = "Alfalfa Forage Yield") +
  geom_point(data = emms_df, aes(x = P, y = response), 
             size = 4, shape = 18, color = "black")+ 
  geom_errorbar(data = emms_df, aes(x = P, ymin = lower.CL, ymax = upper.CL), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  geom_text(data = merged_df, aes(x = P, y = response.x, label = .group), 
            color = "black", vjust = 0, hjust = 1.8)
print(AYSE)
#ggsave("figures/forage/AYSE.jpg", plot = AYSE, width = 8, height = 6, dpi = 300)





#Pairwise P
emmsP <- emmeans(modNYSA, ~ P, type = "response") # Obtain estimated marginal means (excluding N)
cld_dataNYSAP <- cld(emmsP, Letters=custom_letters) # Create compact letter display
cld_dataNYSAP$response <- format(cld_dataNYSAP$response, digits = 5)
rownames(cld_dataNYSAP) <- NULL
cld_dataNYSAP<- cld_dataNYSAP %>%
  select(P, response, .group)
colnames(cld_dataNYSAP) <- c("Site","IWG Forage (kg ha-1)", "Group")
cld_dataNYSAP  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)
#Pairwise C
emmsC <- emmeans(modNYSA, ~ CROP, type = "response") # Obtain estimated marginal means (excluding N)
cld_dataNYSAC <- cld(emmsC, Letters=custom_letters) # Create compact letter display
#Pairwise N:C
emmsNC <- emmeans(modNYSA, ~ N*CROP,at = list(N = N_levels), type= "response") # Obtain estimated marginal means
cld_dataNYSANC <- cld(emmsNC, Letters=custom_letters) # Create compact letter display
cld_dataNYSANC$response <- format(cld_dataNYSANC$response, digits = 5)
rownames(cld_dataNYSANC) <- NULL
cld_dataNYSANC<- cld_dataNYSANC %>%
  select(N,CROP, response, .group)
colnames(cld_dataNYSANC) <- c("N","Cropping System","Alfalfa Forage (kg ha-1)", "Group")
cld_dataNYSANC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)

#slope stuff
emtrends_result<-emtrends(modNYSA,~ CROP, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_C <- c("intercrop", "monoculture")
  emtrends_df$C <- factor(emtrends_df$C, levels = desired_order_C)
  #view(emtrends_df)
  
#equations table
emtrends_result<-emtrends(modNYSA,~ CROP, var= "N", infer=TRUE)
emtrends_df <- as.data.frame(emtrends_result)
emmeans_results<-emmeans(modNYSA, ~CROP, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c( "CROP")) %>%
  select(CROP, emmean, N.trend, SE.x)
#view(merged_df)
merged_df$CROP <- factor(merged_df$C, levels = c("intercrop", "monoculture"))  # Preferred order for CROP
# Create a new data frame with the calculated column
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sorted_df <- new_df %>%
  arrange( CROP)
#view(sorted_df)
```

#Alf forage year 2 fall
```{r}
#LINEAR
modNYFA<-lmer(PlotAlfDryKgHa~N*P*CROP + (1|Rep), data=NdYFA)
anova(modNYFA)
#Check assumptions
NYFA_resid<-resid(modNYFA)
qqnorm(NYFA_resid)
qqline(NYFA_resid)
plot(modNYFA)
#log transform 
modNYFA1<-lmer(log(PlotAlfDryKgHa)~N*P*CROP + (1|Rep), data=NdYFA)
anova(modNYFA1)
#Check assumptions
NYFA1_resid<-resid(modNYFA1)
qqnorm(NYFA1_resid)
qqline(NYFA1_resid)
plot(modNYFA1)

modNYFA1_summary <- summary(modNYFA1)
modNYFA1_coeff <- as.data.frame(modNYFA1_summary$coefficients)%>%
  filter(`Pr(>|t|)` < 0.05)
# Create custom table using kable and kableExtra
save_kable(
  knitr::kable(modNYFA1_coeff, 
               caption = "Y2 Fall Mixed-Effects Model: log(PlotAlfDryKgHa) ~ Nrate * Location * CROPsystem + (1 | Rep)") %>%
    kable_styling(full_width = TRUE, 
                  position = "center", 
                  bootstrap_options = c("striped", "hover", "condensed")),
  file = "figures/forage/ALF_table_significant_coeff_yr2F.html")
# ALF_table_significant_coeff_yr2F

max(NdYFA$PlotAlfDryKgHa)
#LINEAR plots
NdYFA$predicted <- predict(modNYFA1, newdata = NdYFA, re.form = NA)
ggplot(NdYFA, aes(x = N, y = PlotAlfDryKgHa, color = CROP, group= CROP)) +
    geom_point() + geom_line(aes(N, exp(predicted)))+ #regression through backtransformed predicted values
  labs(x = "N-Rate (Kg/ha)", y = "Alf Forage Yield (Kg/ha)") +  # Label the axes
  ggtitle("Yr 2 F Relationship between Alf Forage Yield and N-rate") +  # Add a title
scale_x_continuous(breaks = c(0, 40, 80, 120, 160))+ #fix x axis scale
  facet_wrap(~P, scales = "free_y",ncol=2)+ #make it by location (remove to make it across locations)
  scale_color_discrete(name = "Cropping System")  #legend for colors
# save figures/forage/ALFforage_Nrate_yr2F.jpeg  775x630

#Threeway means
NYFA1emm <- compute_emmeansNYF("modNYFA1")
#write.csv(NYFA1emm, 'data/Final_Data/NYFA1emm.csv')

#Alf forage E plot (YF)
NYFAemmsP <- emmeans(modNYFA1, ~ P, type = "response") 
emms_df <- as.data.frame(NYFAemmsP)
cld_dataNYFAP <- cld(NYFAemmsP, Letters=custom_letters)
cld_df <-as.data.frame(cld_dataNYFAP)
merged_df <- merge(emms_df, cld_df,by = c("P"))
AYFE<-ggplot(NdYFA, aes(x = P, y = exp(predicted))) +
  geom_jitter(width = 0.2, height = 0, size = 3, alpha = 0.7, color="darkgreen") +
  labs(x = "Environment", y = "Alfalfa Forage Yield") +
  geom_point(data = emms_df, aes(x = P, y = response), 
             size = 4, shape = 18, color = "black")+ 
  geom_errorbar(data = emms_df, aes(x = P, ymin = lower.CL, ymax = upper.CL), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  geom_text(data = merged_df, aes(x = P, y = response.x, label = .group), 
            color = "black", vjust = 0, hjust = 1.8)
print(AYFE)
#ggsave("figures/forage/AYFE.jpg", plot = AYFE, width = 8, height = 6, dpi = 300)







#Pairwise N
emmsN <- emmeans(modNYFA1, ~ N,at = list(N = N_levels), type= "response") # Obtain estimated marginal means
cld_dataNYFAN <- cld(emmsN, Letters=custom_letters) # Create compact letter display
#Pairwise N:C
emmsNC <- emmeans(modNYFA1, ~ N*CROP,at = list(N = N_levels), type= "response") # Obtain estimated marginal means
cld_dataNYFANC <- cld(emmsNC, Letters=custom_letters) # Create compact letter display
cld_dataNYFANC$response <- format(cld_dataNYFANC$response, digits = 5)
rownames(cld_dataNYFANC) <- NULL
cld_dataNYFANC<- cld_dataNYFANC %>%
  select(N,CROP, response, .group)
colnames(cld_dataNYFANC) <- c("N","Cropping System","IWG Forage (kg ha-1)", "Group")
cld_dataNYFANC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)

#slope stuff
emtrends_result<-emtrends(modNYFA1,~ CROP, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_C <- c("intercrop", "monoculture")
  emtrends_df$C <- factor(emtrends_df$C, levels = desired_order_C)
  #view(emtrends_df)
  
  #equations table
emtrends_result<-emtrends(modNYFA1,~ CROP, var= "N", infer=TRUE)
emtrends_df <- as.data.frame(emtrends_result)
emmeans_results<-emmeans(modNYFA1, ~CROP, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c( "CROP")) %>%
  select(CROP, emmean, N.trend, SE.x)
#view(merged_df)
merged_df$C <- factor(merged_df$C, levels = c("intercrop", "monoculture"))  # Preferred order for CROP
# Create a new data frame with the calculated column
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sorted_df <- new_df %>%
  arrange( C)
#view(sorted_df)
```

#Alf forage year 3 summer
```{r}
#LINEAR
modNZSA<-lmer(PlotAlfDryKgHa~N*P*CROP + (1|Rep), data=NdZSA)
anova(modNZSA)
#Check assumptions
NZSA_resid<-resid(modNZSA)
qqnorm(NZSA_resid)
qqline(NZSA_resid)
plot(NZSA_resid)
#log transform 
modNZSA1<-lmer(log(PlotAlfDryKgHa)~N*P*CROP + (1|Rep), data=NdZSA)
anova(modNZSA1)
#Check assumptions
NZSA1_resid<-resid(modNZSA1)
qqnorm(NZSA1_resid)
qqline(NZSA1_resid)
plot(modNZSA1)
# normal is better, no difference in what is significant 

modNZSA1_summary <- summary(modNZSA1)
modNZSA1_coeff <- as.data.frame(modNZSA1_summary$coefficients)%>%
  filter(`Pr(>|t|)` < 0.05)
# Create custom table using kable and kableExtra
save_kable(
  knitr::kable(modNZSA1_coeff, 
               caption = "Y3 Summer Mixed-Effects Model: log(PlotAlfDryKgHa) ~ Nrate * Location * CROPsystem + (1 | Rep)") %>%
    kable_styling(full_width = TRUE, 
                  position = "center", 
                  bootstrap_options = c("striped", "hover", "condensed")),
  file = "figures/forage/ALF_table_significant_coeff_yr3S.html")
# ALF_table_significant_coeff_yr3S

max(NdZSA$PlotAlfDryKgHa)
#LINEAR plots
NdZSA$predicted <- predict(modNZSA1, newdata = NdZSA, re.form = NA)
ggplot(NdZSA, aes(x = N, y = PlotAlfDryKgHa, color = C, group= C)) +
    geom_point() + geom_line(aes(N, exp(predicted)))+ #regression through backtransformed predicted values
  labs(x = "N-Rate (Kg/ha)", y = "Alf Forage Yield (Kg/ha)") +  # Label the axes
  ggtitle("Yr 3 S Relationship between Alf Forage Yield and N-rate") +  # Add a title
scale_x_continuous(breaks = c(0, 40, 80, 120, 160))+ #fix x axis scale
  facet_wrap(~P, scales = "free_y",ncol=2)+ #make it by location (remove to make it across locations)
  scale_color_discrete(name = "Cropping System")  #legend for colors
# save figures/forage/ALFforage_Nrate_yr3S.jpeg  775x630

#Threeway means
NZSA1emm <- compute_emmeansNZS("modNZSA1")
#write.csv(NZSA1emm, 'data/Final_Data/NZSA1emm.csv')

#Alf forage E plot (ZS)
NZSAemmsP <- emmeans(modNZSA1, ~ P, type = "response") 
emms_df <- as.data.frame(NZSAemmsP)
cld_dataNZSAP <- cld(NZSAemmsP, Letters=custom_letters)
cld_df <-as.data.frame(cld_dataNZSAP)
merged_df <- merge(emms_df, cld_df,by = c("P"))
AZSE<-ggplot(NdZSA, aes(x = P, y = exp(predicted))) +
  geom_jitter(width = 0.2, height = 0, size = 3, alpha = 0.7, color="darkgreen") +
  labs(x = "Environment", y = "Alfalfa Forage Yield") +
  geom_point(data = emms_df, aes(x = P, y = response), 
             size = 4, shape = 18, color = "black")+ 
  geom_errorbar(data = emms_df, aes(x = P, ymin = lower.CL, ymax = upper.CL), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  geom_text(data = merged_df, aes(x = P, y = response.x, label = .group), 
            color = "black", vjust = 0, hjust = 1.8)
print(AZSE)
#ggsave("figures/forage/AZSE.jpg", plot = AZSE, width = 8, height = 6, dpi = 300)







#Pairwise N
emmsN <- emmeans(modNYFA1, ~ N,at = list(N = N_levels), type= "response") # Obtain estimated marginal means
cld_dataNYFAN <- cld(emmsN, Letters=custom_letters) # Create compact letter display
#Pairwise N:C
emmsNC <- emmeans(modNYFA1, ~ N*CROP,at = list(N = N_levels), type= "response") # Obtain estimated marginal means
cld_dataNYFANC <- cld(emmsNC, Letters=custom_letters) # Create compact letter display
cld_dataNYFANC$response <- format(cld_dataNYFANC$response, digits = 5)
rownames(cld_dataNYFANC) <- NULL
cld_dataNYFANC<- cld_dataNYFANC %>%
  select(N,CROP, response, .group)
colnames(cld_dataNYFANC) <- c("N","Cropping System","IWG Forage (kg ha-1)", "Group")
cld_dataNYFANC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)

#slope stuff
emtrends_result<-emtrends(modNYFA1,~ CROP, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_C <- c("intercrop", "monoculture")
  emtrends_df$CROP <- factor(emtrends_df$CROP, levels = desired_order_C)
  #view(emtrends_df)
  
  #equations table
emtrends_result<-emtrends(modNYFA1,~ CROP, var= "N", infer=TRUE)
emtrends_df <- as.data.frame(emtrends_result)
emmeans_results<-emmeans(modNYFA1, ~CROP, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c( "CROP")) %>%
  select(CROP, emmean, N.trend, SE.x)
#view(merged_df)
merged_df$CROP <- factor(merged_df$CROP, levels = c("intercrop", "monoculture"))  # Preferred order for CROP
# Create a new data frame with the calculated column
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sorted_df <- new_df %>%
  arrange( CROP)
#view(sorted_df)
```

#Alf forage year 3 fall
```{r}
#LINEAR
modNZFA<-lmer(PlotAlfDryKgHa~N*P*CROP + (1|Rep), data=NdZFA)
anova(modNZFA)
#Check assumptions
NZFA_resid<-resid(modNZFA)
qqnorm(NZFA_resid)
qqline(NZFA_resid)
plot(NZFA_resid)
#log transform 
modNZFA1<-lmer(log(PlotAlfDryKgHa+0.0001)~N*P*CROP + (1|Rep), data=NdZFA)
anova(modNZFA1)
#Check assumptions
NZFA1_resid<-resid(modNZFA1)
qqnorm(NZFA1_resid)
qqline(NZFA1_resid)
plot(modNZFA1)
# normal is much better, but does not have E:C as significant which log does

modNZFA1_summary <- summary(modNZFA1)
modNZFA1_coeff <- as.data.frame(modNZFA1_summary$coefficients)%>%
  filter(`Pr(>|t|)` < 0.05)
# Create custom table using kable and kableExtra
save_kable(
  knitr::kable(modNZFA1_coeff, 
               caption = "Y3 Fall Mixed-Effects Model: log(PlotAlfDryKgHa) ~ Nrate * Location * CROPsystem + (1 | Rep)") %>%
    kable_styling(full_width = TRUE, 
                  position = "center", 
                  bootstrap_options = c("striped", "hover", "condensed")),
  file = "figures/forage/ALF_table_significant_coeff_yr3F.html")
# ALF_table_significant_coeff_yr3F

max(NdZFA$PlotAlfDryKgHa)
#LINEAR plots
NdZFA$predicted <- predict(modNZFA1, newdata = NdZFA, re.form = NA)
ggplot(NdZFA, aes(x = N, y = PlotAlfDryKgHa, color = CROP, group= CROP)) +
    geom_point() + geom_line(aes(N, exp(predicted)))+ #regression through backtransformed predicted values
  labs(x = "N-Rate (Kg/ha)", y = "Alf Forage Yield (Kg/ha)") +  # Label the axes
  ggtitle("Yr 3 F Relationship between Alf Forage Yield and N-rate") +  # Add a title
scale_x_continuous(breaks = c(0, 40, 80, 120, 160))+ #fix x axis scale
  facet_wrap(~P, scales = "free_y",ncol=2)+ #make it by location (remove to make it across locations)
  scale_color_discrete(name = "Cropping System")  #legend for colors
# save figures/forage/ALFforage_Nrate_yr3F.jpeg  775x630

#Threeway means
NZFA1emm <- compute_emmeansNZF("modNZFA1")
#write.csv(NZFA1emm, 'data/Final_Data/NZFA1emm.csv')

#Alf forage figure E:C (ZF)
ZFAemmsPC <- emmeans(modNZFA1, ~ P*CROP, type = "response") # Obtain estimated marginal means (excluding N)
emms_df <- as.data.frame(ZFAemmsPC)
cld_dataZFAPC <- cld(ZFAemmsPC, Letters=custom_letters)
cld_df <-as.data.frame(cld_dataZFAPC)
merged_df <- merge(emms_df, cld_df,by = c("P", "CROP"))
custom_labels <- c("Intercrop", "Monoculture Alfalfa")
custom_colors <- c("darkmagenta", "coral1") 
AZFPC<-ggplot(NdZFA, aes(x = P, y = exp(predicted), color = CROP)) +
  geom_jitter(width = 0.2, height = 0, size = 3, alpha = 0.7) +
  labs(x = "Environment", y = "Alfalfa Forage Yield") +
  geom_point(data = emms_df, aes(x = P, y = response), 
             size = 4, shape = 18, color = "black")+ 
  geom_errorbar(data = emms_df, aes(x = P, ymin = lower.CL, ymax = upper.CL), 
                width = 0.2, color = "black", inherit.aes = FALSE) +
  geom_text(data = merged_df, aes(x = P, y = response.x, label = .group), 
            color = "black", vjust = 0, hjust = 2)+
  scale_color_manual(name = "Cropping System", labels = custom_labels,values = custom_colors)+
     ggtitle("Year 3 Fall")+
  theme(plot.title = element_text(hjust = 0.5))#+
#  scale_y_continuous(breaks = c(1000, 3000, 5000, 7000,9000), limits = c(0, 4000))
print(AZFPC)
#ggsave("figures/forage/AZFPC.jpg", plot = AZFPC, width = 10, height = 8, dpi = 300)





#Pairwise N
emmsN <- emmeans(modNZFA1, ~ N,at = list(N = N_levels), type= "response") # Obtain estimated marginal means
cld_dataNZFAN <- cld(emmsN, Letters=custom_letters) # Create compact letter display
#Pairwise N:C
emmsNC <- emmeans(modNZFA1, ~ N*CROP,at = list(N = N_levels), type= "response") # Obtain estimated marginal means
cld_dataNZFANC <- cld(emmsNC, Letters=custom_letters) # Create compact letter display
cld_dataNZFANC$response <- format(cld_dataNZFANC$response, digits = 5)
rownames(cld_dataNZFANC) <- NULL
cld_dataNZFANC<- cld_dataNZFANC %>%
  select(N,CROP, response, .group)
colnames(cld_dataNZFANC) <- c("N","Cropping System","IWG Forage (kg ha-1)", "Group")
cld_dataNZFANC  |> 
  data.frame() |> 
  kbl(align = "c") |> 
  kable_paper(full_width = F) |> 
  column_spec(1, bold = T)

#slope stuff
emtrends_result<-emtrends(modNZFA1,~ CROP, var= "N", infer=TRUE)
  emtrends_df <- as.data.frame(emtrends_result)
  desired_order_C <- c("intercrop", "monoculture")
  emtrends_df$CROP <- factor(emtrends_df$CROP, levels = desired_order_C)
  #view(emtrends_df)
  
  #equations table
emtrends_result<-emtrends(modNZFA1,~ CROP, var= "N", infer=TRUE)
emtrends_df <- as.data.frame(emtrends_result)
emmeans_results<-emmeans(modNZFA1, ~CROP, at=list(N=0))
emmeans_df <- as.data.frame(emmeans_results)
merged_df <- emtrends_df %>%
  inner_join(emmeans_df, by = c( "CROP")) %>%
  select(CROP, emmean, N.trend, SE.x)
#view(merged_df)
merged_df$CROP <- factor(merged_df$CROP, levels = c("intercrop", "monoculture"))  # Preferred order for CROP
# Create a new data frame with the calculated column
new_df <- merged_df %>%
  mutate(equation = sprintf("=%.2f*e(%.4fN)", exp(emmean), N.trend),  SE.x = sprintf("%.4f", SE.x),  percent_change = sprintf("%.2f%%", (exp(N.trend) - 1) * 100))%>%
  select(-emmean, -N.trend)
sorted_df <- new_df %>%
  arrange( CROP)
#view(sorted_df)
```


# Alf Forage anovas Table 
```{r}
aov.tableXS <- anova(modNXSA1)
tableAFXS = flextable(data = aov.tableXS %>%
                    #filter(`Pr(>F)` < 0.05) %>%
                    mutate(`Pr(>F)` = formatC(`Pr(>F)`, digits = 3)) %>% 
                    select(`Pr(>F)`) %>%
                    rownames_to_column(" ")) 
print(tableAFXS)
# save figures/forage/gt_AFXS 

aov.tableXF <- anova(modNXFA1)
tableAFXF = flextable(data = aov.tableXF %>%
                    #filter(`Pr(>F)` < 0.05) %>%
                    mutate(`Pr(>F)` = formatC(`Pr(>F)`, digits = 3)) %>% 
                    select(`Pr(>F)`) %>%
                    rownames_to_column(" ")) 
print(tableAFXF)
# save figures/forage/gt_AFXF

aov.tableYS <- anova(modNYSA1) 
tableAFYS = flextable(data = aov.tableYS %>%
                    #filter(`Pr(>F)` < 0.05) %>%
                    mutate(`Pr(>F)` = formatC(`Pr(>F)`, digits = 3)) %>% 
                    select(`Pr(>F)`) %>%
                    rownames_to_column(" ")) 
print(tableAFYS)
# save figures/forage/gt_AFYS 

aov.tableYF <- anova(modNYFA1)
tableAFYF = flextable(data = aov.tableYF %>%
                    #filter(`Pr(>F)` < 0.05) %>%
                    mutate(`Pr(>F)` = formatC(`Pr(>F)`, digits = 3)) %>% 
                    select(`Pr(>F)`) %>%
                    rownames_to_column(" ")) 
print(tableAFYF)
# save figures/forage/gt_AFYF

aov.tableZS <- anova(modNZSA1)
tableAFZS = flextable(data = aov.tableZS %>%
                    #filter(`Pr(>F)` < 0.05) %>%
                    mutate(`Pr(>F)` = formatC(`Pr(>F)`, digits = 3)) %>% 
                    select(`Pr(>F)`) %>%
                    rownames_to_column(" ")) 
print(tableAFZS)
# save figures/forage/gt_AFZS 

aov.tableZF <- anova(modNZFA1)
tableAFZF = flextable(data = aov.tableZF %>%
                    #filter(`Pr(>F)` < 0.05) %>%
                    mutate(`Pr(>F)` = formatC(`Pr(>F)`, digits = 3)) %>% 
                    select(`Pr(>F)`) %>%
                    rownames_to_column(" ")) 
print(tableAFZF)
# save figures/forage/gt_AFZF


my_modelsNG <- list(modNXSA1, modNXFA1, modNYSA1, modNYFA1, modNZSA1, modNZFA1)
anovasNG <- purrr::map(my_modelsNG, ~anova(.))
names(anovasNG) <- c("Year 1 S", "Year 1 F", "Year 2 S", "Year 2 F", "Year 3 S", "Year 3 F")

# Function to format p-values as stars
format_p_value <- function(p_val) {
  stars <- ifelse(p_val < 0.001, "***", ifelse(p_val < 0.01, "**", ifelse(p_val < 0.05, "*", "")))
  return(stars)
}

# Apply the function to your ANOVA results
NG_stars_tibble <- map(anovasNG, as_tibble, rownames="term") %>%
  bind_rows(.id = "model") %>%
  mutate(stars = map_chr(`Pr(>F)`, format_p_value))

NG_stars_tibble <- NG_stars_tibble %>%
  mutate(term = ifelse(term == "P", "E", term)) %>%
  mutate(term = ifelse(term == "N:P", "N:E", term))%>%
  mutate(term = ifelse(term == "P:CROP", "E:CROP", term))%>%
  mutate(term = ifelse(term == "N:P:CROP", "N:E:CROP", term))%>%
  filter(term != "Residuals")

# Print the tibble
print(NG_stars_tibble)

NG_stars <-NG_stars_tibble |> 
  select(model, term, stars) |>
  pivot_wider(names_from = term, values_from = stars)

gt_NG <- gt(NG_stars)

gt_NG |> gtsave("figures/forage/gt_AF.png", expand = 10)
```




#Alf forage plots N:C 
#HERE
```{r}
# Layer all the plots together!
colors <- c("Year 1 Summer Harvest" = "red", 
            "Year 1 Fall Harvest" = "green", 
            "Year 2 Summer Harvest" = "blue", 
            "Year 2 Fall Harvest" = "purple", 
            "Year 3 Summer Harvest" = "orange")
legend_order <- c("Year 1 Summer Harvest", "Year 1 Fall Harvest",
                  "Year 2 Summer Harvest", "Year 2 Fall Harvest",
                  "Year 3 Summer Harvest")
NdXSA$P <- factor(NdXSA$P, levels = desired_order)
NdYSA$P <- factor(NdYSA$P, levels = desired_order)
NdZSA$P <- factor(NdZSA$P, levels = desired_order)

max(NdXSA$PlotAlfDryKgHa)
max(NdXFA$PlotAlfDryKgHa)
max(NdYSA$PlotAlfDryKgHa)
max(NdYFA$PlotAlfDryKgHa)
max(NdZSA$PlotAlfDryKgHa)

AFcomboplot <- ggplot() +
  geom_line(data = NdXSA, aes(N, exp(predicted), color = "Year 1 Summer Harvest", linetype= CROP)) +
  geom_point(data = NdXSA, aes(x = N, y = PlotAlfDryKgHa, color = "Year 1 Summer Harvest", shape= CROP)) +
  geom_line(data = NdXFA, aes(N, exp(predicted), color = "Year 1 Fall Harvest", linetype= CROP)) +
  geom_point(data = NdXFA, aes(x = N, y = PlotAlfDryKgHa, color = "Year 1 Fall Harvest", shape= CROP)) +
  geom_line(data = NdYSA, aes(N, exp(predicted), color = "Year 2 Summer Harvest", linetype= CROP)) +
  geom_point(data = NdYSA, aes(x = N, y = PlotAlfDryKgHa, color = "Year 2 Summer Harvest", shape= CROP)) +
  geom_line(data = NdYFA, aes(N, exp(predicted), color = "Year 2 Fall Harvest", linetype= CROP)) +
  geom_point(data = NdYFA, aes(x = N, y = PlotAlfDryKgHa, color = "Year 2 Fall Harvest", shape= CROP)) +
  geom_line(data = NdZSA, aes(N, exp(predicted), color = "Year 3 Summer Harvest", linetype= CROP)) +
  geom_point(data = NdZSA, aes(x = N, y = PlotAlfDryKgHa, color = "Year 3 Summer Harvest", shape= CROP)) +
  geom_line(data = NdZFA, aes(N, exp(predicted), color = "Year 3 Fall Harvest", linetype= CROP)) +
  geom_point(data = NdZFA, aes(x = N, y = PlotAlfDryKgHa, color = "Year 3 Fall Harvest", shape= CROP)) +
  labs(x = "N-Rate (kg ha-1)", y = "Total Forage Yield",
       color = "Harvest", 
       linetype = "Cropping System", shape = "Cropping System") +
  ggtitle("Relationship Between Alfalfa Forage Yield and N-rate") +
  scale_x_continuous(breaks = c(0, 40, 80, 120, 160)) +
  ylim(0, 10000) +
  facet_wrap(~P, scales = "free", ncol = 2) +
  scale_color_manual(values = colors, limits = legend_order)+
  scale_shape_manual(values = c(4, 20, 25),labels = c("Intercropped", "Monoculture Alfalfa") )+
  scale_linetype_manual(values = c("inter" = "solid", "monoA" = "dotted"),labels = c("Intercropped", "Monoculture Alfalfa"))


print(AFcomboplot)


ggsave("AFcomboplotNC.jpg", plot = AFcomboplotNC, width = 8, height = 6, dpi = 300)
```





#Alf forage combo plot E:C
```{r}
AEC<-grid.arrange(AXSPC, AXFPC, ncol = 2)
ggsave("AEC.jpg", plot = AEC, width =12, height = 6, dpi = 350)
```

### Action items from Megan: 
# values and proportions of each species in total forage yield for intercropped plots (not PrLER)
#   look at code for proportional partical and adjust to fit what she wants